---
title: "Link2Care Survey Data - Update Individual Survey Data Frames"
date: "2021-07-28 <br> Updated: `r Sys.Date()`"
---

# â­ï¸Overview

This file we update all of the individual data frames that will make up the merged survey data frame. 


# ðŸ“¦Load packages

```{r}
source("R/source_rmd.R")
```


# ðŸ“¥Import data 

We previously imported and did some initial cleaning of the following data sets:

* QDS (data_survey_01_qds_import.Rmd)   
* REDCap (data_survey_02_redcap_import.Rmd)    
* Master log (data_survey_03_master_log_import.Rmd)   
* Timeline followback (data_survey_04_tlfb_import.Rmd)   
* Arrest data (data_survey_05_arrests_import.Rmd)   
* Bridge sessions data (data_survey_06_bridge_sessions_import.Rmd) 

## QDS

```{r}
source_rmd("data_survey_01_qds_import.Rmd")

# 2022-07-11: v1 imported with 360 rows and 810 columns.
# 2022-07-11: v2 imported with 331 rows and 213 columns.
# 2022-07-11: v3 imported with 232 rows and 542 columns.
# 2022-07-11: v4 imported with 170 rows and 598 columns.
# 2022-07-11: v5 imported with 148 rows and 649 columns.
# 2022-07-11: QDS data imported and merged with 1241 rows and 1049 columns.
```

## REDCap

```{r}
source_rmd("data_survey_02_redcap_import.Rmd")

# 2022-07-11: REDCap data cleaned with 21 rows and 911 columns.
```

## Master log 

```{r}
source_rmd("data_survey_03_master_log_import.Rmd")

# 2022-07-11: Master log cleaned with 383 rows and 55 columns.
```

## Timeline followback 

```{r}
source_rmd("data_survey_04_tlfb_import.Rmd")

# 2022-07-11: TLFB data cleaned with 1516 rows and 21 columns.
```

## Arrest data

The arrest data is securely transmitted by Dr. Gonzalez as an Excel file, which is stored on the the UTHealth servers in Participant Data > Arrest Data Requests.

Before you can import the Excel file, you must open it and remove the password from the Excel sheet. File -> Passwords... -> Delete password.   

```{r}
source_rmd("data_survey_05_arrests_import.Rmd")

# Arrest data cleaned with 274 rows and 8 columns.
```

## Bridge sessions data

```{r}
source_rmd("data_survey_06_bridge_sessions_import.Rmd")

# 2022-07-11: Bridge session wide data cleaned with 376 rows and 20 columns.
```

## DDT data

```{r}
source_rmd("data_survey_07_ddt_import.Rmd")

# 2022-07-11: DDT data cleaned with 1516 rows and 4 columns.
```


# ðŸ”„Merge data 

```{r}
source_rmd("data_survey_21_merge.Rmd")

# 2022-07-11: Combined Participant data cleaned with 1285 rows and 1205 columns.
```


# ðŸ—‘Clean up

Don't use `rm(list = ls())` because is causes R to drop the helper functions in data_survey_21_update_all_data.Rmd

```{r}
rm(list = ls())
```
