---
title: "Import and Manage Link2Care Survey Data - Master Log"
date: "2021-04-23 <br> Updated: `r Sys.Date()`"
---

# ⭐️Overview

This file is used to import the Link2Care follow-up visit survey data and do some initial data cleaning.

[Notes on cleaning individual L2C data sets for merging](https://github.com/brad-cannell/link2care_public/wiki/Notes-on-cleaning-individual-L2C-data-sets-for-merging)

# 📦Load packages

```{r message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(readxl, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
```


# 📥Import data 

```{r}
path <- "../Live Documents/Master Log (version2).xlsx"
```

Check the most recent file modification dates on the UTHealth servers and print for user when this file is being sourced.

```{r}
cat(
  stringr::str_extract(path, "([^/]+$)"),
  "last modified on OneDrive:",
  as.character(file.info(path)$mtime), "\n"
)
```

## Screened-in

```{r}
master_log_screened_in <- read_excel(
  path,
  sheet = "Screened In",
  col_names = c(
    "id", "status", "date_baseline", "date_dropped", "date_v2_scheduled", "date_v2_presented",
    "late_v2", "no_show_v2","days_v2_to_v3_scheduled","date_v3_scheduled", 
    "date_v3_presented", "late_v3", "no_show_v3", "days_v3_to_v4_scheduled", 
    "date_v4_scheduled", "date_v4_presented", "late_v4", "no_show_v4", 
    "days_4v_to_v5_scheduled", "date_v5_scheduled", "date_v5_presented", 
    "late_v5", "no_show_v5", "group", "v2_status", "dropped_status", "name_first",
    "name_middle_init",  "name_last", "gender", "race", "hispanic", "date_birth", 
    "age", "clincard_id", "n_clincards", "phone_id", "phone_number_l2c", 
    "phone_n_distributed", "care_manager", "v1", "v2", "v3", "v4", "v5", 
    "v3_r_distributed", "v3_r_completed", "v4_r_distributed", 
    "v4_r_completed","v5_r_distributed", "v5_r_completed", "v2_phone", "v3_phone",
    "v4_phone", "v5_phone"
  ),
  col_types = c(
    # Some of the dates must be imported as text because the have embedded 
    # notes (e.g., "no show")
    rep("text",2), rep("date", 4), rep("text", 2), "numeric", rep("date", 2),
    rep("text", 2), "numeric", rep("date", 2), rep("text", 2), "numeric", rep("date", 2), rep("text", 11),
    "date", "numeric", "text", "numeric", rep("text", 2), "numeric", "text", rep("text", 15)
  ),
  na = c("", ".", "N/A", "No show", "No Show"),
  skip = 1
) %>% 
  filter(!is.na(id))

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Master log screened in imported with", nrow(master_log_screened_in), "rows and",
  ncol(master_log_screened_in),
  "columns.\n"
)

# 2022-07-11: Master log screened in imported with 383 rows and 55 columns.
```

## Screened-out

```{r}
master_log_screened_out <- read_excel(
  path,
  sheet = "Screened Out",
  col_names = c(
    "id", "name_full", "date_baseline", "gender",  "race", "hispanic", 
    "date_birth", "age", "reason_1", "reason_2", "reason_3", "reason_4", "reason_5", "reason_6", "reason_7", "reason_8", "reason_9", "notes"
  ),
  col_types = c(
    "text", "text", "date", rep("text", 3), "date", "numeric", 
    rep("text", 9), "skip", "text"
  ),
  skip = 1,
  na = c("", "N/A")
)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Master log screened out imported with", nrow(master_log_screened_out), 
  "rows and", ncol(master_log_screened_out),
  "columns.\n"
)

# 2022-07-11: Master log screened out imported with 61 rows and 12 columns.
```


# 🚧Data management

## Coerce group to numeric 

So that it can be combined with the QDS data.

```{r}
master_log_screened_in <- master_log_screened_in %>% 
  mutate( 
    group = case_when(
      group == "UCM"    ~ 1,
      group == "UCM+SP" ~ 2,
      group == "L2C"    ~ 3
    )
  )
```

Data check: There should only be 3 groups

```{r}
table(master_log_screened_in$group)
```

```{r}
if (length(table(master_log_screened_in$group)) != 3) {
  stop("The group column should only have 3 values. It has ", length(table(master_log_screened_in$group)))
}
```
# Deidentify master log first, middle, and last names

```{r}
# start <- lubridate::now()
# test_cb <- codebook(
#   test, 
#   no_summary_stats = c(
#     "ml_name_first", "ml_name_middle_init", "ml_name_last", "ml_date_birth",
#     "ml_clincard_id", "ml_phone_number_l2c", "ml_care_manager", "ii"
#   )
# )
# end <- lubridate::now()
```
# 💾Save the data frames

```{r}
path <- "../Participant Data/R Data/master_log_screened_in.rds"
```

```{r}
write_rds(master_log_screened_in, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Master Log Screened In saved to", path, "\n"
)
```

```{r}
path <- "../Participant Data/R Data/master_log_screened_out.rds"
```

```{r}
write_rds(master_log_screened_out, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Master Log Screened Out saved to", path, "\n"
)
```


# 🖨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Master log cleaned with", nrow(master_log_screened_in), "rows and",
  ncol(master_log_screened_in),
  "columns.\n"
)

# 2022-07-01: Master log cleaned with 378 rows and 55 columns.
```


# 🗑Clean up

Don't use `rm(list = ls())` because is causes R to drop the helper functions in data_survey_21_update_all_data.Rmd

```{r}
rm(list = ls()[ls() != "source_rmd"])
```
