---
title: "Import and Manage Arrest Data"
date: "2021-04-23 <br> Updated: `r Sys.Date()`"
---

# â­ï¸Overview

This file is used to import the Link2Care arrest data and do some initial data cleaning. 

**NOTE on data sources:**

The arrest data is securely transmitted by Dr. Gonzalez as an Excel file, which is stored on the the UTHealth servers in Participant Data > Arrest Data Requests.


# ðŸ“¦Load packages

```{r message=FALSE}
library(dplyr)
library(readxl)
library(readr)
```


# ðŸŒŽConnect to UTH server 

```{bash eval=FALSE}
# Don't drill all the way down to live documents because not all of the data is in live documents.
open 'smb://islgpcifs.uthouston.edu/sph_research/Link2Care/'
```


# ðŸ“¥Import data 

* Had to remove password from Excel sheet before import. Help -> Passwords -> Delete password.   
* Had to do a little bit of manual removal of text from dates (i.e., "CURRENTLY IN CUSTODY") in the Excel file.   

```{r}
arrest <- read_excel(
  "/Volumes/Link2Care/Participant Data/Arrest Data Requests/Current_Arrest Data_De-identified_2001-2234.xlsx",
  sheet = "Sheet1",
  col_names = c(
    "subject", "arrested", "arrested_date_baseline", paste("arrested_date", 1:5, sep = "_")
  ),
  col_types = c(
    "numeric", "text", rep("date", 6)
  ),
  na = c("", "None"),
  skip = 1
)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Arrest data", nrow(arrest), "rows and", ncol(arrest), "columns.\n"
)

# 2021-06-30: Arrest data 234 rows and 8 columns.
```


# ðŸ’¾Save the data frame

```{r}
path <- "/Volumes/Link2Care/Participant Data/R Data/arrest.rds"
```

```{r}
write_rds(arrest, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Arrest data saved to", path
)

# 2021-06-30: Arrest data saved to /Volumes/Link2Care/Participant Data/R Data/arrest.rds
```


# ðŸ—‘Clean up

```{r}
rm(path)
```


# ðŸ–¨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Arrest data cleaned with", nrow(arrest), "rows and", ncol(arrest), "columns.\n"
)

# 2021-06-30: Arrest data cleaned with 234 rows and 8 columns.
```

```{r echo=FALSE}
sessionInfo()
```