---
title: "Timeline Followback"
date: "2021-06-30 <br> Updated: `r Sys.Date()`"
---

# â­ï¸Overview

This file is used to import the Link2Care follow-up visit survey data and do some initial data cleaning. 

**NOTE on data sources:**

The TLFB data is exported from somewhere as 3 individual Excel files (i.e., alcohol, drug use, location) for each participant. Those individual files are stored on OneDrive in Participant Data > TLFB Data. At some point, SPSS is used to merge (and possibly clean?) these individual data sets. The merged TLFB data is stored on the UTHealth servers in Participant Data > SPSS Data > TLFB Data. That is the data we are importing below.


# ðŸ“¦Load packages

```{r message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(haven, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(testthat, warn.conflicts = FALSE)
```

# ðŸ“¥Import data 

```{r}
path <- "../Participant Data/Combined Participant Data/SPSS Data/TLFB Data/TLFB_Database.sav"
```

Check the most recent file modification dates on OneDrive and print for user when this file is being sourced.

```{r}
cat(
  stringr::str_extract(path, "([^/]+$)"),
  "last modified on UTHealth server:",
  as.character(file.info(path)$mtime), "\n"
)
```

```{r}
tlfb <- read_sav(path)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "TLFB", nrow(tlfb), "rows and", ncol(tlfb), "columns.\n"
)

# 2022-07-11: TLFB 1516 rows and 21 columns.
```


# Clean variable names

_See "Notes on cleaning individual L2C data sets for merging" for the rationale, style guidelines, and instructions for this section._

* Remove all capital letters   
* Make sure names that appear in QDS have the same name   
* Make sure underscores are used consistently   


```{r}
current_col_names <- names(tlfb)
new_col_names <- tolower(current_col_names)
new_col_names[new_col_names == "participantid"] <- "subject"
new_col_names[new_col_names == "totaldrinks"] <- "total_drinks"
new_col_names[new_col_names == "flag_outofwindow"] <- "flag_out_of_window"
```

```{r}
names(tlfb) <- new_col_names
```


# ðŸš§Data management

## Coerce periods to missing 

Coercing to numeric will replace the periods with `NA` and coerce the number values to actual numbers.

```{r}
tlfb <- tlfb %>%
  mutate(
    across(
      everything(),
      function(x) {
        x[x == "."] <- NA
        x <- suppressWarnings(x_num <- as.numeric(x))
      }
    )
  )
```


# ðŸ’¾Save the data frame

```{r}
path <- "../Participant Data/R data/tlfb.rds"
```

```{r}
write_rds(tlfb, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "TLFB data saved to", path, "\n"
)
```


# ðŸ–¨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "TLFB data cleaned with", nrow(tlfb), "rows and", ncol(tlfb), "columns.\n"
)

# 2022-07-11: TLFB data cleaned with 1516 rows and 21 columns.
# 2023-04-19: TLFB data cleaned with 1768 rows and 21 columns.
```


# ðŸ—‘Clean up

Don't use `rm(list = ls())` because is causes R to drop the helper functions in data_survey_21_update_all_data.Rmd

```{r}
rm(list = ls()[ls() != "source_rmd"])
```
