---
title: "Import and Manage Bridge Sessions Data"
date: "2021-04-23 <br> Updated: `r Sys.Date()`"
---

# â­ï¸Overview

This file is used to import the Link2Care Bridge sessions data and do some initial data cleaning. 

**NOTE on data sources:**

The Bridge sessions data is securely stored as an Excel file on OneDrive in Participant Data > Bridge Session Data.


# ðŸ“¦Load packages

```{r message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(readxl, warn.conflicts = FALSE)
library(stringr, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
```


# ðŸ“¥Import data 

* Bridge session Excel file is password protected and the password can't be removed. Therefore, you have to open the password protected file, select all the data, copy, and then paste into a new Excel file that is not password protected.   

```{r}
path <- "../Participant Data/Combined Participant Data/Bridge Session Data/bridge_session_minutes.xlsx"
```

Check the most recent file modification dates on the UTHealth servers and print for user when this file is being sourced.

```{r}
cat(
  stringr::str_extract(path, "([^/]+$)"),
  "last modified on UTHealth server:",
  as.character(file.info(path)$mtime), "\n"
)
```

```{r}
bridge <- read_excel(
  path,
  sheet = "Sheet1",
  col_names = c(
    "subject", "bridge_baseline_date", "bridge_v2_rand_date", 
    "bridge_v5_sched_final_visit_date", "bridge_date_session", "bridge_type", 
    "bridge_duration", "bridge_flag_ns_v2", "bridge_flag_dropped", "bridge_notes"
  ),
  col_types = c(
    "numeric", rep("date", 3), "text", rep("numeric", 4), "text"
  ),
  na = c("", ".", "None"),
  skip = 10
)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Bridge session data", nrow(bridge), "rows and", ncol(bridge), "columns.\n"
)

# 2022-07-11: Bridge session data 3744 rows and 10 columns.
# 2023-05-15: Bridge session data 4364 rows and 10 columns.
```


# ðŸš§Data management

Remove text from date columns and convert to dates.

```{r}
bridge <- bridge %>%
  mutate(
    bridge_date_session = if_else(
      str_detect(bridge_date_session, "[A-Z]|[a-z]"), 
      NA_character_, bridge_date_session
    ),
    bridge_date_session = as.numeric(bridge_date_session),
    bridge_date_session = as.Date(bridge_date_session, origin = "1899-12-30")
  )
```

Remove instructions from "notes" column of rows 1 and 2.

```{r}
bridge[1, "bridge_notes"] <- NA_character_
bridge[2, "bridge_notes"] <- NA_character_
```

Drop blank rows. In the Excel sheet there were some blank spacer rows.

* `c_across()` doesn't work with columns of different types. So, creating missing data dummy variables.

```{r} 
bridge <- bridge %>%
  # Create missing data dummy variables
  mutate(
    across(
      everything(),
      is.na,
      .names = "{col}_miss"
    )
  ) %>% 
  # Sum missing data dummy variables
  rowwise() %>% 
  mutate(
    n_missing = sum(c_across(ends_with("_miss")))
  ) %>% 
  ungroup() %>% 
  # Drop missing data dummy variables
  select(-ends_with("_miss")) %>% 
  # Drop rows that are missing in every column
  filter(!n_missing == ncol(bridge))
```

Carry forward id numbers. In the Excel sheet, the id number is only given in the first row of each set of rows for each participant.

```{r}
bridge <- bridge %>%
  # Carry forward id
  fill(subject) %>% 
  group_by(subject) %>% 
  # Carry forward other variables grouped by id
  fill(
    bridge_baseline_date, bridge_v2_rand_date, bridge_v5_sched_final_visit_date
  ) %>% 
  ungroup()
```

Create a factor for session type and a dummy variable for case management.

```{r}
bridge <- bridge %>%
    mutate(
    # Change NA to None for type
    bridge_type = if_else(is.na(bridge_type), 4, bridge_type),
    # Create factor version
    bridge_type_f = factor(
      bridge_type,
      1:4,
      c("case_management", "crisis_management", "other", "none")
    ),
    # Create dummy variable for case management
    bridge_case_management = bridge_type_f == "case_management"
  )
```

Create a dummy variable for    
* "Used at least one session of regular case management."    
* "Used at least one session of crisis case management."    
* "Used at least one session of other case management."    
* "Used no forms of Bridge case management."    

```{r}
bridge <- bridge %>%
  group_by(subject) %>% 
  mutate(
    bridge_row = row_number(),
    bridge_total_sessions = sum(bridge_type %in% 1:3),
    bridge_total_minutes = sum(bridge_duration, na.rm = TRUE),
    bridge_any_case_management = any(bridge_type_f == "case_management"),
    bridge_any_crisis_management = any(bridge_type_f == "crisis_management"),
    bridge_any_other = any(bridge_type_f == "other"),
    bridge_all_none = all(bridge_type_f == "none")
  ) %>% 
  ungroup()
```

Create a "wide" version of the data with one row per participant.

```{r}
bridge_wide <- bridge %>% 
  filter(bridge_row == 1)
```


# ðŸ’¾Save the data frames

```{r}
path <- "../Participant Data/R data/bridge.rds"
```

```{r}
write_rds(bridge, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Bridge session long data saved to", path, "\n"
)
```

```{r}
path <- "../Participant Data/R data/bridge_wide.rds"
```

```{r}
write_rds(bridge_wide, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Bridge session wide data saved to", path, "\n"
)
```


# ðŸ–¨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Bridge session long data cleaned with", nrow(bridge), "rows and", ncol(bridge), "columns.\n"
)

# 2022-07-11: Bridge session long data cleaned with 3095 rows and 20 columns.
# 2023-05-15: Bridge session long data cleaned with 3715 rows and 20 columns.
```

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Bridge session wide data cleaned with", nrow(bridge_wide), "rows and", ncol(bridge_wide), "columns.\n"
)

# 2022-07-11: Bridge session wide data cleaned with 376 rows and 20 columns.
# 2023-05-15: Bridge session wide data cleaned with 442 rows and 20 columns.

```


# ðŸ—‘Clean up

Don't use `rm(list = ls())` because is causes R to drop the helper functions in data_survey_21_update_all_data.Rmd

```{r}
rm(list = ls()[ls() != "source_rmd"])
```
