---
title: "Import Link2Care Survey Data - QDS Visit 1"
date: "2020-12-23 <br> Updated: `r Sys.Date()`"
---

# ⭐️Overview

This file is used to import the Link2Care follow-up visit survey data and do some initial data cleaning. 

**NOTE on using multiple import code files:**
Previously, I was trying to clean all the separate data frames (i.e, QDS v1-v5, REDCap, and Master Log) in a single Rmd file. 

In theory, this is more efficient than importing and cleaning each visit file separately. For example, we can clean "race" instead of cleaning "race_v1", "race_v2", etc.

However, there are at least two issues with that approach:   
1. There are intentional differences in the variable names (e.g., "V1" and "V2"), and unintentional errors (e.g., HEIGHT_3) in the variable names, from data frame to data frame that make combining them very difficult.   
2. These differences and errors can be "fixed"; however, doing so makes the variable names so different from the codebook that the codebook is barely usable.

For now, I'm going to try importing and cleaning each data file using a separate code file. There may be opportunities to make this more efficient in the future.

**NOTE on data sources:**
* The QDS data is exported from QDS in SPSS data format. The data has to be exported by visit (i.e., v1, v2, ... v5). The SPSS data is then added to the UTHealth servers.

* Some of the v3-v5 visits are also done using REDCap. That data is exported from REDCap and added to the UTHealth servers.

**NOTE on Kiteworks:**
Currently, I'm importing all of this data from the UTHealth server. The data should also be available on Kiteworks if you are unable to connect to the server for some reason.


# 📦Load packages

```{r message=FALSE}
library(dplyr)
library(purrr)
library(haven)
library(officer)
library(readr)
library(tidyr)
library(stringr)
library(testthat)
```

```{r}
source("R/standardize_col_names.R")
source("R/word_cb_extract_fs.R")
```


# 🌎Connect to UTH server 

```{bash eval=FALSE}
# Don't drill all the way down to live documents because not all of the data is in live documents.
open 'smb://islgpcifs.uthouston.edu/sph_research/Link2Care/'
```


# 📥Import data 

Import all 5 QDS data frames

```{r}
qds_spss_path <- "/Volumes/Link2Care/Participant Data/SPSS Data/QDS Data/"

walk(
  .x = c(1:5),
  .f = function(x) {
    new_nm <- paste0("v", x)
    sav_nm <- paste0("Visit_", x, "_Data.SAV")
    path <- paste0(qds_spss_path, sav_nm)
    assign(new_nm, read_sav(path), envir = .GlobalEnv)
  }
)

rm(qds_spss_path)
```

Print a message for when this file is being sourced

```{r}
walk(
  .x = c(1:5),
  .f = function(x) {
    df_nm <- paste0("v", x)
    df <- get(df_nm, envir = .GlobalEnv)
    # Print a message for when this file is being sourced
    cat(
      paste0(Sys.Date(), ":"),
      df_nm, "imported with", nrow(df), "rows and", ncol(df), "columns.\n"
    )
  }
)

# These are expected to change over time as we add more people to the study.
# However, drastic changes from month-to-month, or even quarter-to-quarter,
# should initiate an investigation into what's going on.
# 2021-07-12: v1 imported with 295 rows and 810 columns.
# 2021-07-12: v2 imported with 271 rows and 210 columns.
# 2021-07-12: v3 imported with 194 rows and 542 columns.
# 2021-07-12: v4 imported with 145 rows and 598 columns.
# 2021-07-12: v5 imported with 133 rows and 639 columns.
```


# Clean column names

We have to make the column names match across visits so that we can merge all of the individual QDS data frames into one.

## Reorder columnn names and manual changes

1. The columns in the data are not arranged in the order that they exist in the actual QDS survey for some reason. This makes the data harder to work with, and it will make the codebook we eventually create difficult to use. So, we are going to reorder them. To prevent us from typing out 810 variable names manually, we are going to read-in the variable names from the codebook and then create a blog of text that we copy and paste into a code chunk using `select()` below. Prepping the codebook to be able to do this took a long time and isn't very future-proof. However, we should only have to do this step once. As changes occur to QDS in the future, we can just update the code chunk with the `select()` function.

2. There are some instances where it makes sense to make manual changes to column names now, before the standardization process below. For example, the MMSE columns. It's better to manually change them now because after standardize_col_names you can no longer cut and paste from the Word codebooks. Also, it becomes difficult to be sure which variables in the data correspond to which variables in the codebook (e.g., "mms_4" and "mms_4v").There will also be additional manual changes made after the standardization process. 

### Extract content from Word codebooks

_See "Notes on cleaning individual L2C data sets for merging" for the rationale, style guidelines, and instructions for this section._

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
word_cb_content_list <- map(
  .x = c(1:5),
  .f = function(x) {
    word_cb_full_path <- paste0("docs/codebooks/", "L2C_V", x, " Codebook.docx")
    word_cb_content <- read_docx(word_cb_full_path) %>% 
      docx_summary() %>% 
      mutate(visit = x)
  }
)
```

Keep the parts of the codebook we are interested in for this process (i.e., section names and column names)

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
word_cb_secs_cols_list <- map(
  .x = word_cb_content_list,
  .f = get_sec_and_col_names_from_word_cb
)
```

Clean up the section names. For example, convert `Sect-0.*****Admin*****` to `Admin`

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
word_cb_secs_cols_list <- map(
  .x = word_cb_secs_cols_list,
  .f = clean_word_cb_sec_names
)
```

Create a new column in the new_name = old_name format that we can copy and paste into `select()` later.

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
word_cb_secs_cols_list <- map(
  .x = word_cb_secs_cols_list,
  .f = create_copy_paste_col
)
```

Record the sections that are completed at visit 1. We will use this for checking to make sure all of the correct questionnaire sections merge later.

```{r}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
q_sections <- map(
  .x = word_cb_secs_cols_list,
  .f = ~ unique(.x$section_name)
)
```

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
write_rds(q_sections, "data/qds_questionnaire_sections.rds")
```

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
rm(q_sections)
```

**NOTE:** There are more columns in the data than there are in the codebooks. This is due to calculated variables that were created when the raw QDS data was passed through an SPSS script. We may change that process at some point in the future. 

Have R write out the column names in the order that they appear in QDS. Then, we will copy and paste into the `select()` function. We will do this instead of directly passing the column order to `select()` because we need to make some manual changes to the column names now. Again, we should only have to do this once, and all future updates will be done directly in the code chunk with `select()`. 

### v1: Reorder columnn names and manual changes

**Change log:**

On 2021-06-10, VISIT_TYPE was added to QDS.

On 2021-06-05, Joe Waring found a discrepancy between the way Tobacco 26 was being asked in QDS and REDCap. 

In QDS, T26_V1, T26_V3, T26_V4, and T26_V5 read:

Which option would give you the best chance for quitting smoking?
1	=	Medications
2	=	Counseling
3	=	Both medications and counseling
4	=	Smartphone app
5	=	Both smartphone app and medications
6	=	Quitting "cold turkey" - without counseling or medications
9	=	skipped

And only one answer choice was possible.

In REDCap, t26_v1 reads:

If you were to try to quit smoking, which of the following would you prefer to receive: (select all that apply)

1 t26_v1___1 Medications
2 t26_v1___2 Group Counseling
3 t26_v1___3 Smartphone app
4 t26_v1___4 In person individual counseling
5 t26_v1___5 Helpline phone counseling
6 t26_v1___6 None of the above

Where multiple answers are possible and t26_v1___1 - t26_v1___6 are dummy variables.

On 2021-06-30 the QDS survey was changed to be more like the REDCap survey. The QDS data now has T26A_V1, T26A_V1A, T26A_V1B, T26A_V1C, T26A_V1D, T26A_V1E, and T26A_V1F that correspond to t26_v1___1 - t26_v1___6 in REDCap.

Remember that because of a naming error with T3B_V1, T26_V1 was already manually changed to T27 in the codebook by MBC. Changing "T26_V1" (the name that appears in the outdated codebook) to "T26A_V1" (the name that actually appears in the data frame now).

We manually make these changes in the code chunk below. 

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
# paste(word_cb_secs_cols_list[[1]][["copy_and_paste"]], collapse = ", ")
```

```{r}
v1_test <- v1 %>% 
  select(
    TODAY_V1, VISIT_TYPE, II_V1, VISIT_V1, TEST_V1, 
    
    # Add intuitive names to the screening question (demographic) variables
    GENDER, sq_hispanic = SQ_2, sq_race = SQ_3, sq_age = SQ_4, SQ_5, SQ_6, SQ_7, 
    SQ_7A, SQ_7B, SQ_7C, SQ_7D, SQ_8, SQ_9, SQ_9L, SQ_10, SQ_11, SQ_12, SQ_13, 
    SQ_14, SQ_15, SQ_16, SQ_17, SQ_18, SQ_18A, SQ_18B, SQ_18C, SQ_18D, SQ_18E, 
    SQ_18F, SQ_18G, SQ_18H, SQ_18I, SQ_19, SQ_20, SQ_21, SQ_22, SQ_22A, SQ_22B, 
    SQ_22C, SQ_22D, SQ_22E, SQ_22F, SQ_22G, SQ_22H,
    
    # Changes to MMSE column names
    # In visit 1, the MMSE questions go MMS_4, MMS_4A-MMS_4F, COUNT, MMS4V, 
    # MMS4VA-MMS4VF, NUM, MMS_5. However, MMS4V should have been MMS_5 and 
    # MMS_5 should have been MMS_6, etc. This proliferates all the way down 
    # the questions. We need to fix these before the standardization process.

    # Better to do this now because after standardize_col_names you can no 
    # longer cut and paste from the Word codebooks. Also, it becomes difficult 
    # to be sure which variables in the data correspond to which variables in 
    # the codebook (e.g., "mms_4" and "mms_4v").

    # Additionally, I'm going to add the section name (mms) in front of some of 
    # the column names that don't include it. For example, RECAL1 to mms_recall1.
    MMS_1A, MMS_1B, MMS_1C, MMS_1D, MMS_1E, MMS_1, MMS_2A, MMS_2B, MMS_2C, MMS_2D, 
    MMS_2E, MMS_2, MMS_3, MMS_3G, MMS_3H, MMS_3I, MMS_3J, 
    mms_recall_1 = RECAL1, 
    MMS_4, MMS_4A, MMS_4B, MMS_4C, MMS_4D, MMS_4E, MMS_4F, 
    mms_count = COUNT, 
    mms_5 = MMS4V, 
    mms_5a = MMS4VA, 
    mms_5b = MMS4VB, 
    mms_5c = MMS4VC, 
    mms_5d = MMS4VD, 
    mms_5e = MMS4VE, 
    mms_5f = MMS4VF, 
    mms_num = NUM, 
    mms_6 = MMS_5, 
    mms_6a = MMS_5A, 
    mms_6b = MMS_5B, 
    mms_6c = MMS_5C, 
    mms_6d = MMS_5D, 
    mms_recall_2 = RECAL2, 
    mms_7 = MMS_6, 
    mms_7a = MMS_6A, 
    mms_7b = MMS_6B, 
    mms_7c = MMS_6C, 
    mms_object = OBJECT, 
    mms_8 = MMS_7, 
    mms_9 = MMS_8, 
    mms_9a = MMS_8A, 
    mms_9b = MMS_8B, 
    mms_9c = MMS_8C, 
    mms_9d = MMS_8D, 
    mms_paper = PAPER, 
    mms_10 = MMS_9, 
    mms_11 = MMS_10, 
    mms_12 = MMS_11, 
    MMS_S, 
   
    # Realm  
    REALM, 
    realm_a = REALMA, 
    realm_b = REALMB, 
    realm_c = REALMC, 
    realm_d = REALMD, 
    realm_e = REALME, 
    realm_f = REALMF, 
    realm_g = REALMG, 
    realm_h = REALMH, 
    realm_i = REALMI, 
    realm_total = REALM_S,  
   
    # Biological/Anthropometric Measures
    SQ_23, SUBJECT, WEIGHT, HEIGHT, WAIST_C, CO_V1, READ1_V1, READ2_V1, 
    read_3 = READ3_V5, CTIME_V1,
    
    # Demographic/Background Information Questionnaire
    # Use intuitive names for many of these variables.
    # Also, demo_16g was incorrectly numbered when the data was created.
    dem_marital_status = DEM1V1, 
    dem_children = DEM2V1, 
    dem_race = DEM3V1, 
    dem_race_mult_n = DEM4V1, 
    dem_race_mult_white = DEM4V1A, 
    dem_race_mult_black = DEM4V1B, 
    dem_race_mult_asian = DEM4V1C, 
    dem_race_mult_pacific = DEM4V1D, 
    dem_race_mult_native = DEM4V1E, 
    dem_race_mult_other = DEM4V1F, 
    dem_edu_20_cat = DEM5V1, 
    dem_edu_ged = DEM5AV1, 
    dem_employ_status = DEM6V1, 
    dem_employ_hpw = DEM6AV1, 
    dem_employ_7days = DME6BV1, 
    dem_ins = DEM7V1, 
    dem_ins_medicare = DEM7V1A, 
    dem_medicaid = DEM7V1B, 
    dem_ins_military = DEM7V1C, 
    dem_ins_private = DEM7V1D, 
    dem_ins_none = DEM7V1E, 
    dem_social_security = DEM8V1, 
    dem_social_security_amount = DEM9V1, 
    dem_snap = DEM10V1, 
    dem_snap_amount = DEM11V1,
    dem_income_source = DEM12V1, 
    dem_income_source_work = DEM12V1A, 
    dem_income_source_criminalized = DEM12V1B, 
    dem_income_source_disability = DEM12V1C, 
    dem_income_source_emp_benefits = DEM12V1D, 
    dem_income_source_self_emp = DEM12V1E, 
    dem_income_source_sex = DEM12V1F, 
    dem_income_source_drugs = DEM12V1G, 
    dem_income_source_social_assistance = DEM12V1H, 
    dem_income_source_student_loans = DEM12V1I, 
    dem_income_source_friends_relatives = DEM12V1J, 
    dem_income_source_other = DEM12V1K, 
    dem_income_source_none = DEM12V1L, 
    dem_income_12_mnth_8_cat = DEM13V1, 
    DEM13AV1, DEM13BV1, DEM13CV1, DEM13DV1, DEM13EV1, DEM13FV1, DEM13GV1, DEM13HV1, 
    dem_income_1_mnth_7_cat = DEM14V1, DEM14AV1, DEM14BV1, DEM14CV1, DEM14DV1, 
    DEM14EV1, DEM14FV1, 
    dem_14g = DEMO16G, 
    dem_veteran = DEM15V1, 
    DEM16V1, 
    dem_sexual_orientation = DEM17V1, 
    dem_transgender = DEM18V1,
   
    # The Brief Homelessness Questionnaire
    # Remove the extra "A" from several names (e.g., BH12AV1)
    # Renumber starting at BH13BV1. BH13BV1, BH13BV1, and BH13CV1 all ask people 
    # if they've been arrested for various things. Ideally, this should have
    # been one long question, but it wasn't. I don't like the idea of having
    # bh_13aa, bh_13ba, bh_13ca, etc. Because the answer choices are all 
    # entirely different, I'm going to treat these as separate questions and 
    # renumber them.
    BH1V1, BH1V1Y, BH1V1M, BH1V1D, BH2V1, BH3V1, BH4V1, BH4V1Y, BH4V1M, BH4V1D, 
    BH5V1, BH6V1, BH7V1, BH7V1Y, BH7V1M, BH7V1W, BH8V1, BH9V1, BH10V1, 
    bh_11 = BH11AV1, 
    bh_12 = BH12AV1, 
    bh_12a = BH12AV1A, 
    bh_12b = BH12AV1B, 
    bh_12c = BH12AV1C, 
    bh_12d = BH12AV1D, 
    bh_12e = BH12AV1E, 
    bh_12f = BH12AV1F, 
    bh_12g = BH12AV1G, 
    bh_12h = BH12AV1H, 
    bh_12i = BH12AV1I, 
    bh_12j = BH12AV1J, 
    bh_12k = BH12AV1K, 
    bh_12l = BH12AV1L, 
    bh_13 = BH13AV1, 
    bh_13a = BH13AV1A, 
    bh_13b = BH13AV1B, 
    bh_13c = BH13AV1C, 
    bh_13d = BH13AV1D, 
    bh_13e = BH13AV1E, 
    bh_13f = BH13AV1F, 
    bh_14 = BH13BV1, 
    bh_14a = BH13BV1A, 
    bh_14b = BH13BV1B, 
    bh_14c = BH13BV1C, 
    bh_14d = BH13BV1D, 
    bh_14e = BH13BV1E, 
    bh_14f = BH13BV1F, 
    bh_14g = BH13BV1G, 
    bh_14h = BH13BV1H, 
    bh_15 = BH13CV1, 
    bh_15a = BH13CV1A, 
    bh_15b = BH13CV1B, 
    bh_15c = BH13CV1C, 
    bh_15d = BH13CV1D, 
    bh_15e = BH13CV1E, 
    bh_15f = BH13CV1F, 
    bh_15g = BH13CV1G, 
    bh_15h = BH13CV1H, 
    bh_16 = BH14V1, 
    bh_17 = BH14BV1, 
    bh_18y = BH14BV1Y, 
    bh_18m = BH14BV1M, 
    bh_18w = BH14BV1W,
    bh_19 = BH15V1, 
    bh_20 = BH15AV1, 
    bh_21 = BH16V1, 
    bh_22 = BH17V1, 
    bh_22y = BH17V1Y, 
    bh_22m = BH17V1M, 
    bh_22w = BH17V1W, 
    bh_23 = BH18V1, 
    bh_24 = BH18BV1, 
    bh_24a = BH18BV1A, 
    bh_24b = BH18BV1B, 
    bh_24c = BH18BV1C, 
    bh_24d = BH18BV1D, 
    bh_24e = BH18BV1E, 
    bh_24f = BH18BV1F, 
    bh_24g = BH18BV1G, 
    bh_24h = BH18BV1H, 
    bh_24i = BH18B1V1, 
    bh_25 = BH19V1, 
    bh_26 = BH20V1, 
   
    # MacArthur Scale of Subjective Social Status
    SSS1_V1, SSS2_V1,
   
    # Patient Health Questionnaire
    PHQ1_V1, PHQ2_V1, PHQ3_V1, PHQ4_V1, PHQ5_V1, PHQ6_V1, PHQ7_V1, PHQ8_V1, 
    PHQ9_V1, PHQ10_V1, PHQ11_V1, PHQ12_V1, PHQ13_V1, PHQ14_V1, PHQ15_V1,
   
    # SF-12 Health Survey
    HS1_V1, HS2_V1, HS3_V1, HS4_V1, HS5_V1, HS6_V1, HS7_V1, HS8_V1, HS9_V1, 
    HS10_V1, HS11_V1, HS12_V1,
   
    # Health Related Quality of Life
    HRQ1_V1, HRQ2_V1, HRQ3_V1,
   
    # Self-Rated Health Questionnaire
    # The numbering and naming convention in this section gets pretty messed up 
    # below. Since I already have to retype the name of some many of these, I’m 
    # going to go ahead and give these a better name from the beginning. This 
    # questionnaire is also used in v3, v4, v5
    srh_1 = S2_V1, 
    srh_1a = S2_V1A, 
    srh_1b = S2_V1B, 
    srh_1c = S2_V1C, 
    srh_1d = S2_V1D, 
    srh_1e = S2_V1E, 
    srh_1f = S2_V1F, 
    srh_1g = S2_V1G, 
    srh_1h = S2_V1H, 
    srh_2a = SR3A_V1, 
    srh_2b = SR3B_V1, 
    srh_2c = SR3C_V1, 
    srh_2d = SR3D_V1,
    srh_2e = SR3E_V1,
    srh_2f = SR3F_V1,
    srh_3 = S3_V1,
    srh_4 = S4_V1,
    srh_5a = S4_V1A,
    srh_5b = S4_V1B,
    srh_5c = S4_V1C,
    srh_5d = S4_V1D,
    srh_5e = S4_V1E,
    srh_5f = S4_V1F,
    srh_5g = S4_V1G,
    srh_5h = S4_V1H,
    srh_5 = S5_V1,
    srh_6 = S6_V1,
    srh_7 = S7_V1,
    srh_7a = S7_V1A,
    srh_7b = S7_V1B,
    srh_7c = S7_V1C,
    srh_7d = S7_V1D,
    srh_7e = S7_V1E,
    srh_7f = S7_V1F,
    srh_7g = S7_V1G,
    srh_8 = S8_V1,
    srh_8a = S8_V1A,
    srh_8b = S8_V1B,
    srh_8c = S8_V1C,
    srh_8d = S8_V1D,
    srh_8e = S8_V1E,
    srh_8f = S8_V1F,
    srh_8g = S8_V1G,
    srh_9 = S9_V1,
    srh_9a = S9_V1A,
    srh_9b = S9_V1B,
    srh_9c = S9_V1C,
    srh_9d = S9_V1D,
    srh_9e = S9_V1E,
    srh_9f = S9_V1F,
    srh_9g = S9_V1G,
    srh_9h = S9_V1H,
    srh_9i = S9_V1I,
    srh_9j = S9_V1J,
    srh_9k = S9_V1K,
    srh_9l = S9_V1L,
    srh_9m = S9_V1M,
    srh_9n = S9_V1N,
    srh_9o = S9_V1O,
    srh_9p = S9_V1P,
    srh_9q = S9_V1Q,
    srh_9r = S9_V1R,
    srh_10 = S10_V1,
    srh_11 = S11_V1,
    srh_12 = S12_V1,
    srh_13 = S13_V1,
    srh_14 = S14_V1,
    srh_14a = S14_V1A,
    srh_14b = S14_V1B,
    srh_14c = S14_V1C,
    srh_14d = S14_V1D,
    srh_15 = S15_V1,
    srh_16 = S16_V1,
    srh_17 = S17_V1,
    srh_18 = S18_V1,
    srh_18a = S18_V1A,
    srh_18b = S18_V1B,
    srh_18c = S18_V1C,
    srh_18d = S18_V1D,
    srh_18e = S18_V1E,
    srh_18f = S18_V1F,
    srh_18g = S18_V1G,
    srh_18h = S18_V1H,
    srh_18i = S18_V1I,
    srh_18j = S18_V1J,
    srh_18k = S18_V1K,
    srh_18l = S18_V1L,
    srh_19 = S19_V1,
    srh_20 = S20_V1,
    srh_21 = S21_V1,
    srh_22 = S22_V1,
    srh_23 = S23_V1,
    srh_24 = S24_V1,
    srh_24a = S24_V1A,
    srh_24b = S24_V1B,
    srh_24c = S24_V1C,
    srh_24d = S24_V1D,
    srh_24e = S24_V1E,
    srh_24f = S24_V1F,
    srh_25 = S25A_V1,
    srh_26 = S26A_V1,
    srh_26a = S26A_V1A,
    srh_26b = S26A_V1B,
    srh_26c = S26A_V1C,
    srh_26d = S26A_V1D,
    srh_26e = S26A_V1E,
    srh_26f = S26A_V1F,
    srh_26g = S26A_V1G,
    srh_27 = S25B_V1,
    srh_28 = S26B_V1,
    srh_28a = S26B_V1A,
    srh_28b = S26B_V1B,
    srh_28c = S26B_V1C,
    srh_28d = S26B_V1D,
    srh_28e = S26B_V1E,
    srh_28f = S26B_V1F,
    srh_28g = S26B_V1G,
    srh_29 = S25C_V1,
    srh_30 = S26C_V1,
    srh_30a = S26C_V1A,
    srh_30b = S26C_V1B,
    srh_30c = S26C_V1C,
    srh_30d = S26C_V1D,
    srh_30e = S26C_V1E,
    srh_30f = S26C_V1F,
    srh_30g = S26C_V1G,
    srh_31 = S25D_V1,
    srh_32 = S26D_V1,
    srh_32a = S26D_V1A,
    srh_32b = S26D_V1B,
    srh_32c = S26D_V1C,
    srh_32d = S26D_V1D,
    srh_32e = S26D_V1E,
    srh_32f = S26D_V1F,
    srh_32g = S26D_V1G,
    srh_33 = S25E_V1,
    srh_34 = S26E_V1,
    srh_34a = S26E_V1A,
    srh_34b = S26E_V1B,
    srh_34c = S26E_V1C,
    srh_34d = S26E_V1D,
    srh_34e = S26E_V1E,
    srh_34f = S26E_V1F,
    srh_34g = S26E_V1G,
    srh_35 = S27_V1,
    srh_36 = S28_V1,
    srh_37 = S29_V1,
    srh_38 = S30_V1,
    srh_38a = S30_V1A,
    srh_38b = S30_V1B,
    srh_38c = S30_V1C,
    srh_38d = S30_V1D,
    srh_38e = S30_V1E,
    srh_38f = S30_V1F,
    srh_38g = S30_V1G,
    srh_39 = S31_V1,
    srh_40 = S32_V1,
    srh_40a = S32_V1A,
    srh_40b = S32_V1B,
    srh_40c = S32_V1C,
    srh_40d = S32_V1D,
    srh_40e = S32_V1E,
    srh_40f = S32_V1F,
    srh_40g = S32_V1G,
    srh_40h = S32_V1H,
    srh_40i = S32_V1I,
    srh_41 = S33_V1,
    srh_42 = S34_V1,
    srh_43 = S35_V1,
    srh_44 = S36_V1,
    srh_45 = S37_V1,
    srh_46 = S38_V1,
    srh_47 = S39A_V1,
    srh_48 = S39B_V1,
    srh_49 = S40_V1,
    srh_50 = S41_V1,
    srh_51 = S42_V1,
    srh_52 = S43_V1,
    srh_52a = S43_V1A,
    srh_52b = S43_V1B,
    srh_52c = S43_V1C,
    srh_52d = S43_V1D,
    srh_52e = S43_V1E,
    srh_52f = S43_V1F,
    srh_52g = S43_V1G,
    srh_52h = S43_V1H,
    srh_52i = S43_V1I,
   
    # PTSD Screen
    PTSD1_V1, PTSD2_V1, PTSD3_V1, PTSD4_V1,
   
    # Tobacco History Questionnaire
    # T3B_V1 should really be t4. This throws off the numbering all the way 
    # through the questionnaire.
    # On 2021-06-30 the QDS survey was changed to be more like the REDCap survey. 
    # Explained above
    T1_V1, T2_V1, 
    t_3 = T3A_V1,
    t_3y = T3A_V1Y,
    t_3m = T3A_V1M,
    t_4 = T3B_V1,
    t_5 = T4_V1,
    t_6 = T5_V1,
    t_6a = T5A1_V1,
    t_6b = T5A2_V1,
    t_6c = T5A3_V1,
    t_6d = T5A4_V1,
    t_6e = T5A5_V1,
    t_6f = T5A6_V1,
    t_7 = T6_V1,
    t_7a = T6A1_V1,
    t_7b = T6A2_V1,
    t_7c = T6A3_V1,
    t_7d = T6A4_V1,
    t_7e = T6A5_V1,
    t_7f = T6A6_V1,
    t_8 = T7_V1,
    t_9 = T8_V1,
    t_10 = T9_V1,
    t_11 = T10_V1,
    t_12 = T11_V1,
    t_13 = T12_V1,
    t_13a = T12A_V1,
    t_13b = T12B_V1,
    t_14 = T13_V1,
    t_15 = T14_V1,
    t_15a = T14_V1A,
    t_15b = T14_V1B,
    t_15c = T14_V1C,
    t_15d = T14_V1D,
    t_15e = T14_V1E,
    t_15f = T14_V1F,
    t_15g = T14_V1G,
    t_15h = T14_V1H,
    t_15i = T14_V1I,
    t_16 = T15_V1,
    t_17 = T16_V1,
    t_18 = T17_V1,
    t_19 = T18_V1,
    t_20 = T19_V1,
    t_21 = T20_V1,
    t_22 = T21_V1,
    t_23 = T22_V1,
    t_24 = T23_V1,
    t_24a = T23_V1A,
    t_24b = T23_V1B,
    t_24c = T23_V1C,
    t_24d = T23_V1D,
    t_24e = T23_V1E,
    t_24f = T23_V1F,
    t_24g = T23_V1G,
    t_24h = T23_V1H,
    t_25 = T24_V1,
    t_26 = T25_V1,
    t_27 = T26A_V1,
    t_27a = T26A_V1A,
    t_27b = T26A_V1B,
    t_27c = T26A_V1C,
    t_27d = T26A_V1D,
    t_27e = T26A_V1E,
    t_27f = T26A_V1F,
    t_28 = T27_V1,
    t_29 = T28_V1,
    t_30 = T29_V1,
    t_31 = T30_V1,
    t_32 = T31_V1,
    t_32a = T31_V1A,
    t_32b = T31_V1B,
    t_32c = T31_V1C,
    t_32d = T31_V1D,
    t_32e = T31_V1E,
    t_32f = T31_V1F,
    t_32g = T31_V1G,
    t_32h = T31_V1H,
    t_32i = T31_V1I,
    t_32j = T31_V1J,
    t_33 = T31B_V1,
    t_33a = T31B_V1A,
    t_33b = T31B_V1B,
    t_33c = T31B_V1C,
    t_34 = T32_V1,
    t_35 = T33_V1,
    t_35a = T33_V1A,
    t_35b = T33_V1B,
    t_35c = T33_V1C,
    t_35d = T33_V1D,
    t_35e = T33_V1E,
    t_35f = T33_V1F,
    t_35g = T33_V1G,
    t_35h = T33_V1H,
    t_35i = T33_V1I,
    t_35j = T33_V1J,
    t_36 = T34_V1,
    t_37 = T35_V1,
    t_38 = T36_V1,
    t_39 = T37_V1,
    t_40 = T38_V1,
    t_41 = T39_V1,
    t_42 = T40_V1,
   
    # Heaviness of Smoking Index
    HSI1_V1, HSI2_V1,
   
    # BRFSS - Inadequate Sleep
    BRS1_V1, BRS2_V1, BRS3_V1, BRS4_V1, BRS5_V1,
   
    # Alcohol Quantity, Frequency and Binge Drinking Questionnaire
    AF1_V1, AF2M_V1, AF3TU_V1, AF4W_V1, AF5TH_V1, AF6F_V1, AF6SA_V1, AF8SU_V1, 
    af_drinks = DRINKS, AF9_V1, AF9A_V1, AF9B_V1, AF9C_V1,
   
    # Meal Survey
    MS1_V1, MS2_V1, MS3_V1, ms_4 = MS8_V1,
   
    # Sexual Behaviors
    SB1_V1, SB2_V1, SB3_V1, SB4_V1, SB5_V1, SB6_V1, SB7_V1, SB7_V1A, SB7_V1B, 
    SB7_V1C, SB7_V1D, SB7_V1E, SB7_V1F, SB7_V1G, SB8_V1, SB9_V1,
   
    # Detroit Day Discrimination
    DD1_V1, DD2_V1, DD3_V1, DD4_V1, DD5_V1, DD6_V1, DD7_V1, DD8_V1, DD9_V1, 
    DD10_V1,
   
    # Aggression Questionnaire
    AQ1_V1, AQ2_V1, AQ3_V1, AQ4_V1, AQ5_V1, AQ6_V1, AQ7_V1, AQ8_V1, AQ9_V1, 
    AQ10_V1, AQ11_V1, AQ12_V1,
   
    # CES-D
    CES1_V1, CES2_V1, CES3_V1, CES4_V1, CES5_V1, CES6_V1, CES7_V1, CES8_V1, 
    CES9_V1, CES10_V1,
   
    # Interpersonal Support Evaluation List
    IS1_V1, IS2_V1, IS3_V1, IS4_V1, IS5_V1, IS6_V1, IS7_V1, IS8_V1, IS9_V1, 
    IS10_V1, IS11_V1, IS12_V1,
   
    # Religious Participation
    RP1_V1, RP2_V1,
   
    # Lubben Social Network Scale
    LSN1_V1, LSN2_V1, LSN3_V1, LSN4_V1, LSN5_V1, LSN6_V1,
   
    # Resource Utilization
    R1_V1, R2_V1, R3_V1, R4_V1, R5_V1, R6_V1, R7_V1, R8_V1, R9_V1, R10_V1, 
    R11_V1, 
    r_12 = R11B_V1, 
    r_13 = R12_V1, 
    r_14 = R13_V1, 
    r_15 = R14_V1, 
    r_16 = R15_V1, 
    r_16a = R15_V1A, 
    r_16b = R15_V1B, 
    r_16c = R15_V1C, 
    r_16d = R15_V1D, 
    r_16e = R15_V1E, 
    r_16f = R15_V1F, 
    r_16g = R15_V1G, 
    r_16h = R15_V1H, 
    r_16i = R15_V1I, 
    r_16j = R15_V1J, 
    r_16k = R15_V1K, 
    r_16l = R15_V1L, 
    r_16m = R15_V1M, 
    r_16n = R15_V1N, 
    r_16o = R15_V1O,
   
    # Barriers to Phone Based Case Management
    BPM1_V1, BPM2_V1, BPM3_V1, BPM4_V1, BPM5_V1, BPM5_V1A, BPM5_V1B, BPM5_V1C, 
    BPM5_V1D, BPM5_V1E, BPM5_V1F, BPM5_V1G, endtime = ENDTIME1, ETIME_V1,
   
    # Add everything() to make sure no columns are lost. Many of these will be
    # calculated variables from the SPSS script. 
    everything()
)
```


### v2: Reorder columnn names and manual changes

**Change log:**

On 2021-06-10, VISIT_TYPE was added to QDS.

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
# paste(word_cb_secs_cols_list[[2]][["copy_and_paste"]], collapse = ", ")
```

```{r}
v2_test <- v2 %>% 
  select(
    TODAY_V2, VISIT_TYPE, II_V2, SUBJECT, VISIT_V2, TEST_V2, READ1_V2, READ2_V2, 
    READ3_V2, CTIME_V2,
    
    # TCU Drug Screen 5
    DS1_V2, DS2_V2, DS3_V2, DS4_V2, DS5_V2, DS6_V2, DS7_V2, DS8_V2, DS9_V2, 
    DS10A_V2, DS10B_V2, DS11A_V2, DS11B_V2, 
    
    # BRFSS Adverse Childhood Experience (ACE) Model
    BRAC1, BRAC2, BRAC3, BRAC4, BRAC5, BRAC6, BRAC7, BRAC8, BRAC9, BRAC10, BRAC11, 
    
    # Personality Beliefs Questionnaire-Short Form- Antisocial Beliefs
    PBQ1, PBQ2, PBQ3, PBQ4, PBQ5, PBQ6, PBQ7, 
    
    # Food Security
    FSS1_V2, FSS2_V2, FSS3_V2, FSS3A_V2, FSS4_V2, FSS5_V2, 
    
    # TCU CJ Client Evaluation of Self and Treatment
    CJ1_V2, CJ2_V2, CJ3_V2, CJ4_V2, CJ5_V2, CJ6_V2, CJ7_V2, CJ8_V2, CJ9_V2, 
    CJ10_V2, CJ11_V2, CJ12_V2, CJ13_V2, CJ14_V2, CJ15_V2, CJ16_V2, CJ17_V2, 
    CJ18_V2, CJ19_V2, CJ20_V2, CJ21_V2, CJ22_V2, CJ23_V2, CJ24_V2, CJ25_V2, 
    CJ26_V2, CJ27_V2, CJ28_V2, CJ29_V2, CJ30_V2, CJ31_V2, CJ32_V2, CJ33_V2, 
    CJ34_V2, CJ35_V2, CJ36_V2, CJ37_V2, CJ38_V2, CJ39_V2, CJ40_V2, 
    
    # MacArthur Major Discrimination
    MMD1A, MMD1B, MMD1C, MMD1D, MMD1E, MMD1F, MMD1G, MMD1H, MMD1I, MMD1J, MMD1K, 
    MMD2, MMD3, MMD4, 
    
    # Urban Life Stressor Scale
    ULS1_V2, ULS2_V2, ULS3_V2, ULS4_V2, ULS5_V2, ULS6_V2, ULS7_V2, ULS8_V2, 
    ULS9_V2, ULS10_V2, ULS11_V2, ULS12_V2, ULS13_V2, ULS14_V2, ULS15_V2, 
    ULS16_V2, ULS17_V2, ULS18_V2, ULS19_V2, ULS20_V2, ULS21_V2, 
    
    # Personal Victimization
    pv_1 = PV1_V2, pv_2 = PV2_V2, pv_3 = PV3_V2, 
    
    # Perceived Stress Scale
    PS1_V2, PS2_V2, PS3_V2, PS4_V2, 
    
    # Distress Tolerance Scale
    DTS1_V2, DTS2_V2, DTS3_V2, DTS4_V2, DTS5_V2, DTS6_V2, DTS7_V2, DTS8_V2, 
    DTS9_V2, DTS10_V2, DTS11_V2, DTS12_V2, DTS13_V2, DTS14_V2, DTS15_V2, DTS16_V2, 
    endtime = ENDTIME2, ETIME_V2,
    
    # Add everything() to make sure no columns are lost. Many of these will be
    # calculated variables from the SPSS script. 
    everything()
) %>% 
  # Drop unneeded columns
  select(-II_V1)
```


### v3: Reorder columnn names and manual changes

**Change log:**

On 2021-06-10, VISIT_TYPE was added to QDS.

On 2021-06-30 the QDS survey was changed to be more like the REDCap survey. The QDS data now has T26A_V1, T26A_V1A, T26A_V1B, T26A_V1C, T26A_V1D, T26A_V1E, and T26A_V1F that correspond to t26_v1___1 - t26_v1___6 in REDCap.

```{r eval=FALSE}
# This shouldn't need to be run again in the future. Just leaving it in the code to preserve an accurate history of what was done. 
# paste(word_cb_secs_cols_list[[3]][["copy_and_paste"]], collapse = ", ")
```

```{r}
v3_test <- v3 %>% 
  select(
    TODAY_V3, VISIT_TYPE, II_V3, SUBJECT, GROUP, VISIT_V3, TEST_V3, 
    
    # Biological/Anthropometric Measures
    GENDER, weight = WEIGHT_3, height = HEIGHT_3, waist_c = WAIST_C3, CO_V3, 
    READ1_V3, READ2_V3, READ3_V3, CTIME_V3, 
    
    # Demographic/Background Information Questionnaire
    # Use intuitive names for many of these variables.
    dem_employ_status = DEM6V3, 
    dem_employ_hpw = DEM6AV3,
    dem_employ_7days = DME6BV3,
    dem_ins = DEM7V3,
    dem_ins_medicare = DEM7V3A,
    dem_medicaid = DEM7V3B,
    dem_ins_military = DEM7V3C,
    dem_ins_private = DEM7V3D,
    dem_ins_none = DEM7V3E,
    dem_social_security = DEM8V3,
    dem_social_security_amount = DEM9V3,
    dem_snap = DEM10V3,
    dem_snap_amount = DEM11V3,
    dem_income_source = DEM12V3,
    dem_income_source_work = DEM12V3A,
    dem_income_source_criminalized = DEM12V3B,
    dem_income_source_disability = DEM12V3C,
    dem_income_source_emp_benefits = DEM12V3D,
    dem_income_source_self_emp = DEM12V3E,
    dem_income_source_sex = DEM12V3F,
    dem_income_source_drugs = DEM12V3G,
    dem_income_source_social_assistance = DEM12V3H,
    dem_income_source_student_loans = DEM12V3I,
    dem_income_source_friends_relatives = DEM12V3J,
    dem_income_source_other = DEM12V3K,
    dem_income_source_none = DEM12V3L,
    dem_income_1_mnth_7_cat = DEM14V3,
    dEM14AV3,
    dEM14BV3,
    dEM14CV3,
    dEM14DV3,
    dEM14EV3,
    dEM14FV3,
    dEM14GV3,
   
    # The Brief Homelessness Questionnaire
    BH8V3, BH9V3, BH10V3, 
    bh_11 = BH11AV3, 
    bh_16 = BH14V3, 
    bh_17 = BH14BV3, 
    bh_18y = BH14BV1Y, 
    bh_18m = BH14BV3M, 
    bh_18w = BH14BV3W,
    bh_18d = BH14BV3D, # Left off here... Move down from v1
    BH18V3, BH18BV3, BH18BV3A, BH18BV3B, BH18BV3C, BH18BV3D, BH18BV3E, BH18BV3F, BH18BV3G, BH18BV3H, BH18B1V3, 
   
    # MacArthur Scale of Subjective Social Status
    SSS1_V3, SSS2_V3, 
   
    # Patient Health Questionnaire
    PHQ1_V3, PHQ2_V3, PHQ3_V3, PHQ4_V3, PHQ5_V3, PHQ6_V3, PHQ7_V3, PHQ8_V3, PHQ9_V3, PHQ10_V3, PHQ11_V3, PHQ12_V3, PHQ13_V3, PHQ14_V3, PHQ15_V3, 
   
    # SF-12 Health Survey 
    HS1_V3, HS2_V3, HS3_V3, HS4_V3, HS5_V3, HS6_V3, HS7_V3, HS8_V3, HS9_V3, HS10_V3, HS11_V3, HS12_V3, 
    
    # Health Related Quality of Life
    HRQ1_V3, HRQ2_V3, HRQ3_V3, 
   
    # Self-Rated Health Questionnaire
    srh_1 = S2_V3, srh_1a = S2_V3A, srh_1b = S2_V3B, srh_1c = S2_V3C, srh_1d = S2_V3D, srh_1e = S2_V3E, srh_1f = S2_V3F, srh_1g = S2_V3G, srh_1h = S2_V3H, srh_2a = SR3A_V3, srh_2b = SR3B_V3, srh_2c = SR3C_V3, srh_2d = SR3D_V3, srh_2e = SR3E_V3, srh_2f = SR3F_V3, srh_18 = S18_V3, srh_18a = S18_V3A, srh_18b = S18_V3B, srh_18c = S18_V3C, srh_18d = S18_V3D, srh_18e = S18_V3E, srh_18f = S18_V3F, srh_18g = S18_V3G, srh_18h = S18_V3H, srh_18i = S18_V3I, srh_18j = S18_V3J, srh_18k = S18_V3K, srh_18l = S18_V3L, srh_24 = S24_V3, srh_24a = S24_V3A, srh_24b = S24_V3B, srh_24c = S24_V3C, srh_24d = S24_V3D, srh_24e = S24_V3E, srh_24f = S24_V3F, srh_25 = S25A_V3, srh_26 = S26A_V3, srh_26a = S26A_V3A, srh_26b = S26A_V3B, srh_26c = S26A_V3C, srh_26d = S26A_V3D, srh_26e = S26A_V3E, srh_26f = S26A_V3F, srh_26g = S26A_V3G, srh_27 = S25B_V3, srh_28 = S26B_V3, srh_28a = S26B_V3A, srh_28b = S26B_V3B, srh_28c = S26B_V3C, srh_28d = S26B_V3D, srh_28e = S26B_V3E, srh_28f = S26B_V3F, srh_28g = S26B_V3G, srh_29 = S25C_V3, srh_30 = S26C_V3, srh_30a = S26C_V3A, srh_30b = S26C_V3B, srh_30c = S26C_V3C, srh_30d = S26C_V3D, srh_30e = S26C_V3E, srh_30f = S26C_V3F, srh_30g = S26C_V3G, srh_31 = S25D_V3, srh_32 = S26D_V3, srh_32a = S26D_V3A, srh_32b = S26D_V3B, srh_32c = S26D_V3C, srh_32d = S26D_V3D, srh_32e = S26D_V3E, srh_32f = S26D_V3F, srh_32g = S26D_V3G, srh_33 = S25E_V3, srh_34 = S26E_V3, srh_34a = S26E_V3A, srh_34b = S26E_V3B, srh_34c = S26E_V3C, srh_34d = S26E_V3D, srh_34e = S26E_V3E, srh_34f = S26E_V3F, srh_34g = S26E_V3G, srh_35 = S27_V3, srh_36 = S28_V3, srh_40 = S32_V3, srh_40a = S32_V3A, srh_40b = S32_V3B, srh_40c = S32_V3C, srh_40d = S32_V3D, srh_40e = S32_V3E, srh_40f = S32_V3F, srh_40g = S32_V3G, srh_40h = S32_V3H, srh_40i = S32_V3I, srh_41 = S33_V3, srh_45 = S37_V3, srh_47 = S39A_V3, srh_48 = S39B_V3, srh_49 = S40_V3, srh_50 = S41_V3, srh_51 = S42_V3, srh_52 = S43_V3, srh_52a = S43_V3A, srh_52b = S43_V3B, srh_52c = S43_V3C, srh_52d = S43_V3D, srh_52e = S43_V3E, srh_52f = S43_V3F, srh_52g = S43_V3G, srh_52h = S43_V3H, srh_52i = S43_V3I,
   
    # Tobacco History Questionnaire
    # On 2021-06-30 the QDS survey was changed to be more like the REDCap survey. 
    # Explained above
    T1_V3, T2_V3, t_3 = T3A_V3, t_3y = T3A_V3Y, t_3m = T3A_V3M, t_4 = T3B_V3, t_6 = T5_V3, t_6a = T5A1_V3, t_6b = T5A2_V3, t_6c = T5A3_V3, t_6d = T5A4_V3, t_6e = T5A5_V3, t_6f = T5A6_V3, t_7 = T6_V3, t_7a = T6A1_V3, t_7b = T6A2_V3, t_7c = T6A3_V3, t_7d = T6A4_V3, t_7e = T6A5_V3, t_7f = T6A6_V3, t_8 = T7_V3, t_11 = T10_V3, t_17 = T16_V3, t_18 = T17_V3, t_23 = T22_V3, t_25 = T24_V3, t_26 = T25_V3, t_27 = T26A_V3, t_27a = T26A_V3A, t_27b = T26A_V3B, t_27c = T26A_V3C, t_27d = T26A_V3D, t_27e = T26A_V3E, t_27f = T26A_V3F, t_28 = T27_V3, t_29 = T28_V3, t_30 = T29_V3, t_31 = T30_V3, t_32 = T31_V3, t_32a = T31_V3A, t_32b = T31_V3B, t_32c = T31_V3C, t_32d = T31_V3D, t_32e = T31_V3E, t_32f = T31_V3F, t_32g = T31_V3G, t_32h = T31_V3H, t_32i = T31_V3I, t_32j = T31_V3J, t_33 = T31B_V3, t_33a = T31B_V3A, t_33b = T31B_V3B, t_33c = T31B_V3C, t_35 = T33_V3, t_35a = T33_V3A, t_35b = T33_V3B, t_35c = T33_V3C, t_35d = T33_V3D, t_35e = T33_V3E, t_35f = T33_V3F, t_35g = T33_V3G, t_35h = T33_V3H, t_35i = T33_V3I, t_35j = T33_V3J, t_36 = T34_V3, t_37 = T35_V3, t_38 = T36_V3, t_39 = T37_V3, t_40 = T38_V3, t_41 = T39_V3, t_42 = T40_V3,
   
    # Heaviness of Smoking Index
    HSI1_V3, hsi_2 = HSI2_V13, 
   
    # BRFSS - Inadequate Sleep
    BRS1_V3, BRS2_V3, BRS3_V3, BRS4_V3, BRS5_V3, 
   
    # Alcohol Quantity, Frequency and Binge Drinking Questionnaire
    AF1_V3, AF2M_V3, AF3TU_V3, AF4W_V3, AF5TH_V3, AF6F_V3, AF6SA_V3, AF8SU_V3, DRINKS, AF9_V3, AF9A_V3, AF9B_V3, AF9C_V3, 
    
    # Food Security
    FSS1_V3, FSS2_V3, FSS3_V3, FSS3A_V3, FSS4_V3, FSS5_V3, 
    
    # Meal Survey
    MS1_V3, MS2_V3, MS3_V3, MS4_V3, 
    
    # Detroit Day Discrimination
    DD1_V3, DD2_V3, DD3_V3, DD4_V3, DD5_V3, DD6_V3, DD7_V3, DD8_V3, DD9_V3, DD10_V3, 
    
    # Urban Life Stressor Scale
    ULS1_V3, ULS2_V3, ULS3_V3, ULS4_V3, ULS5_V3, ULS6_V3, ULS7_V3, ULS8_V3, ULS9_V3, ULS10_V3, ULS11_V3, ULS12_V3, ULS13_V3, ULS14_V3, ULS15_V3, ULS16_V3, ULS17_V3, ULS18_V3, ULS19_V3, ULS20_V3, ULS21_V3, 
    
    # Personal Victimization
    pv_1 = PV1_V3, pv2 = PV2_V3, 
    
    # Perceived Stress Scale
    PS1_V3, PS2_V3, PS3_V3, PS4_V3, 
    
    # Aggression Questionnaire
    AQ1_V3, AQ2_V3, AQ3_V3, AQ4_V3, AQ5_V3, AQ6_V3, AQ7_V3, AQ8_V3, AQ9_V3, AQ10_V3, AQ11_V3, AQ12_V3, 
    
    # CES-D
    CES1_V3, CES2_V3, CES3_V3, CES4_V3, CES5_V3, CES6_V3, CES7_V3, CES8_V3, CES9_V3, CES10_V3, 
    
    # Interpersonal Support Evaluation List
    IS1_V3, IS2_V3, IS3_V3, IS4_V3, IS5_V3, IS6_V3, IS7_V3, IS8_V3, IS9_V3, IS10_V3, IS11_V3, IS12_V3, 
    
    # Religious Participation
    RP1_V3, RP2_V3, 
    
    # Lubben Social Network Scale
    LSN1_V3, LSN2_V3, LSN3_V3, LSN4_V3, LSN5_V3, LSN6_V3, 
    
    # Resource Utilization
    R1_V3, R2_V3, R3_V3, R4_V3, R5_V3, R6_V3, R7_V3, R8_V3, R9_V3, R10_V3, R11_V3, r_12 = R11B_V3, r_13 = R12_V3, r_14 = R13_V3, r_15 = R14_V3, r_16 = R15_V3, r_16a = R15_V3A, r_16b = R15_V3B, r_16c = R15_V3C, r_16d = R15_V3D, r_16e = R15_V3E, r_16f = R15_V3F, r_16g = R15_V3G, r_16h = R15_V3H, r_16i = R15_V3I, r_16j = R15_V3J, r_16k = R15_V3K, r_16l = R15_V3L, r_16m = R15_V3M, r_16n = R15_V3N, r_16o = R15_V3O,
    
    # Treatment Quality and Satisfaction Survey
    TQ1_1V3, TQ2_1V3, TQ14_1V3, TQ1_2V3, TQ2_2V3, TQ3_2V3, TQ4_2V3, TQ9_2V3, TQ10_2V3, TQ11_2V3, TQ12_2V3, TQ13_2V3, TQ14_2V3, TQ1_3V3, TQ2_3V3, TQ3_3V3, TQ4_3V3, TQ5_3V3, TQ6_3V3, TQ7_3V3, TQ8_3V3, TQ9_3V3, TQ10_3V3, TQ11_3V3, TQ12_3V3, TQ13_3V3, TQ14_3V3, TQ15_3V3, TQ16_3V3, TQ17_3V3, TQ18_3V3, endtime = ENDTIME3, ETIME_V3,
    
    # Add everything() to make sure no columns are lost. Many of these will be
    # calculated variables from the SPSS script. 
    everything()
)
```

## Standardize column names

* Remove _v{1, 2, 3} and v{1, 2, 3} from column names   
* Replace spaces with underscores   
* Convert to lower case   
* Add underscore in-between the abbreviated tool name and question number   

This won’t be perfect, but it will drastically reduce the number of manual changes we have to make.

```{r}
# For testing
walk(
  .x = paste0("v", 1:3, "_test"),
  .f = function(df_name) {
    df <- get(df_name, envir = .GlobalEnv)
    df <- rename_with(df, standardize_col_names)
    assign(df_name, df, envir = .GlobalEnv)
  }
)
```

```{r}
walk(
  .x = paste0("v", 1:5),
  .f = function(df_name) {
    df <- get(df_name, envir = .GlobalEnv)
    df <- rename_with(df, standardize_col_names)
    assign(df_name, df, envir = .GlobalEnv)
  }
)
```

All of the variables above will have to be investigated and fixed manually later.


# Merge visits 1 through 5

```{r}
qds_all_visits <- v1_test %>% 
  bind_rows(v2_test) %>% 
  bind_rows(v3_test) %>% 
  arrange(subject, visit)

# qds_all_visits
```

# Left off here... check the names for problems

```{r}
data.frame(names(qds_all_visits)) %>% slice(1000:1046)
```
Standard variables should end at 733, Start again at 811

Renumber the bh variables

```{r}
v1 %>% select(starts_with("bh18b"))
v3 %>% select(starts_with("bh18b"))
qds_all_visits %>% select(starts_with("bh_18b"))
```



# Additional data cleaning

* Make a couple more column name changes   
* Make id the first column   
* Carry forward time-invariant variables   
* Drop `test`. Not sure why it exists.   
* Drop `subject_1`. Not sure why it exists.   
* Move bh_14bd to behind bh_14bw

```{r}
# qds_all_visits <- 
qds_all_visits %>% 
  rename(id = subject, date_visit = today) %>% 
  select(-test, -subject_1) %>% 
  relocate(bh_14bd, .after = bh_14bw) %>% 
  select(id, everything())
```

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected columns exists in the qds_all_visits data.", {
  expect_equal(
    length(qds_all_visits),
    1046L
  )
})
```


# 💾Save the data frame

```{r}
path <- "/Volumes/Link2Care/Participant Data/R Data/qds_all_visits_import.rds"
```

```{r}
write_rds(qds_all_visits, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "QDS data saved to", path
)
```


# 🗑Clean up

```{r}
rm(list = ls())
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "QDS data imported and merged with", nrow(qds_all_visits), "rows and", ncol(qds_all_visits), "columns.\n"
)

# 2021-07-09: 2021-07-13: QDS data imported and merged with 760 rows and 1046 columns.
```

```{r echo=FALSE}
sessionInfo()
```






































# Clean variable names

_See "Notes on cleaning individual L2C data sets for merging" for the rationale, style guidelines, and instructions for this section._
  
## Extract content from Word codebook

```{r}
v1_cb_content <- read_docx("docs/codebooks/L2C_V1 Codebook.docx") %>% 
  docx_summary()
```

### Keep the variables of interest only

```{r}
v1_cb_col_names <- v1_cb_content %>%
  filter(style_name %in% c("section_name", "cb_col_name", "col_name")) %>% 
  select(doc_index, style_name:text) %>% 
  pivot_wider(
    names_from = "style_name",
    values_from = "text"
  )
```

```{r}
rm(v1_cb_content)
```

### Clean section names

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  mutate(
    # Remove "Sect-number."
    section_name = str_remove(section_name, "Sect-\\d{1,}."),
    # Remove asterisks
    section_name = str_remove_all(section_name, "\\*"),
    # Remove empty spaces
    section_name = str_trim(section_name),
    # Clean " (SQ_7 - SQ_11)" from exclusion criteria
    section_name = str_remove(section_name, " \\(SQ_7 - SQ_11\\)")
  ) %>% 
  # Fill section down across rows
  fill(section_name)
```

### Record the sections that are completed at visit 1

We will use this for checking to make sure all of the correct questionnaire sections merge later.

**NOTE:** If you rerun this section, you must run the files to clean v2-v5 again.

```{r}
q_sections <- list(v1 = unique(v1_cb_col_names$section_name))
# q_sections[["v1"]]
```

```{r}
write_rds(q_sections, "data/questionnaire_section.rds")
```

```{r}
rm(q_sections)
```

### Reduce to one row per column

Currently, cb_col_name and col_name are on separate rows. We will spread the different column names vertically across rows so that we can reduce the data frame down to one row per column.

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  # Spread cb_col_name across rows
  fill(cb_col_name) %>% 
  # Spread col_name across rows within cb_col_name
  group_by(cb_col_name) %>% 
  fill(col_name, .direction = "up") %>% 
  # # For data checking
  # filter(section_name == "Self-Rated Health Questionnaire") %>%
  # ungroup() %>%
  # slice(-1) %>%
  # summarise(
  #   length(unique(cb_col_name)),
  #   length(unique(col_name))
  # )
  group_by(cb_col_name) %>% 
  filter(row_number() == 1) %>% 
  ungroup() %>% 
  # Remove first row
  slice(-1)
```

```{r}
dim(v1_cb_col_names) # 725   4
```

### Standardize new column names

* Remove _V1 and V1 from column names
* Replace spaces with underscores
* Convert to lower case
* Add underscore in-between the abbreviated tool name and question number

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  mutate(
    # Remove _V1 from column name
    # Remove V1 at end of column name (e.g., DEM1V1)
    # Don't include values for col_name that were changed in the Word
    # document.
    col_name = if_else(
      is.na(col_name),
      str_replace(cb_col_name, "_V1|V1", ""),
      col_name
    ),
    # Replace spaces with underscores
    col_name = str_replace_all(col_name, " ", "_"),
    # Convert to lower case
    col_name = str_to_lower(col_name),
    # Add underscore in-between the abbreviated tool name and question number
    col_name = str_replace(col_name, "([a-z])(\\d)", "\\1_\\2")
  )
```

## New column: Visit type

On 2021-06-10, VISIT_TYPE was added to QDS, but not the codebook. Therefore, we will create a new row for v1_cb_col_names that will include the VISIT_TYPE variables that would have been there if it were in the codebook. 

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  add_row(
    doc_index    = NA,
    section_name = "Admin",
    cb_col_name  = "VISIT_TYPE",
    col_name     = "visit_type",
    .after       = which(v1_cb_col_names$cb_col_name == "TODAY_V1")
  )
```

## New columns: Tobacco 26 questions

On 2021-06-05, Joe Waring found a discrepancy between the way Tobacco 26 was being asked in QDS and REDCap. 

In QDS, T26_V1, T26_V3, T26_V4, and T26_V5 read:

Which option would give you the best chance for quitting smoking?
1	=	Medications
2	=	Counseling
3	=	Both medications and counseling
4	=	Smartphone app
5	=	Both smartphone app and medications
6	=	Quitting "cold turkey" - without counseling or medications
9	=	skipped

And only one answer choice was possible.

In REDCap, t26_v1 reads:

If you were to try to quit smoking, which of the following wouldyou prefer to receive: (select all that apply)

1 t26_v1___1 Medications
2 t26_v1___2 Group Counseling
3 t26_v1___3 Smartphone app
4 t26_v1___4 In person individual counseling
5 t26_v1___5 Helpline phone counseling
6 t26_v1___6 None of the above

Where multiple answers are possible and t26_v1___1 - t26_v1___6 are dummy variables.

On 2021-06-30 the QDS survey was changed to be more like the REDCap survey. The QDS data now has T26A_V1, T26A_V1A, T26A_V1B, T26A_V1C, T26A_V1D, T26A_V1E, and T26A_V1F that correspond to t26_v1___1 - t26_v1___6 in REDCap. 

These variables will not exist in the Word codebooks, so we will manually add them to v1_cb_col_names and manually make sure they follow naming conventions.

Remember that because of a naming error with T3B_V1, T26_V1 was already manually changed to T27 in the codebook by MBC. Changing "T26_V1" (the name that appears in the outdated codebook) to "T26A_V1" (the name that actually appears in the data frame now).

```{r}
v1_cb_col_names <- v1_cb_col_names %>% 
  mutate(cb_col_name = if_else(cb_col_name == "T26_V1", "T26A_V1", cb_col_name))
```

Next, create new rows for v1_cb_col_names that will add the T26 dummy variables that would have been there if the new variables were in the codebook. 

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  add_row(
    doc_index    = NA,
    section_name = "Tobacco History Questionnaire",
    cb_col_name  = c(
      "T26A_V1A", "T26A_V1B", "T26A_V1C", "T26A_V1D", "T26A_V1E", "T26A_V1F"
    ),
    col_name     = c("t_27a", "t_27b", "t_27c", "t_27d", "t_27e", "t_27f"),
    .after       = which(v1_cb_col_names$cb_col_name == "T26A_V1")
  )
```

## Check for duplicate column names

Check to make sure this process didn't accidentally create any duplicate column names

```{r}
test_that("No duplicate col_names were created in the visit 1 data.", {
  check_dup_col_name <- v1_cb_col_names %>% 
    group_by(col_name) %>% 
    filter(max(row_number()) > 1) %>% 
    pull(col_name)
  
  expect_length(check_dup_col_name, 0)
})
```

## Save column names

Save v1_cb_col_names as a key that maps the new names to the old names in case we need that information in the future. Possibly for the codebook.

**NOTE:** If you rerun this section, you must run the files to clean v2-v5 again.

```{r}
v1_col_names_key <- v1_cb_col_names %>%  
  # Drop doc_index column
  select(-doc_index) %>% 
  # Add df identifier
  mutate(df = "v1") %>% 
  select(df, everything())
```

```{r}
col_name_keys <- list(v1 = v1_col_names_key)
# col_name_keys[["v1"]]
```

```{r}
write_rds(col_name_keys, "data/col_name_keys.rds")
```

```{r}
rm(col_name_keys, v1_cb_col_names)
```

## Differences between codebook columns and data columns

Check to see what differences, if any, exist between the columns in the codebook and the columns in the actual data frame.

```{r}
in_cb_not_df <- setdiff(v1_col_names_key$cb_col_name, names(v1))
in_cb_not_df
```

There are **0** column names in the codebook that don't appear in the data.   

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected columns exist in the codebook, but not the v1 df.", {
  expect_equal(
    length(in_cb_not_df),
    0L
  )
})
```

Now, check for columns that exist in the data frame, but not the codebook.

```{r}
in_df_not_cb <- setdiff(names(v1), v1_col_names_key$cb_col_name)
# in_df_not_cb
```

Drop SUBJECT1. It's missing in every row.

```{r}
v1 <- select(v1, -SUBJECT1)
```

```{r}
in_df_not_cb <- setdiff(names(v1), v1_col_names_key$cb_col_name)
# in_df_not_cb
```

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected columns exist in the v1 df, but not the v1 codebook.", {
  expect_equal(
    length(in_df_not_cb),
    77L
  )
})
```

The remainder of these variables are calculated variables created by the SPSS export script. We will save them in a separate data frame and deal with them later. 

```{r}
v1_spss_calc_vars <- v1 %>% 
  select(id = SUBJECT, visit = VISIT_V1, all_of(in_df_not_cb))
```

```{r}
write_sav(v1_spss_calc_vars, "data/v1_spss_calc_vars.sav")
```

Remove calculated variables from the v1 data. This makes it easier to merge with the other QDS data frames later.

```{r}
v1 <- v1 %>% select(!all_of(in_df_not_cb))
```

2021-07-09: After adding visit_type and the T26 dummy variables, the expected number of columns in v1 changes from 725 to 732.

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected number of columns exist in the v1 df after cleaning.", {
  expect_equal(
    length(names(v1)),
    732L
  )
})
```

Clean up

```{r}
rm(v1_spss_calc_vars, in_cb_not_df, in_df_not_cb)
```

## Replace variable names in the full data frame

Put them in the same order used in the codebook.

```{r}
v1 <- v1 %>% 
  select(all_of(v1_col_names_key$cb_col_name))

names(v1) <- v1_col_names_key$col_name
```


# 💾Save the data frame

```{r}
path <- "/Volumes/Link2Care/Participant Data/R Data/qds_v1_import.rds"
```

```{r}
write_rds(v1, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "QDS Visit 1 saved to", path
)
```


# 🗑Clean up

```{r}
rm(v1_col_names_key, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "QDS Visit 1 cleaned with", nrow(v1), "rows and", ncol(v1), "columns.\n"
)

# 2021-07-09: QDS Visit 1 cleaned with 295 rows and 732 columns.
```

```{r echo=FALSE}
sessionInfo()
```
