---
title: "Link2Care Survey Data - Merge Survey Data"
date: "2021-04-28 <br> Updated: `r Sys.Date()`"
---

# ⭐️Overview

This file is used to merged together multiple data sets containing survey responses.

# 📦Load packages

```{r message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(purrr, warn.conflicts = FALSE)
library(testthat, warn.conflicts = FALSE)
library(stringr, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
library(haven, warn.conflicts = FALSE)
```

# 🌎Connect to UTH server 

```{bash eval=FALSE}
# Don't drill all the way down to live documents because not all of the data is in live documents.
open 'smb://islgpcifs.uthouston.edu/sph_research/Link2Care/'
```


# 📥Import data 

We previously imported and did some initial cleaning of the following data sets:

* QDS (data_survey_01_qds_import.Rmd)   
* REDCap (data_survey_06_redcap_import.Rmd)    
* Master log (data_survey_07_master_log_import.Rmd)   
* Timeline followback (data_survey_08_tlfb_import.Rmd)   
* Arrest data (data_survey_09_arrests_import.Rmd)   
* Bridge sessions data (data_survey_10_bridge_sessions_import.Rmd)   

Most of the data cleaning that was done was to standardize column names. [Click here](https://github.com/brad-cannell/link2care_public/blob/master/data/notes_cleaning_individual_data_sets_for_merge.md) for notes on column naming conventions. 

After doing this initial cleaning, the individual files were saved in RDS format on the U drive.

```{r}
path <- "/Volumes/Link2Care/Participant Data/R data/"
```

```{r}
data_frames <- c(
  qds    = "qds_all_visits_import.rds",
  rc     = "redcap_import.rds",
  ml     = "master_log_screened_in.rds",
  tlfb   = "tlfb.rds",
  arrest = "arrest.rds",
  bridge = "bridge_wide.rds"
)
```

```{r}
for (i in seq_along(data_frames)) {
  full_path <- paste0(path, data_frames[[i]])
  df_nm     <- names(data_frames)[[i]]
  df        <- read_rds(full_path)
  assign(df_nm, df, envir = .GlobalEnv)
  # Print a message for when this file is being sourced
  cat(
    paste0(Sys.Date(), ":"),
    data_frames[[i]], "imported as", df_nm, "with", nrow(df), "rows and", ncol(df), "columns.\n"
  )
}

rm(data_frames, df_nm, full_path, i, path)

# 2021-07-30: qds_all_visits_import.rds imported as qds with 1038 rows and 1046 columns.
# 2021-07-30: redcap_import.rds imported as rc with 21 rows and 911 columns.
# 2021-07-30: master_log_screened_in.rds imported as ml with 300 rows and 37 columns.
# 2021-07-30: tlfb.rds imported as tlfb with 1200 rows and 21 columns.
# 2021-07-30: arrest.rds imported as arrest with 238 rows and 8 columns.
# 2021-07-30: bridge_wide.rds imported as bridge with 300 rows and 20 columns.
```


# Remove attributes for all variables

Causes problems with `tidyr::fill()` and "Error: Can't combine `..1$hrq_1` <double> and `..2$hrq_1` <haven_labelled>."

I will almost certainly want to do something different once I start making the codebook, but for now, just remove all the attributes from all of the columns so that we can see if we can get them to bind. 

```{r}
qds_stripped <- map_df(
  .x = qds, 
  .f = function(x) {
    attributes(x) <- NULL
    x
  }
)
```

```{r}
attributes(qds_stripped$date_visit)$class <- "Date"
```

```{r}
rc_stripped <- map_df(
  .x = rc,
  .f = function(x) {
    attributes(x) <- NULL
    x
  }
)
```

```{r}
attributes(rc_stripped$date_visit)$class <- "Date"
```


# Clean group value

Group assignment from across visits can be conflicting. Additionally, group assignments between data collection instruments (i.e., QDS, REDCap, and Master Log) can be conflicting.

First, gather all of the group information from the QDS data.

```{r}
group_qds_long <- qds_stripped %>%
  select(id, group, visit) %>% 
  arrange(id, visit) %>% 
  
  # Fill values of group down within id
  group_by(id) %>% 
  tidyr::fill(group, .direction = "downup") %>% 
  
  # Now check for multiple group values within id
  mutate(mult_group = unique(group) %>% length() > 1) %>% 
  ungroup()
```

Manually review id's with multiple group values

```{r}
group_qds_long %>% 
  filter(mult_group == TRUE)
```

**NOTE on multiple groups per id:**
Manually fix group value and let James know that they need to be fixed in QDS. After they are fixed, they will no longer show up here. Still, use these notes to keep a record.

2021-01-11, From James: 
* P2057: V3 grouping entered incorrectly on QDS. Entered 'UCM' (1) instead of 'L2C' (3) 

```{r}
# Do it this way instead of with dplyr, so you don't have to mess with class
group_qds_long[group_qds_long$id == 2057, "group"] <- 3
```

Do one more check for multiple group values

Wrapping this data check in a stop function for when this file is sourced.

```{r}
# For data checks
check_qds_group_values <- group_qds_long %>% 
  group_by(id) %>% 
  # Now check for multiple group values within id
  filter(unique(group) %>% length() > 1)

if (nrow(check_qds_group_values) > 0) {
  stop("At least one participant in the QDS data is assigned to more than one group. Please investigate further in data_survey_21_merge.Rmd.")
}
```

Now, the value of group is the same in every row for each id. So, just use the first row for each id.

```{r}
group_qds <- group_qds_long %>% 
  group_by(id) %>% 
  filter(row_number() == 1) %>% 
  select(id, group) %>% 
  ungroup()
```

### REDCap: Check for differences in the REDCap data

Are the group values consistent in REDCap?

Wrapping this data check in a stop function for when this file is sourced.

```{r}
# For data checks
check_redcap_group_values <- rc_stripped %>% 
  group_by(id) %>% 
  filter(unique(group) %>% length() > 1)

if (nrow(check_redcap_group_values) > 0) {
  stop("At least one participant in the REDCap data is assigned to more than one group. Please investigate further in data_survey_21_merge.Rmd.")
}
```

Yes, so now we don't need to worry about visit number. We can just keep one row per id, and check to make sure that group in REDCap matches group in the QDS data.

```{r}
rc_id_group <- rc_stripped %>% 
  select(id, group) %>% 
  distinct(id, group)
```

Manually check for differences between group assignment in QDS and REDCap.

```{r}
rc_id_group %>% 
  left_join(
    group_qds %>% 
      select(id, group) %>% 
      # To prevent type mismatch error:
      mutate(id = as.character(id)),
    by = "id",
    suffix = c("_rc", "_qds")
  ) %>% 
  rowwise() %>% 
  filter(length(unique(c_across(group_rc:group_qds))) > 1)
```

Manually fill in data values in the QDS data.

```{r}
group_qds$group[group_qds$id == 2252] <- 2
group_qds$group[group_qds$id == 2253] <- 3
```

Wrapping this data check in a stop function for when this file is sourced.

```{r}
# For data checks
check_qds_redcap_group_diffs <- rc_id_group %>% 
  left_join(
    group_qds %>% 
      select(id, group) %>% 
      # To prevent type mismatch error:
      mutate(id = as.character(id)),
    by = "id",
    suffix = c("_rc", "_qds")
  ) %>% 
  rowwise() %>% 
  filter(length(unique(c_across(group_rc:group_qds))) > 1)

if (nrow(check_qds_redcap_group_diffs) > 0) {
  stop("At least one participant is assigned to different groups in the QDS and REDCap data. Please investigate further in data_survey_21_merge.Rmd.")
}
```

### Master log: Supplement with Excel master log data

Manually check for differences between group assignment in QDS and master log.

Error: Can't join on `x$id` x `y$id` because of incompatible types. ℹ `x$id` is of type <character>>. ℹ `y$id` is of type <double>>.

```{r}
group_qds <- group_qds %>% 
  mutate(id = as.character(id))
```

```{r}
check_qds_ml_group_diffs <- ml %>%
  left_join(
    group_qds %>% 
      select(id, group),
    by = "id",
    suffix = c("_ml", "_qds")
  ) %>% 
  select(id, group_ml, group_qds) %>% 
  rowwise() %>% 
  filter(length(unique(c_across(group_ml:group_qds))) > 1)
```

There are a bunch of id's with group membership data in master log, but not in QDS. Mostly, because these people haven't completed a v3 in QDS yet. We will go ahead and fill in the missing group data from the master log.

Below, we will formally check to see if there are any conflicting group values aside from group simply being missing in the QDS data. We will also wrap this data check in a stop function for when this file is sourced.

```{r}
# For data checks
check_qds_ml_group_diffs_not_na <- check_qds_ml_group_diffs %>% 
  filter(!is.na(group_qds))

if (nrow(check_qds_ml_group_diffs_not_na) > 0) {
  stop("At least one participant is assigned to different groups in the QDS and master log data. This not simply due to a missing group value in master log. Please investigate further in data_survey_21_merge.Rmd.")
}
```

Now there are no "conflicts" between group in the QDS data and group in the master log. The differences were all simply due to the fact that there is no group membership information at all in QDS for these participants. Therefore, we can just go ahead and row bind. In the future, if there are conflicts between group_diffs\$group_diffs and group_diffs\$group_qds, we will need to manage them.

```{r}
group_membership_key <- group_qds %>% 
  full_join(
    check_qds_ml_group_diffs %>% 
      select(id, group_ml),
    by = "id"
  ) %>% 
  mutate(group = if_else(is.na(group), group_ml, group)) %>% 
  select(-group_ml)
```

Make sure there are no duplicated ids in `group_membership_key` 

```{r}
if (length(unique(group_membership_key$id)) != nrow(group_membership_key)) {
  stop(
    "There are duplicate ids in `group_membership_key`. Investigate in data_survey_21_merge.Rmd"
  )
}
```

```{r}
# Clean up the data checking objects
rm(
  check_qds_group_values, check_qds_ml_group_diffs, check_qds_ml_group_diffs_not_na,
  check_qds_redcap_group_diffs, check_redcap_group_values, group_qds, group_qds_long
)
```

At this point, `group_membership_key` contains the final group value we will use for each participant. After merging all the other data sets below, we will add the corrected group membership information. 

# 🔄Merge data 

## QDS and REDCap

Error: Can't combine `..1$id` <double> and `..2$id` <character>.

Error: Can't combine `..1$af_drinks` <character> and `..2$af_drinks` <double>.

```{r}
qds_stripped <- qds_stripped %>% 
  mutate(
    id = as.character(id),
    af_drinks = as.numeric(af_drinks)
  )
```

```{r}
l2c_survey <- qds_stripped %>% 
  bind_rows(rc_stripped) %>% 
  arrange(id, visit) 
```

## Master log

Some of the information in master log is redundant.

Error: Can't join on `x$id` x `y$id` because of incompatible types. ℹ `x$id` is of type <character>>. ℹ `y$id` is of type <double>>.

Add "ml" to the beginning of every column name in the master log. This is to prevent duplicate names (e.g. `gender.x` and `gender.y` when we join below)

```{r}
ml_sub <- ml %>% 
  select(id, status, group, name_first:v5_r_completed) %>% 
  mutate(id = as.character(id)) %>% 
  rename_with(~ paste0("ml_", .x))
```

Make sure there is one row per id in master log before joining.

```{r}
test_that("Master log has one row per id", {
  rows_in_ml <- nrow(ml_sub)
  ids_in_ml <- length(unique(ml_sub$ml_id))
  expect_equal(rows_in_ml, ids_in_ml)
})
```

There are also more people in the Master log than there are in the QDS/REDCap data. This is because the Master Log is updated more frequently than the QDS/REDCap data.

Put in a check for this. If it fails, you probably need to update the Master Log import.

```{r}
test_that("There are also more people in the Master log than there are in the QDS/REDCap data.", {
  expect_true(length(unique(ml_sub$ml_id)) >= length(unique(l2c_survey$id)))
})
```

```{r}
l2c_survey <- ml_sub %>% 
  left_join(l2c_survey, by = c("ml_id" = "id")) %>% 
  rename(id = ml_id)
```

## TLFB

Error: Can't join on `x$id` x `y$id` because of incompatible types. ℹ `x$id` is of type <character>>. ℹ `y$id` is of type <double>>.

```{r}
tlfb <- tlfb %>% 
  mutate(subject = as.character(subject)) %>% 
  rename(id = subject)
```

```{r}
l2c_survey <- l2c_survey %>% 
  left_join(tlfb, by = c("id", "visit"))
```

## Arrest data 

It looks like there is only one row per id. Check to make sure this is always the case. The join below will expect this condition. 

```{r}
test_that("Arrest data has one row per id in data_survey_21_merge.Rmd", {
  expect_true(
    arrest %>% 
      summarise(one_row_per_id = nrow(.) == length(unique(subject))) %>% 
      pull() 
  )
})
```

```{r}
arrest <- arrest %>% 
  mutate(subject = as.character(subject)) %>% 
  rename(id = subject)
```

```{r}
l2c_survey <- l2c_survey %>%
  left_join(arrest, by = "id")
```

## Bridge sessions data

It looks like there is only one row per id. Check to make sure this is always the case. The join below will expect this condition. 

```{r}
test_that("Bridge session data has one row per id in data_survey_21_merge.Rmd", {
  expect_true(
    bridge %>% 
      summarise(one_row_per_id = nrow(.) == length(unique(subject))) %>% 
      pull() 
  )
})
```

```{r}
bridge <- bridge %>% 
  mutate(subject = as.character(subject)) %>% 
  rename(id = subject)
```

```{r}
l2c_survey <- l2c_survey %>%
  left_join(bridge, by = "id")
```


# Set group status

Use `group_membership_key` to set the final group status for each participant.

There should not be more ids in `group_membership_key` than `l2c_survey`. Check to make sure.

```{r}
test_that("There are not more ids in `group_membership_key` than `l2c_survey` in data_survey_01_import.Rmd", {
  expect_true(
    nrow(group_membership_key) <= length(unique(l2c_survey$id)) 
  )
})
```

```{r}
l2c_survey <- l2c_survey %>% 
  select(-group) %>% 
  left_join(group_membership_key, by = "id") %>% 
  select(id, visit, date_visit, group, everything()) %>% 
  mutate(consent_date = as.Date(consent_date))
```

Make sure we get a warning if the number of columns in `l2c_survey` changes.

```{r}
if (ncol(l2c_survey) != 1200) {
  stop(
    "The number of columns in l2c_survey is different than expected.",
    " The expected number was 1,200.",
    " The actual number was ", ncol(l2c_survey), ".",
    " Investigate in data_survey_21_merge.Rmd"
  )
}
```

# 🖨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant data cleaned with", nrow(l2c_survey), 
  "rows and", ncol(l2c_survey), "columns.\n"
)

# 2021-07-28: Bridge session long data cleaned with 2346 rows and 20 columns.
```


# 💾Save the data frame

```{r}
path <- "/Volumes/Link2Care/Participant Data/SPSS Data/combined_participant_data.sav"
```

```{r}
write_sav(l2c_survey, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant data saved to", path, "\n"
)
```

```{r}
path <- "/Volumes/Link2Care/Participant Data/R Data/combined_participant_data.rds"
```

```{r}
write_rds(l2c_survey, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant data saved to", path, "\n"
)
```


# 🗑Clean up

Don't use `rm(list = ls())` because is causes R to drop the helper functions in data_survey_21_update_all_data.Rmd

```{r}
rm(list = ls()[ls() != "source_rmd"])
```

```{r echo=FALSE}
sessionInfo()
```
