---
title: "Link2Care Survey Data - Merge Survey Data Codebook"
date: "2022-07-11 <br> Updated: `r Sys.Date()`"
---

# ⭐️Overview

This file creates a codebook for combined_participant_data.rds, which is created in `data_survey_21_merge.Rmd`.


# 📦Load packages

```{r message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(codebookr, warn.conflicts = FALSE)
install.packages("flextable")
library(shiny, warn.conflicts = FALSE)
```


# 📥Import data

* combined_participant_data.rds was created in `data_survey_21_merge.Rmd`, cleaned in `data_survey_22_calculated_columns.Rmd`.

```{r}
path <- "../Participant Data/R Data/combined_participant_data.rds"
```

```{r}
combined_participant_data <- read_rds(path)
```

# Add column attributes

```{r}
label <- function(col, label) {
  df <- get("combined_participant_data", envir = .GlobalEnv)
  attributes(df[[col]])$label <- label
  assign("combined_participant_data", df, envir = .GlobalEnv)
}
```

Find and replace

* label\(\"(\w+)\", ?(\".+\")\)
* cb_add_col_attributes(\n  \1, \n  description = \2\n) %>%\n


```{r}
combined_participant_data <- combined_participant_data %>%
  cb_add_col_attributes(
  id, 
  description = "Subject ID"
) %>%
  
cb_add_col_attributes(
  date_visit, 
  description = "Date of visit"
) %>%
  
cb_add_col_attributes(
  ml_hispanic, 
  description = "Master log hispanic"
)
```

```{r}
#PT Info
label("id", "Subject ID")
label("date_visit", "Date of visit")
label("group", "What is the participant's treatment group?")
label("ml_status","Master log status")
label("ml_gender","Master log gender")
label("ml_race","Master log race")
label("ml_hispanic","Master log hispanic")
label("ml_date_birth","Master log date of birth")
label("ml_age","Master log age")
label("ml_clincard_id","ClinCard ID")
label("ml_n_clincards","N clinicard distributed")
label("ml_phone_id","Phone ID")
label("ml_phone_number_l2c","L2C phone number")
label("ml_phone_n_distributed", "N phone distributed")
label("ml_care_manager","Care manager")
label("ml_v1","Visit 1 attended")
label("ml_v2","Visit 2 attended")
label("ml_v3","Visit 3 attended")
label("ml_v4","Visit 4 attended")
label("ml_v5","Visit 5 attended")
label("ml_v3_r_distributed","Redcap visit 3 distributed")
label("ml_v3_r_completed","Redcap visit 3 completed")
label("ml_v4_r_distributed","Redcap visit 4 distributed")
label("ml_v4_r_completed","Redcap visit 4 completed")
label("ml_v5_r_distributed","Redcap visit 5 distributed")
label("ml_v5_r_completed","Redcap visit 5 completed")
label("visit_type", "Visit Type")
label("ii","Interviewer Initials")

#Screening Questions
label("sq_age","What is your age?")
label("sq_7a","How long ago were you released from the jail?")
label("sq_7c","Other form of evidence of recent incarceration in Dallas Country Jail?")
label("sq_9l","Homeless shelters name:")
label("cell_have_f","Factor version of `do you have an active cell phone?`")
label("cell_pays_f","Factor version of `who pays for your cell phone service?`")
label("cell_talk_minutes_f","Factor version of `how many talk minutes does your plan have?`")
label("cell_smart_f","Factor version of `is your cell phone a smart phone?`")
label("cell_data_plan_f","Factor version of `does your phone service include a data plan?`")
label("cell_number_change_f","Factor version of `how many times has your phone number changed in the past year?`")
label("sq_18","Which of the following forms of media do you use?")
label("media_use_email_f","Factor version of `Email: Which of the following forms of media do you use?`")
label("media_use_facebook_f","Factor version of `Facebook: Which of the following forms of media do you use?`")
label("media_use_google_plus_f","Factor version of `Google Plus: Which of the following forms of media do you use?`")
label("media_use_twitter_f","Factor version of `Twitter: Which of the following forms of media do you use?`")
label("media_use_blogs_f","Factor version of `Blogs: Which of the following forms of media do you use?`")
label("media_use_instagram_f","Factor version of `Instagram: Which of the following forms of media do you use?`")
label("media_use_snapchat_f","Factor version of `Snapchat: Which of the following forms of media do you use?`")
label("media_use_linkedin_f","Factor version of `Linkedin: Which of the following forms of media do you use?`")
label("media_use_none_f","Factor version of `None of the above: Which of the following forms of media do you use?`")
label("access_internet_f","Factor version of `How often do you access the internet?`")
label("facebook_active_f","Factor version of `Do you have an active Facebook page?`")
label("sq_22","Which of the following forms of identification do you possess?")

#Mini-Mental Exam
label("mms_1","Score for MMS_1")
label("mms_2","Score for MMS_2")
label("mms_3","Word recall")
label("mms_recall_1","Word recall score")
label("mms_4","Ask the individual to count backwards from 100 by 7's")
label("mms_count","Number count")
label("mms_5","Please spell the word WORLD backwards")
label("mms_num","Number count 2")
label("mms_6","Earlier I told you three words. Can you name all three words?")
label("mms_recall_2","Word recall score 2 ")
label("mms_7","I am going to point to an object and ask you to name the objects")
label("mms_object","NAMING OBJECTS")
label("mms_9","Give the individual a piece of paper and ask the them to: 1) Hold the paper in their right hand 2) Fold the paper in half. 3) Put the paper on the floor.")
label("mms_paper","FOLDING PAPER")
label("mms_total","Mini Mental State Exam total Score")

#REALM (Rapid Estimate of Adult Literacy in Medicine)
label("realm","Realm")
label("realm_total","Realm total")

#Anthropometrics
label("weight_kg", "Weight in kilograms")
label("height_meter", "Height in meters")
label("height_meter_sq", "Height in meters squared")
label("bmi", "Body mass index")

#DDT
label("ddt_k","DDT K")
label("ddt_ed50","DDT ED50")

#Administrative
label("ctime","Current time")
label("endtime","End Time")
label("etime","Elapsed interview/data entry time")

#Demographic/Background Information Questionnaire
label("dem_race_mult_n","You have stated that you have more than one race. Please look at the categories below and mark the ones that best describe your race (Check all that apply)")
label("dem_ins","Do you have health insurance? Please check all that apply.")
label("dem_social_security_amount","What is the amount of Social Security benefits each month?")
label("dem_snap_amount","What is the amount of food stamps (SNAP) do you get each month?")
label("dem_income_source","What are your sources of income? (Please check all that apply).")

#Arrest
label("arrested","Have you been arrested in the past year?")
label("arrested_date_baseline","Date of baseline visit")
label("arrested_date_1","First arrest date")
label("arrested_date_2","Second arrest date")
label("arrested_date_3","Third arrest date")
label("arrested_date_4","Fourth arrest date")
label("arrested_date_5","Fifth arrest date")
label("arrested_date_6","Sixth arrest date")
label("arrested_date_7","Seventh arrest date")
label("arrested_date_8","Eighth arrest date")
label("arrested_date_9","Ninth arrest date")
label("arrested_date_10","Tenth arrest date")
label("arrested_date_11","Eleventh arrest date")
label("arrested_date_12","Twelfth arrest date")
label("arrested_num_summary","Total arrests made in the past year")

#The Brief Homelessness Questionnaire
label("homeless_time_total","What is the total amount of time you have been homeless in your lifetime? (for example 3 and a half years would be 3 years and 6 months)")
label("bh_1y","Years: What is the total amount of time you have been homeless in your lifetime? (for example 3 and a half years would be 3 years and 6 months)")
label("bh_1m","Months: What is the total amount of time you have been homeless in your lifetime? (for example 3 and a half years would be 3 years and 6 months)")
label("bh_1d","Days: What is the total amount of time you have been homeless in your lifetime? (for example 3 and a half years would be 3 years and 6 months)")
label("bh_4y","Years: How long ago did the current period of homelessness begin? (for example 3 years would be 3 years and 0 months)")
label("bh_4m","Months: How long ago did the current period of homelessness begin? (for example 3 years would be 3 years and 0 months)")
label("bh_4d","Days: How long ago did the current period of homelessness begin? (for example 3 years would be 3 years and 0 months)")
label("bh_7","How long have you been receiving services at the Bridge? (for example, 6 and a half months would be 2 weeks, 6 months, 0 years)")
label("bh_7y","Years: How long have you been receiving services at the Bridge? (for example, 6 and a half months would be 2 weeks, 6 months, 0 years)")
label("bh_7m","Months: How long have you been receiving services at the Bridge? (for example, 6 and a half months would be 2 weeks, 6 months, 0 years)")
label("bh_7w","Weeks: How long have you been receiving services at the Bridge? (for example, 6 and a half months would be 2 weeks, 6 months, 0 years)")
label("bh_11","On average, how many hours do you spend at shelters each day (counting sleep time)?")
label("bh_13","Have you ever been arrested and booked for: (Check all that apply)")
label("bh_14","Were you arrested or booked for breaking the law in the PAST MONTH?")
label("jail_lifetime_n","During your lifetime, how many separate times have you been to jail or prison?")
label("bh_18y","Years: During your most recent incarceration, how long were you in jail?")
label("bh_18m","Months: During your most recent incarceration, how long were you in jail?")
label("bh_18w","Weeks: During your most recent incarceration, how long were you in jail?")
label("bh_18d","Weeks: During your most recent incarceration, how long were you in jail?")
label("bh_22","During your lifetime, how much time have you spent in jail or prison?")
label("bh_22y","Years: During your lifetime, how much time have you spent in jail or prison?")
label("bh_22m","Months: During your lifetime, how much time have you spent in jail or prison?")
label("bh_22w","Weeks: During your lifetime, how much time have you spent in jail or prison?")
label("bh_22w","Weeks: During your lifetime, how much time have you spent in jail or prison?")
label("bh_24","What type of correctional supervision are you now under?")
label("bh_24i","If other, please specify:")

#Patient-Health Questionnaire
label("phq_dep_dichot_total","Total PHQ depression score dichotomized")
label("phq_gad","Is there generalized anxiety disorder?")
label("phq_8_gt_10_f","Factor version of PHQ 8 total score greater than 10")

#SF-12 Health Survey 
label("gen_health_f","Factor version of `in general, would you say your health is:`")
label("gen_health_dichot_f","Factor version of `self rated health fair or poor`")

#Health Related Quality of Life
label("hrq_physical_30","Factor version of `health related quality of life: physical health score`")
label("hrq_physical_30","Health related quality of life: mental health score")
label("hrq_mental_30","Health related quality of life: physical health score")
label("hrq_limit_activities_30","Health related quality of life: Limititation of activities")

#Self-Rated Health Questionnaire
label("srh_1","Which of the following apply to you? (Check all that apply)") # Remove 2a-2f
label("srh_7","Please select the Cardiovascular Diseases (heart/circulatory disease) that you have been diagnosed with. (Check all that apply)")
label("srh_8","Please select the Pulmonary Diseases (lung diseases) that you have been diagnosed with. (Check all that apply)")
label("srh_9","Please select the Cancers you have been diagnosed with? (Check all that apply)")
label("srh_14","Which of the following have you been diagnosed with? (Check all that apply)")
label("srh_18","I am currently taking medication for: (check all conditions for which you ARE taking medication)")
label("srh_24","I have a prescription for the following disorders: (check all that apply)")
label("srh_26","What were the reasons that you did not take your depression medication yesterday? (check all that apply)")
label("srh_28","What were the reasons that you did not take your Schizophrenia or Schizoaffective disorder medication yesterday? (check all that apply)")
label("srh_30","What were the reasons that you did not take your Bipolar Disorder medication yesterday? (check all that apply)")
label("srh_32","What were the reasons that you did not take your Anxiety Disorder medication yesterday? (check all that apply)")
label("srh_34","What were the reasons that you did not take your PTSD medication yesterday? (check all that apply)")
label("srh_38","Which Substance Use Disorder have you been diagnosed with? (check all that apply)")
label("srh_40","Please select all the substances that you used in the past 30 days.")
label("srh_52","What type of health related issue? (Check all types of smartphone apps that you have used)")
label("sp_app_change_behavior_f","Factor version of `Do you believe that a smartphone app can help you to change your actions or behavior?`")
label("sp_app_manage_health_f","Factor version of `Have you ever used a smartphone app to manage one or more health-related issues?`")
label("sp_app_manage_health_f","Factor version of `Have you ever used a smartphone app to manage one or more health-related issues?`")

#TCU Drug Screen 5
label("tcu_ds_total","Sum TCU Desire for help subscale (888 indicates they have not used drugs in past 12 months")
label("tcu_ds_score","Score TCU Desire for help subscale")

#PTSD Primary Care Screen (PC-PTSD)
label("ptsd_total","Sum PTSD total")

#Tobacco History 
label("t_3","How long ago did you quit smoking? (for example 3 and a half years would be 3 years and 6 months)")
label("t_3y","Years: How long ago did you quit smoking? (for example 3 and a half years would be 3 years and 6 months)")
label("t_3m","Months: How long ago did you quit smoking? (for example 3 and a half years would be 3 years and 6 months)")
label("t_4","How many years were you a smoker")
label("t_9","How many years have you smoked?")
label("t_12","At what age did you begin smoking cigarettes or cigarillos?")
label("t_15","Which of the following have you used to help you quit smoking in the past (check all that apply)?")
label("t_24","Which of these would be the hardest thing about stopping smoking? (select all that apply)")
label("t_27","If you were try to quit smoking, which of the following would you prefer to receive:")
label("t_32","Which of the following products have you tried, even just one time (click all items that you have used in the past)?")
label("t_33","You reported that you have used e-cigarettes, vapes, or other vaping devices in the past. Which of these types of devices have you used?")
label("t_35","Which of the following products have you used in the past 30 days? (Click all items that you have used in the past 30 days).")
label("t_38","During an average weekday, how many smokers are you around?")
label("t_39","During an average weekend, how many smokers are you around")
label("t_40","How many close friends do you have? It is okay to count family members if you consider them your best friends.")
label("t_41","How many of these close friends smoke?")
label("t_42","How many of your 5 best friends smoke? It is okay to count family members if you consider them your best friends.")
label("t_5val","How often do you smoke cigarettes or cigarillos?")
label("t_6val","In the last 24 hours, how many cigarettes or cigarillos have you smoked?")

#Heaviness of Smoking Index
label("hsi","Heaviness of Smoking Index score")
label("friends_smoke","Ratio of close friends who smoke for baseline")

# BRFSS (Behavioral Risk Factor Surveillance System) Inadequate Sleep
label("brs_1","During the past 30 days, for how many days have you felt you did not get enough rest or sleep?")
label("brs_2","On average, how many hours of sleep do you get in a 24-hour period? Think about the time you actually spend sleeping or napping, not just the amount of sleep you think you should get.")
label("brs_4","During the past 30 days, for about how many days did you find yourself unintentionally falling asleep during the day?")

#Alcohol Quantity and Frequency
label("af_drinks","Number of drinks based on gender")
label("alcqf","Number of days consumed alcohol based on gender")

#Alcohol and Drug TLFBs
label("total_drinks","Total drinks")
label("num_drinking_days","Number of days drinking")
label("ave_drinks_day","Average drinks per day")
label("num_alc_abstinent_days","Number of abstinent days")
label("heavy_drinking_days","Heavy drinking days")
label("greatest_drinks_1_day","Greatest number of drinks in 1 day")
label("drinks_wk","Drinks per week")
label("num_days_using_drugs","Number of days using drugs")
label("per_days_using_drugs","Percentage of days using drugs")
label("per_drug_abstinent_days","Percentage of abstinent days")
label("drug_use_days_yr","Estimated drug use days per year")
label("drug_use_days_week","Average drug use days per week")
label("num_days_homeless","Number of days homeless")

#Personality-Based Questionnaire
label("pbq_v_2_total","Personality Beliefs Questionaire-Short Form- Antisocial Beliefs visit 2 Total")

#USDA Food Security Survey
label("fss_total","Recoded food security status score total")
label("fss_3a_f","Factor version of `How often did this happen?`")
label("fss_4_f","Factor version of `In the last month, did you ever eat less than you felt you should because there wasn't enough money for food?`")
label("fss_5_f","Factor version of `In the last month, were you every hungry but didn't eat because there wasn't enough money for food.`")
label("fss_total_f","Factor version of `Recoded food security status score total`")
label("fss_score_f","Factor version of `Recoded categorization of food security`")
label("fss_score_dichotomous_f","Factor version of `Food secure or insecure`")
label("fsse_f","Factor version of `in the last month, did you ever eat less than you felt you should because there wasn't enough money for food? recoded`")
label("fssf_f","Factor version of `in the last month, were you ever hungry but didn't eat because there wasn't enough money for food. recoded`")

#Meal Survey
label("meals_eaten_yesterday_f","Factor version of `how many meals did you eat yesterday?`")
label("meals_cafeteria_24_hours_f","Factor version of `how many times in the past 24 hours have you eaten food from: The shelter cafeteria?`")
label("meals_fruit_veg_yesterday_f","Factor version of `how many servings of fruits and vegetables did you eat YESTERDAY?`")
label("meals_missed_week_f","Factor version of `how many meals have you missed in the PAST WEEK because you were unable to find food?`")

#TCU CJ Client Evaluation of Self and Treatment (CJ CEST)
label("cj_1_f","Factor version of `Have you used drugs or alcohol in the past 12 months?`")
label("cj_2_f","Factor version of `You need help in dealing with your drug or alcohol use.`")
label("cj_3_f","Factor version of `It is urgent that you find help immediately for your drug or alcohol use.`")
label("cj_4_f","Factor version of `You will give up your friends and hangouts to solve your drug or alcohol problems.`")
label("cj_5_f","Factor version of `Your life has gone out of control.`")
label("cj_6_f","Factor version of `You are tired of the problems caused by drugs or alcohol.`")
label("cj_7_f","Factor version of `You want to get your life straightened out.`")
label("cj_8_f","Factor version of `You need more help with your emotional troubles.`")
label("cj_9_f","Factor version of `You need more individual counseling sessions.`")
label("cj_10_f","Factor version of `You need more educational or vocational training services.`")
label("cj_11_f","Factor version of `You need more group counseling sessions.`")
label("cj_12_f","Factor version of `You need more medical care and services.`")
label("cj_13_f","Factor version of `Time schedules for counseling sessions at the Bridge are convenient for you.`")
label("cj_14_f","Factor version of `The Bridge expects you to learn responsibility and self-discipline.`")
label("cj_15_f","Factor version of `The Bridge expects you to learn responsibility and self-discipline.`")
label("cj_16_f","Factor version of `You are satisfied with the Bridge program.`")
label("cj_17_f","Factor version of `The staff here at the Bridge are efficient at doing their job.`")
label("cj_18_f","Factor version of `You can get plenty of personal counseling at the Bridge.`")
label("cj_19_f","Factor version of `The Bridge program location is convenient for you.`")
label("cj_20_f","Factor version of `You have much to be proud of.`")
label("cj_21_f","Factor version of `You feel like a failure.`")
label("cj_22_f","Factor version of `You wish you had more respect for yourself.`")
label("cj_23_f","Factor version of `You feel you are basically no good.`")
label("cj_24_f","Factor version of `In general, you are satisfied with yourself.`")
label("cj_25_f","Factor version of `You feel you are unimportant to others.`")
label("cj_26_f","Factor version of `You have carried weapons, like knives or guns.`")
label("cj_27_f","Factor version of `You feel a lot of anger inside you.`")
label("cj_28_f","Factor version of `You have a hot temper.`")
label("cj_29_f","Factor version of `You like others to feel afraid of you.`")
label("cj_30_f","Factor version of `You feel mistreated by other people.`")
label("cj_31_f","Factor version of `You get mad at other people easily.`")
label("cj_32_f","Factor version of `You have urges to fight or hurt others.`")
label("cj_33_f","Factor version of `Your temper gets you into fights or other trouble.`")
label("cj_34_f","Factor version of `You only do things that feel safe.`")
label("cj_35_f","Factor version of `You avoid anything dangerous.`")
label("cj_36_f","Factor version of `You are very careful and cautious.`")
label("cj_21r_f","Factor version of `You feel like a failure recoded`")
label("cj_21r","You feel like a failure recoded")
label("cj_22r_f","Factor version of `You wish you had more respect for yourself recoded`")
label("cj_22r","You wish you had more respect for yourself recoded")
label("cj_23r_f","Factor version of `You feel you are basically no good recoded`")
label("cj_23r","You feel you are basically no good recoded")
label("cj_25r_f","Factor version of `You feel you are unimportant to others recoded`")
label("cj_25r","You feel you are unimportant to others recoded")
label("cj_34r_f","Factor version of `You only do things that feel safe recoded`")
label("cj_34r","You only do things that feel safe recoded")
label("cj_35r","You avoid anything dangerous recoded")
label("cj_36r_f","Factor version of `You are very careful and cautious recoded`")
label("cj_36r","You are very careful and cautious recoded")
label("tcu_desire_v_2_total_f","Factor version of `Sum, TCU Desire for help subscale at Visit 2(888 indicates they have not used drugs in past 12 months`")
label("tcu_desire_v_2_total","Sum, TCU Desire for help subscale at Visit 2(888 indicates they have not used drugs in past 12 months")
label("tcu_tn_v_2_total","Sum, TCU Treatment needs subscale")
label("tcu_ts_v_2_total_f","Factor version of `Sum, TCU treatment satisfaction subscale`")
label("tcu_ts_v_2_total","Sum, TCU treatment satisfaction subscale")
label("tcu_rt_v_2_total_f","Factor version of `Sum, TCU risk taking subscale`")
label("tcu_rt_v_2_total","Sum, TCU risk taking subscale")
label("tcu_se_v_2_total_f","Factor version of `Sum, TCU self esteem subscale`")
label("tcu_se_v_2_total","Sum, TCU self esteem subscale")
label("tcu_hs_v_2_total_f","Factor version of `Sum, TCU hostility subscale`")
label("tcu_hs_v_2_total","Sum, TCU hostility subscale")
label("tcu_desire_v_4_total","Sum, TCU Desire for help subscale at Visit 4(888 indicates they have not used drugs in past 12 months")
label("tcu_tn_v_4_total","Sum, TCU Treatment needs subscale Visit 4")
label("tcu_ts_total","Sum, TCU hostility subscale")

#Sexual Behaviors
label("sb_2","How old were you the first time you had any kind of sex, including vaginal, anal, or oral?")
label("sb_3","In the past 12 months, with how many people have you had any kind of sex?")
label("sb_7","Has a health care professional EVER told you that you had: (Please select all that apply)")

#COVID-19 Vaccine
label("vac_2","You stated that you received a COVID-19 vaccine. What was the date that you received the first (or only) dose (if you do not remember the exact date, please provide your best estimate).")
label("vac_2y","Covid-19 vaccine year")
label("vac_2m","Covid-19 vaccine year")
label("vac_2d","Covid-19 vaccine year")
label("vac_3","You stated that you received a COVID-19 vaccine. What was the date that you received the second dose (if you do not remember the exact date, please provide your best estimate).")
label("vac_3y","Covid-19 vaccine year")
label("vac_3m","Covid-19 vaccine year")
label("vac_3d","Covid-19 vaccine year")

#Detroit-Day Discrimination
label("dd_total","Sum Detroit Day Discrimination")

#MacArthur Major Discrimination
label("mmd_1a","How many times in your life have you been discriminated against by being discouraged by a teacher or advisor from seeking higher education because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1b","How many times in your life have you been discriminated against by being denied a scholarship because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1c","How many times in your life have you been discriminated against by not being hired for a job because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1d","How many times in your life have you been discriminated against by not receiving a job promotion because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1e","How many times in your life have you been discriminated against by being fired because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1f","How many times in your life have you been discriminated against by being prevented from renting or buying a home in the neighborhood you wanted because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1g","How many times in your life have you been discriminated against by being prevented from remaining in neighborhood because neighbors made life so uncomfortable because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1h","How many times in your life have you been discriminated against by being hassled by the police because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1i","How many times in your life have you been discriminated against by being denied a bank loan because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1j","How many times in your life have you been discriminated against by being denied or provided inferior medical care because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_1k","How many times in your life have you been discriminated against by being denied or provided inferior service by a plumber, car mechanic, or other service provider because of such things as your race, ethnicity, gender, age, religion, physical appearance, sexual orientation, or other characteristics?")
label("mmd_total","MacArthur Major Discrimination total score")
label("mmd_2_f","Factor version of `what was the main reason for the discrimination you experienced?`")
label("mmd_3_f","Factor version of `overall, how much has discrimination interfered with y ou having a full and productive life?`")
label("mmd_4_f","Factor version of `overall, how much harder has your life been because of discrimination?`")
label("mmd_total_f","Factor version of `MacArthur Major Discrimination total score`")

#Urban Life Stress Scale
label("uls_1_f","Factor version of `how much stress do you generally experience related to money or finances.`")
label("uls_2_f","Factor version of `how much stress do you generally experience related to your job satisfaction.`")
label("uls_3_f","Factor version of `how much stress do you generally experience related to raising children/being a parent.`")
label("uls_4_f","Factor version of `how much stress do you generally experience related to death, injury, or illness of someone close.`")
label("uls_5_f","Factor version of `how much stress do you generally experience related to your housing, or living situation.`")
label("uls_6_f","Factor version of `how much stress do you generally experience related to your physical health`")
label("uls_7_f","Factor version of `how much stress do you generally experience related to your neighborhood environment.`")
label("uls_8_f","Factor version of `how much stress do you generally experience related to transportation.`")
label("uls_9_f","Factor version of `how much stress do you generally experience related to your education.`")
label("uls_10_f","Factor version of `how much stress do you generally experience related to marriage or romantic relationships.`")
label("uls_11_f","Factor version of `how much stress do you generally experience related to other family problems.`")
label("uls_12_f","Factor version of `how much stress do you generally experience related to using public services.`")
label("uls_13_f","Factor version of `how much stress do you generally experience related to crime and violence.`")
label("uls_14_f","Factor version of `how much stress do you generally experience related to gang activity.`")
label("uls_15_f","Factor version of `how much stress do you generally experience related to experiences involving racism or discrimination.`")
label("uls_16_f","Factor version of `how much stress do you generally experience related to social life, social activities.`")
label("uls_17_f","Factor version of `how much stress do you generally experience related to drugs or alcohol.`")
label("uls_18_f","Factor version of `how much stress do you generally experience related to communication or cultural conflicts.`")
label("uls_19_f","Factor version of `how much stress do you generally experience related to family violence.`")
label("uls_20_f","Factor version of `how much stress do you generally experience related to relations with racial groups not your own.`")
label("uls_21_f","Factor version of `how much stress do you generally experience related to relations with police.`")
label("uls_total","urban life stress total score")
label("uls_total_f","Factor version of `urban life stress total score`")

#Perceived Stress Scale Reverse Code
label("ps_2r","Perceived Stress Scale Item 2 Reverse Code")
label("ps_3r","Perceived Stress Scale Item 3 Reverse Code")
label("ps_total","Perceived Stress Scale total score")
label("ps_1_f","Factor version of `in the last week, how often have you felt that you were unable to control the important things in your life?`")
label("ps_2_f","Factor version of `in the last week, how often have you felt confident about your ability to handle your personal problems?`")
label("ps_3_f","Factor version of `in the last week, how often have you felt that things were going your way?`")
label("ps_4_f","Factor version of `in the last week, how often have you felt difficulties were piling up so high that you could not overcome them?`")

#Personal Victimization
label("pv_1_f","Factor version of `in the past 30 days, has anyone used violence, such as in a mugging, fight, or sexual assault, against you?")
label("pv_2_f","Factor version of `in the past 30 days, how many times have you been a witness to acts of violence?`")
label("pv_3_f","Factor version of `in the past 6 months, how many times have you been a witness to acts of violence?`")

#Distress Tolerance Scale Reverse Code
label("dts_1r","Feeling distressed or upset is unbearable to me - Reverse coded")
label("dts_1r_f","Factor version of `Feeling distressed or upset is unbearable to me - Reverse coded`")
label("dts_2r","When I feel distressed or upset, all I can think about is how bad I feel - Reverse coded")
label("dts_2r_f","Factor version of `When I feel distressed or upset, all I can think about is how bad I feel - Reverse coded`")
label("dts_3r","I can’t handle feeling distressed or upset - Reverse coded")
label("dts_3r_f","Factor version of `I can’t handle feeling distressed or upset - Reverse coded`")
label("dts_4r","My feelings of distress are so intense that they completely take over - Reverse coded")
label("dts_4r_f","Factor version of `My feelings of distress are so intense that they completely take over - Reverse coded`")
label("dts_5r","There’s nothing worse than feeling distressed or upset - Reverse coded")
label("dts_5r_f","Factor version of `There’s nothing worse than feeling distressed or upset - Reverse coded`")
label("dts_6r","My feelings of distress or being upset are just an acceptable part of life - Reverse coded")
label("dts_6r_f","Factor version of `My feelings of distress or being upset are just an acceptable part of life - Reverse coded`")
label("dts_8r","My feelings of distress or being upset are not acceptable - Reverse coded")
label("dts_8r_f","Factor version of `My feelings of distress or being upset are not acceptable - Reverse coded`")
label("dts_9r","I’ll do anything to avoid feeling distressed or upset - Reverse coded")
label("dts_9r_f","Factor version of `I’ll do anything to avoid feeling distressed or upset - Reverse coded`")
label("dts_10r","Other people seem to be able to tolerate feeling distressed or upset better than I can - Reverse coded")
label("dts_10r_f","Factor version of `Other people seem to be able to tolerate feeling distressed or upset better than I can - Reverse coded`")
label("dts_11r","Being distressed or upset is always a major ordeal for me - Reverse coded")
label("dts_11r_f","Factor version of `Being distressed or upset is always a major ordeal for me - Reverse coded`")
label("dts_12r","I am ashamed of myself when I feel distressed or upset - Reverse coded")
label("dts_12r_f","Factor version of `I am ashamed of myself when I feel distressed or upset - Reverse coded`")
label("dts_13r","My feelings of distress or being upset scare me - Reverse coded")
label("dts_13r_f","Factor version of `My feelings of distress or being upset scare me - Reverse coded`")
label("dts_14r","I’ll do anything to stop feeling distressed or upset - Reverse coded")
label("dts_14r_f","Factor version of `I’ll do anything to stop feeling distressed or upset - Reverse coded`")
label("dts_15r","When I feel distressed or upset, I must do something about it immediately - Reverse coded")
label("dts_15r","Factor version of `When I feel distressed or upset, I must do something about it immediately - Reverse coded`")
label("dts_16r","When I feel distressed or upset, I cannot help but concentrate on how bad the distress actually feels - Reverse coded")
label("dts_16r_f","Factor version of `When I feel distressed or upset, I cannot help but concentrate on how bad the distress actually feels - Reverse coded`")
label("dts_tolerance_f","DTS Tolerance  subscale mean total")
label("dts_tolerance","DTS Tolerance  subscale mean total")
label("dts_absorption_f","Factor version of `DTS absorption subscale mean total`")
label("dts_absorption","DTS absorption subscale mean total")
label("dts_appraisal","DTS appraisal subscale mean total")
label("dts_regulation","DTS regulation subscale mean total")
label("dts_total","Distress Tolerance Scale total score")
label("dts_1_f","Factor version of `feeling distressed or upset is unbearable to me.`")
label("dts_2_f","Factor version of `when i feel distressed or upset, all I can think about is how bad I feel.`")
label("dts_3_f","Factor version of `i can't handle feeling distressed or upset.`")
label("dts_4_f","Factor version of my feelings of distress are so intense that they completely take over.`")
label("dts_5_f","Factor version of `there's nothing worse than feeling distressed or upset.`")
label("dts_6_f","Factor version of `my feelings of distress or being upset are an acceptable part of life`")
label("dts_7_f","Factor version of `i can tolerate being distressed or upset as well as most people.`")
label("dts_8_f","Factor version of `my feelings of distress or being upset are not acceptable.`")
label("dts_9_f","Factor version of `i'll do anything to avoid feeling distressed or upset.`")
label("dts_10_f","Factor version of `other people seem to be able to tolerate feeling distressed or upset better than I can.`")
label("dts_11_f","Factor version of `being distressed or upset is always a major ordeal for me.`")
label("dts_12_f","Factor version of `i am ashamed of myself when I feel distressed or upset.`")
label("dts_13_f","Factor version of `my feelings of distress or being upset scare me.`")

#Aggression Questionnaire
label("pa","Physical aggression subscale")
label("va","Verbal aggression subscale")
label("a","Anger subscale")
label("ha","Hostility subscale")
label("aq","Agression subscale totals")

#CES-D Dichotomous Reverse Code 
label("ces_5r","Reverse I felt hopeful scored")
label("ces_8r","Reverse I was happy scored")
label("ces_total","CES-D total: 1-10 (10 or greater is considered depressed")
label("ces_1_dichot","CES-D dichotomus:During the past week, I was bothered by things that don't usually bother me")
label("ces_2_dichot","CES-D dichotomus:During the past week, I had trouble keeping my mind on what I was doing.")
label("ces_3_dichot","CES-D dichotomus:During the past week, I felt depressed.")
label("ces_4_dichot","CES-D dichotomus:During the past week, I felt that everything I did was an effort.")
label("ces_5r_dichot","CES-D dichotomus:During the past week, I felt hopeful about the future.")
label("ces_6_dichot","CES-D dichotomus:During the past week, I felt fearful.")
label("ces_7_dichot","CES-D dichotomus:During the past week, my sleep was restless.")
label("ces_8r_dichot","CES-D dichotomus:During the past week, I was happy.")
label("ces_9_dichot","CES-D dichotomus:During the past week, I felt lonely.")
label("ces_10_dichot","CES-D dichotomus:During the past week, I could not get going.")
label("ces_dichot_total","CES-D dichotomus total")

#Interpersonal Support Evaluation List Reverse Code
label("is_1r","Reverse trip for a day")
label("is_2r","Reverse no one to share worries")
label("is_7r","Reverse don't often get invited")
label("is_8r","Reverse difficult to find home sitter")
label("is_11r","Reverse difficult to find good advice")
label("is_12r","Reverse no help moving")
label("iseapp","ISE appraisal")
label("isebel","ISE belonging")
label("isetan","ISE tangable")

#Lubben Social Network Scale
label("lsn_family","Sum LSN_V1_family 0-15 (scores of less than 6 are considered to have marginal family ties")
label("lsn_friends","Sum LSN_V1_total 0-30 ((scores of less than 6 are considered to have marginal friendship ties")
label("lsn_total","Sum LSN_V1_total 0-30 (a score of 12 and lower delineates “at-risk” for social isolation and higher scores indicate more social engagement")
label("lsn_family_f","Factor version of `Sum LSN_V1_family 0-15 (scores of less than 6 are considered to have marginal family ties`")

#Homeless Location TLFBs
label("days_followed","TLFB total days followed")
label("per_days_homeless","Percentage of days homeless")
label("num_days_home","Number of days at home")
label("est_days_homeless_yr","Estimated number of days homeless per year")
label("avg_days_homeless_wk","Average number of days homeless per week")
label("flag_out_of_window","Flag visit out of window")

#Resource Utilization Questionnaire
label("r_1","Over the past 30 days, how many days did you receive Mental Health/Behavioral Health Counseling at local shelters?")
label("r_2","Over the past 30 days, how many days did you receive Substance Abuse Counseling at local shelters?")
label("r_3","Over the past 30 days, how many days did you receive Smoking Cessation Counseling at local shelters?")
label("r_4","Over the past 30 days, how many days did you see a doctor for a medical problem at local shelters?")
label("r_5","Over the past 30 days, how many days did you spend the night at a shelter?")
label("r_6","Over the past 30 days, how many days did you receive meals at local shelters?")
label("r_8","Over the past 30 days, how many days did you speak over the phone with a case manager from local shelters?")
label("r_9","Over the past 30 days, how many days did you attended group educational meetings at local shelters?")
label("r_10","Over the past 30 days, how many days did you receive employment/job readiness training at local shelters?")
label("r_13","Over the past 30 days, how many days did you receive help with getting vital documents (For example, birth certificates, state identification, social security cards) at local shelters?")
label("r_14","Over the past 30 days, how many days did shelter staff help you to reconnect with family members?")
label("r_15","What types of services would be most helpful to you right now? (select all that apply)") #Drop r15

#Barriers to Phone Based Management
label("bpm_5","Which of the following would keep you from connecting to your case manager over the phone? (select all that apply)")

#Treatment Quality and Satisfaction Survey
label("tq_15_3","What do you like about the Link2Care smart phone application?")
label("tq_16_3","What do you not like about the Link2Care smart phone application?")
label("tq_17_3","How would you improve the Link2Care smart phone application?")
label("tq_18_3","What other thoughts and opinions do you have about the Link2Care application?")

#Bridge Case Manager Sessions
label("bridge_baseline_date","Bridge Case manager sessions: Participant baseline date")
label("bridge_v2_rand_date","Bridge Case manager sessions: Randomized date")
label("bridge_v5_sched_final_visit_date","Bridge Case manager sessions: Visit 5 date")
label("bridge_date_session","Date of Bridge session")
label("bridge_type","Type of Bridge session")
label("bridge_duration","Duration of Bridge session")
label("bridge_flag_ns_v2","Bridge session no show V2")
label("bridge_flag_dropped","Bridge session dropped")
label("bridge_notes","Bridge session notes")
label("n_missing","Bridge session missing")
label("bridge_type_f","Case management")
label("bridge_case_management","dummy variable case management")
label("bridge_row","Bridge session row number")
label("bridge_total_sessions","Sum type of Bridge session")
label("bridge_total_minutes","Sum duration of bridge session")
label("bridge_any_case_management","Used at least one session of regular case management")
label("bridge_any_crisis_management","Used at least one session of crisis case management")
label("bridge_any_other","Used at least one session of other case management")
label("bridge_all_none","Used no forms of Bridge case management")
```

# Drop  variables that are duplicates & move `flag_out_of_window`
```{r}
combined_participant_data = subset(combined_participant_data, select = -c(147, 148) )
combined_participant_data <- combined_participant_data %>%
  relocate(234, .before = 29)
combined_participant_data = subset(combined_participant_data, select = -c(260) )
combined_participant_data = subset(combined_participant_data, select = -c(302) )
combined_participant_data = subset(combined_participant_data, select = -c(338) )
```

# Assess number of variables to be sourced (excluding factor and reverse coded calculated variables)
```{r}
dim(combined_participant_data) # 1614 1298
```

# Source raw variables based on dataframe that variable comes from

## Administrative
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes( 
    visit_type,
    source = "V1, V2, V3, V4, V5"
) %>%

cb_add_col_attributes(
    flag_out_of_window, 
    source = "V1, V3, V4, V5"
) %>%
  
cb_add_col_attributes( 
    ii, 
    source = "V1, V2, V3, V4, V5"
) %>%
  
cb_add_col_attributes(
    read_1, 
    source = "V1, V2, V3, V4, V5"
) %>%
  
cb_add_col_attributes(
    read_2, 
    source = "V1, V2, V3, V4, V5"
) %>%
  
cb_add_col_attributes(
    read_3, 
    source = "V1, V2, V3, V4, V5"
) %>%

cb_add_col_attributes(
    ctime, 
    source = "V1, V2, V3, V4, V5"
) %>%

cb_add_col_attributes(
    endtime, 
    source = "V1, V2, V3, V4, V5"
) %>%
  
cb_add_col_attributes(
    etime, 
    source = "V1, V2, V3, V4, V5"
)
```

## De-identifiers, Master Log, & Screening Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>% 
  cb_add_col_attributes(
    id, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
  cb_add_col_attributes(
    visit,
    source = "V1, V2, V3, V4, V5"
) %>% 
  
  cb_add_col_attributes(
    date_visit, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    group, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ml_status, 
    source = "Master Log"
) %>%
  
cb_add_col_attributes(
    ml_gender, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_race, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_hispanic, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_date_birth, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_age, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_clincard_id, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_n_clincards, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_phone_id, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_phone_number_l2c, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_phone_n_distributed, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_care_manager, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_v1, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_v2, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_v3, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes(
    ml_v4, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    ml_v5, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    ml_v3_r_distributed, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    ml_v3_r_completed, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    ml_v4_r_distributed, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    ml_v4_r_completed, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    ml_v5_r_distributed, 
    source = "Master Log"
) %>% 

cb_add_col_attributes( 
    ml_v5_r_completed, 
    source = "Master Log"
) %>% 
  
cb_add_col_attributes( 
    gender, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes( 
    sq_hispanic, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_race, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_age, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_5, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_6, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_7, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_7a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_7b, 
    source = "V1"
) %>% 

cb_add_col_attributes( 
    sq_7c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_7d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_8, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_9, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_9l, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_10, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_11, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    cell_have, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    cell_pays, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    cell_talk_minutes, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    cell_smart, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    cell_data_plan, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    cell_number_change, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_18, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    media_use_email, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    media_use_facebook, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    media_use_google_plus, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    media_use_twitter, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    media_use_blogs, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    media_use_instagram, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    media_use_snapchat, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    media_use_linkedin, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    media_use_none, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    access_internet, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    facebook_active, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    facebook_check, 
    source = "V1"
) %>% 

cb_add_col_attributes( 
    sq_22, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22e, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes( 
    sq_22f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22g, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    sq_22h, 
    source = "V1"
)
```

## Mini-Mental State Exam

```{r}
combined_participant_data <- combined_participant_data %>%  
cb_add_col_attributes( 
    mms_1a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_1b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_1c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_1d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_1e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_1, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_2a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_2b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_2c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_2d, 
    source = "V1"
) %>% 

cb_add_col_attributes( 
    mms_2e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_2, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_3, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    mms_3g, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    mms_3h, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    mms_3i, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    mms_3j, 
    source = "V1"
) %>% 
    
cb_add_col_attributes( 
    mms_recall_1, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_4f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_count, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_5f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_num, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_6, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_6a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_6b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_6c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_6d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_recall_2, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_7, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_7a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_7b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_7c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_object, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_8, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_9, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_9a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_9b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_9c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_9d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_paper, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_10, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_11, 
    source = "V1"
) %>% 
  
cb_add_col_attributes( 
    mms_12, 
    source = "V1"
) %>% 

cb_add_col_attributes( 
    mms_total, 
    source = "V1"
) 
```

## Rapid Estimate of Adult Literacy in Medicine (REALM) and End of Screening Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>% 
  cb_add_col_attributes(
    realm, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_a, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_b, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_c, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_d, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_e, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_f, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_g, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_h, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_i, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    realm_total, 
    source = "V1"
) %>% 
  
  cb_add_col_attributes(
    sq_23, 
    source = "V1"
)
```

## Biological/Anthropometric Measures

```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    weight, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    height, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    waist_c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    co, 
    source = "V1, V3, V4, V5"
)
```

## Demographic/Background Information Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    dem_marital_status, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    dem_children, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_n, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_white, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_black, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_asian, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_pacific, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_native, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_race_mult_other, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_edu_20_cat, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_edu_ged, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_employ_status, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_employ_hpw, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    dem_employ_7days, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_ins, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    any_health_insurance, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    dem_ins_medicare, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_medicaid, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_ins_military, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_ins_private, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_ins_none, 
    source = "V1, V3, V4, V5"
) %>% 
  
  cb_add_col_attributes(
    dem_social_security, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_social_security_amount, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_snap, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_snap_amount, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    dem_income_source, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_work, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_criminalized, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_disability, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_emp_benefits, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_self_emp, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_sex, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_drugs, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_social_assistance, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_student_loans, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_friends_relatives, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_other, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_source_none, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_12_mnth_8_cat, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_13a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_13b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_13c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_13d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_13e, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    dem_13f, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    dem_13g, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    dem_13h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_income_1_mnth_7_cat, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_14h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_veteran, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_16, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_sexual_orientation, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    dem_transgender, 
    source = "V1, V3, V4, V5"
)
```
## Arrest
```{r}
combined_participant_data <- combined_participant_data %>%
  cb_add_col_attributes(
    arrested, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_baseline, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    arrested_date_1, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_2, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_3, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_4, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_5, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_6, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_7, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_8, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_9, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_10, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_11, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_date_12, 
    source = "Dallas County"
) %>% 
  
cb_add_col_attributes(
    arrested_num_summary, 
    source = "Dallas County"
)
```

## The Brief Homelessness Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    homeless_time_total, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_1y, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_1m, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_1d, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_periods, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_age_first_time, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_current_total, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_4y, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_4m, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_4d, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_mental_treatment, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_6, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_7, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_7y, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_7m, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_7w, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_8, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_9, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bh_10, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_11, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_reason_total, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_reason_not_homeless, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_lost_job, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    homeless_reason_evicted, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_substance, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_mental_illness, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_medical_bills, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_family, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_legal, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_jail, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_natural_disaster, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_domestic_violence, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    homeless_reason_other, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_13f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14g, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_14h, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15g, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_15h, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_16, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    jail_time_total, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_18y, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_18m, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_18w, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_18d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_19, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_20, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_21, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_22, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_22y, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_22m, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_22w, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_23, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24g, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24h, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_24i, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_25, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    bh_26, 
    source = "V1"
)
```

## MacArthur Scale of Subjective Social Status
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    sss_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    sss_2, 
    source = "V1, V3, V4, V5"
) 
```

## Patient Health Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    phq_1, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    phq_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_12, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_13, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_14, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    phq_15, 
    source = "V1, V3, V4, V5"
)
```

## SF-12 Health Survey
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    hs_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hs_12, 
    source = "V1, V3, V4, V5"
)
```

## Health Related Quality of Life
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    hrq_physical_30, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    hrq_mental_30, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    hrq_limit_activities_30, 
    source = "V1, V3, V4, V5"
)
```

## Self-Rated Health
```{r}
combined_participant_data <- combined_participant_data %>%  
cb_add_col_attributes(
    srh_1, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    srh_1a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_1h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_2f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_4h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_7g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_8g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9i, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9j, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9k, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9l, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9m, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9n, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9o, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9p, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9q, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_9r, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_12, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_13, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_14, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_14a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_14b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_14c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_14d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_15, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_16, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_17, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18a, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    srh_18b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18i, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18j, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18k, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_18l, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_19, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_20, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_21, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_22, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_23, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_24f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_25, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_26g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_27, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_28f, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    srh_28g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_29, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    srh_30a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_30g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_31, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_32g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_33, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_34g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_35, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    srh_36, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    srh_37, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    srh_38, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_38g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_39, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40e, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    srh_40f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_40i, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_41, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_42, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_43, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_44, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_45, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_46, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_47, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_48, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_49, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    sp_app_change_behavior, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    sp_app_manage_health, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    srh_52h, 
    source = "V1, V3, V4, V5"
) %>% 
  
  cb_add_col_attributes(
    srh_52i, 
    source = "V1, V3, V4, V5"
)
```
## TCU Drug Screen 5
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    ds_1, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_2, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_3, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_4, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_5, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_6, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_7, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_8, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_9, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_10, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_10a, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_10b, 
    source = "V2, V4, V5"
) %>% 

cb_add_col_attributes(
    ds_11, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_11a, 
    source = "V2, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ds_11b, 
    source = "V2, V4, V5"
)
```

## Primary Care PTSD Screen (PC-PTSD)
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    ptsd_1, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    ptsd_2, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    ptsd_3, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    ptsd_4, 
    source = "V1"
)
```
## BRFSS Adverse Childhood Experience (ACE) Module 
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    brac_1, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_2, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_3, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_4, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_5, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_6, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_7, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_8, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_9, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_10, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    brac_11, 
    source = "V2"
) 
```

## Tobacco History
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    t_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_3y, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_3m, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_6f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_7a, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    t_7b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_7c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_7d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_7e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_7f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_12, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_13, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_13a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_13b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_14, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_15i, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_16, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_17, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_18, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_19, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_20, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_21, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_22, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_23, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_24h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_25, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_26, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_27f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_28, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_29, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_30, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_31, 
    source = "V1, V3, V4, V5"
) %>% 
    
cb_add_col_attributes(
    t_32, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32a, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32b, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32c, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32d, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32e, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32f, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32g, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32h, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32i, 
    source = "V1, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    t_32j, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_33, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    t_33a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_33b, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    t_33c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_34, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35i, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_35j, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_36, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_37, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_38, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_39, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_40, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_41, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    t_42, 
    source = "V1, V3, V4, V5"
)
```

## Heaviness of Smoking Index
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    hsi_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    hsi_2, 
    source = "V1, V3, V4, V5"
)
```

## Behavioral Risk Factor Surveillance System (BRFSS) Inadequate Sleep
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    brs_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    brs_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    brs_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    brs_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    brs_5, 
    source = "V1, V3, V4, V5"
)
```

## Alcohol Quantity and Frequency Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    af_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_2m, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_3tu, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_4w, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_5th, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_6f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_6sa, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_8su, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_drinks, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_9a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_9b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    af_9c, 
    source = "V1, V3, V4, V5"
)
```

## Alcohol and Drug Timeline Follow-Back (TLFB)
```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    days_followed, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    total_drinks, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    num_drinking_days, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ave_drinks_day, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    num_alc_abstinent_days, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    heavy_drinking_days, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    greatest_drinks_1_day, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    drinks_wk, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    num_days_using_drugs, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    per_days_using_drugs, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    per_drug_abstinent_days, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    drug_use_days_yr, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    drug_use_days_week, 
    source = "V1, V3, V4, V5"
)
```


## Personality Beliefs Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    pbq_1, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    pbq_2, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    pbq_3, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    pbq_4, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    pbq_5, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    pbq_6, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    pbq_7, 
    source = "V2"
)
```

## USDA Food Security Survey
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    fss_1, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    fss_2, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    fss_3, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    fss_3a, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    fss_4, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    fss_5, 
    source = "V1, V2, V3, V4, V5"
)
```

## Meal Survey
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    meals_eaten_yesterday, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    meals_cafeteria_24_hours, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    meals_fruit_veg_yesterday, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    meals_missed_week, 
    source = "V1, V3, V4, V5"
)
```

## TCU CJ Client Evaluation of Self and Treatment (CJ CEST)
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    cj_1, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_2, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_3, 
    source = "V2, V4"
) %>% 
    
cb_add_col_attributes(
    cj_4, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_5, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_6, 
    source = "V2, V4"
) %>% 
    
cb_add_col_attributes(
    cj_7, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_8, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_9, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_10, 
    source = "V2, V4"
) %>% 
    
cb_add_col_attributes(
    cj_11, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_12, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_13, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_14, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_15, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_16, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_17, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_18, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_19, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_20, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_21, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_22, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_23, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_24, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_25, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_26, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_27, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_28, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_29, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_30, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_31, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_32, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_33, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_34, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_35, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_36, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_37, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_38, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_39, 
    source = "V2, V4"
) %>% 
  
cb_add_col_attributes(
    cj_40, 
    source = "V2, V4"
)
```

## Sexual Behaviors

```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    sb_1, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_2, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_3, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_4, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_5, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_6, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7a, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7b, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7c, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7d, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7e, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7f, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_7g, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_8, 
    source = "V1"
) %>% 
  
cb_add_col_attributes(
    sb_9, 
    source = "V1"
)
```

## COVID-19 Vaccine
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    vac_1, 
    source = "V1, V2, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    vac_2, 
    source = "V1, V2, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    vac_2y, 
    source = "V1, V2, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    vac_2m, 
    source = "V1, V2, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    vac_2d, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    vac_3, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    vac_3y, 
    source = "V1, V2, V3, V4, V5"
) %>% 
      
cb_add_col_attributes(
    vac_3m, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    vac_3d, 
    source = "V1, V2, V3, V4, V5"
)
```

## Well-Being Assessment
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    well_being_1, 
    source = "V2"
) %>% 
    
cb_add_col_attributes(
    well_being_2, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    well_being_3, 
    source = "V1, V2, V3, V4, V5"
)
```

## Detroit Area Study Assessment of Day-to-Day Discrimination

```{r}
combined_participant_data <- combined_participant_data %>% 
cb_add_col_attributes(
    ddd_less_courtesy, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_less_respect, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_poorer_service, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_not_smart, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_afraid, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_dishonest, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_better, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_insulted, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_threatened, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddd_main_reason, 
    source = "V1, V3, V4, V5"
)
```

## MacArthur Major Discrimination
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    mmd_1a, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1b, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1c, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1d, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1e, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1f, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1g, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1h, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1i, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1j, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    mmd_1k, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    macarthur_main_reason, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    macarthur_interfere, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    macarthur_harder_life, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    macarthur_main_reason, 
    source = "V2"
)
```

## Urban Life Stress Scale
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    uls_1, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_2, 
    source = "V2, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    uls_3, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_4, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_5, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_6, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_7, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_8, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_9, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_10, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_11, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_12, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_13, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_14, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_15, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_16, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_17, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_18, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_19, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_20, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    uls_21, 
    source = "V2, V3, V4, V5"
)
```

## Personal Victimization
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    pv_violence_victim_30, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    pv_witness_violence_30, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    pv_witness_violence_6, 
    source = "V1, V2, V3, V4, V5"
)
```

## Perceived Stress Scale
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    ps_1, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ps_2, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ps_3, 
    source = "V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ps_4, 
    source = "V2, V3, V4, V5"
)
```

## Distress Tolerance Scale (DTS)
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    dts_1, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_2, 
    source = "V2, V5"
) %>% 
  
  cb_add_col_attributes(
    dts_3, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_4, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_5, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_6, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_7, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_8, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_9, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_10, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_11, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_12, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_13, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_14, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_15, 
    source = "V2, V5"
) %>% 
  
cb_add_col_attributes(
    dts_16, 
    source = "V2, V5"
)
```

## The Pandemic Stress Index (PSI)

## Aggression Questionnaire (AQ-12)

```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    aq_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    aq_12, 
    source = "V1, V3, V4, V5"
)
```

## Center for Epidemiological Studies Depression (CES-D)
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    ces_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ces_10, 
    source = "V1, V3, V4, V5"
)
```

## Interpersonal Support Evaluation List 

```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    is_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    is_12, 
    source = "V1, V3, V4, V5"
)
```

## Religious Participation
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    rp_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    rp_2, 
    source = "V1, V3, V4, V5"
)
```

## Lubben Social Network Scale-6
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    lsn_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    lsn_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    lsn_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    lsn_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    lsn_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    lsn_6, 
    source = "V1, V3, V4, V5"
)
```

## Homeless Timeline Follow-Back (TLFB)
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    num_days_homeless, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    per_days_homeless, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    num_days_home, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    est_days_homeless_yr, 
    source = "V1, V3, V4, V5"
) %>% 

cb_add_col_attributes(
    avg_days_homeless_wk, 
    source = "V1, V3, V4, V5"
)
```


## Resource Utilization Questionnaire
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    r_1, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_2, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_3, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_4, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_5, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_6, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_7, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_8, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_9, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_10, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_11, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_12, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_13, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_14, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_15, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16a, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16b, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16c, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16d, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16e, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16f, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16g, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16h, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16i, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16j, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16k, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16l, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16m, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16n, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    r_16o, 
    source = "V1, V3, V4, V5"
)
```

## Barriers to Phone Based Case Management
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    bpm_1, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_2, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_3, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_4, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5a, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5b, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5c, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5d, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5e, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5f, 
    source = "V1, V5"
) %>% 
  
cb_add_col_attributes(
    bpm_5g, 
    source = "V1, V5"
)
```

## Treatment Quality and Satisfaction Survey

```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    tq_1_1, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_2_1, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_14_1, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_1_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_2_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_3_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_4_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_9_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_10_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_11_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_12_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_13_2, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_1_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_2_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_3_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_4_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_5_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_6_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_7_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_8_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_9_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_10_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_11_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_12_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_13_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_14_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_15_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_16_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_17_3, 
    source = "V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    tq_18_3, 
    source = "V3, V4, V5"
) 
```

## Bridge Sessions
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    bridge_baseline_date, 
    source = "V1"
) %>% 

cb_add_col_attributes(
    bridge_v2_rand_date, 
    source = "V2"
) %>% 

cb_add_col_attributes(
    bridge_v5_sched_final_visit_date, 
    source = "V5"
) %>% 

cb_add_col_attributes(
    bridge_date_session, 
    source = "The Bridge Shelter"
) %>% 
  
cb_add_col_attributes(
    bridge_type, 
    source = "The Bridge Shelter"
) %>% 
  
cb_add_col_attributes(
    bridge_duration, 
    source = "The Bridge Shelter"
) %>% 

cb_add_col_attributes(
    bridge_flag_ns_v2, 
    source = "V2"
) %>% 
  
cb_add_col_attributes(
    bridge_flag_dropped, 
    source = "V1, V2, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    bridge_notes, 
    source = "The Bridge Shelter"
)
```

## Delay Discounting Task
```{r}
combined_participant_data <- combined_participant_data %>%
cb_add_col_attributes(
    ddt_k, 
    source = "V1, V3, V4, V5"
) %>% 
  
cb_add_col_attributes(
    ddt_ed50, 
    source = "V1, V3, V4, V5"
)
```

## Staff Perceptions of the Link2Care App *don't include?

## Usual Daily EMA Items

## Monday EMA Items

# Create codebook

```{r}
# print(test_cb, "test.docx")
```

# 🖨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant data cleaned with", nrow(combined_participant_data),
  "rows and", ncol(combined_participant_data), "columns.\n"
)
# 2022-07-11: Combined Participant data cleaned with 1157 rows and 1202 columns.
# 2023-03-20: Combined Participant data cleaned with 1601 rows and 1184 columns.
# 2023-04-18: Combined Participant data cleaned with 1601 rows and 1184 columns.
# 2023-04-19: Combined Participant data cleaned with 1770 rows and 1131 columns.
# 2023-04-20: Combined Participant data cleaned with 1769 rows and 1221 columns.
# 2023-05-02: Combined Participant data cleaned with 48064 rows and 1132 columns.
# 2023-05-11: Combined Participant data cleaned with 1611 rows and 1129 columns.
# 2023-05-15: Combined Participant data cleaned with 1614 rows and 1129 columns.
# 2023-05-16: Combined Participant data cleaned with 1614 rows and 1126 columns.
# 2023-05-20: Combined Participant data cleaned with 1614 rows and 1178 columns.
# 2023-05-23: Combined Participant data cleaned with 1614 rows and 1303 columns.
# 2023-05-23: Combined Participant data cleaned with 1614 rows and 1298 columns.
```

# 💾Save the data frame

```{r}
path <- "../Participant Data/Combined Participant Data/SPSS Data/combined_participant_data.sav"
```

```{r}
write_sav(combined_participant_data, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant data saved to", path, "\n"
)
```

```{r}
path <- "../Participant Data/R Data/combined_participant_data.rds"
```

```{r}
write_rds(combined_participant_data, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant data saved to", path, "\n"
)
```
```{r}
library(codebookr)
install.packages("flextable", type = "binary")
```

```{r}
start <- lubridate::now()
combined_participant_data_cb <- codebook(
  # select(combined_participant_data, 835:840),
  # select(combined_participant_data, 835),
  combined_participant_data,
   no_summary_stats = c(
   "ml_date_birth", "ml_clincard_id", "ml_phone_number_l2c", "ml_care_manager", "ii"
  )
)
end <- lubridate::now()
```

```{r}
end - start # Time difference of 9.671826 mins
```

# Create codebook

```{r}
print(combined_participant_data_cb, "codebooks/Combined Participant Survey Data Codebook.docx")
```





