---
title: "Combined Data Codebook"
date: "2022-10-23 <br> Updated: `r Sys.Date()`"
format: pdf
editor: 
  markdown: 
    wrap: sentence
---

# ⭐️Overview

This file generates a codebook from the combined Link2Care (L2C) data set and variable map using Codebookr.

# 📦Load packages & Functions

```{r, message=FALSE, warning=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(codebookr, warn.conflicts = FALSE)
library(purrr, warn.conflicts = FALSE)
library(here, warn.conflicts = FALSE)
library(stringr, warn.conflicts = FALSE)
library(lubridate, warn.conflicts = FALSE)
library(readxl, warn.conflicts = FALSE)
library(openxlsx, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(tidyverse, warn.conflicts = FALSE)
```

```{r}
source(here("R", "vm_check.R"))
```

# 📥 Import data

## Combined Data Set

We imported our Combined Data Set

```{r}
combined_data_path <- here(
  "data", "Combined Participant Data", "combined_data_03.rds"
  )
```

Import the data.
Check the most recent file modification dates and print for user when this file is being sourced.

```{r message=FALSE}
combined_data <- readRDS(combined_data_path)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Combined data imported with", nrow(combined_data), "rows and", 
  ncol(combined_data), "columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Combined data last modified on OneDrive", 
      as.character(file.info(combined_data_path)$mtime), "\n"
    )

# 2023-10-25: Combined data imported with 1610 rows and 1062 columns.
# Combined data last modified on OneDrive 2023-10-26 11:15:17 
```

We purged the import path for memory management.

```{r}
rm(combined_data_path)
```

## Variable Map

We imported our Variable Map.

```{r}
variable_map_path <- here(
  "data", "Combined Participant Data", "variable_map_03.rds"
  )
```

Import the data.
Check the most recent file modification dates and print for user when this file is being sourced.

```{r message=FALSE}
variable_map <- readRDS(variable_map_path)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Variable Map imported with", nrow(variable_map), "rows and", 
  ncol(variable_map), "columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Variable Map data last modified on OneDrive", 
      as.character(file.info(variable_map_path)$mtime), "\n"
    )

# 2023-10-25: Variable Map imported with 1083 rows and 24 columns.
# Variable Map data last modified on OneDrive 2023-10-26 11:15:18 
```

We ensured our Variable Map met our required minimum format.

```{r}
vm_check(variable_map)
# TRUE
```

We purged the import path for memory management.

```{r}
rm(variable_map_path)
```

# Modifying Interviewer and Care Manager Columns

We dropped the labels from the interviewer and case manager variables to protect these identifier variables.

```{r}
# INTERVIEWER

var_val_labels <- tibble::tibble(
      'val_text' = names(attributes(combined_data[['interviewer']])$labels)
    ) %>%
  rowwise() %>%
      mutate(
        'val' = attributes(combined_data[['interviewer']])$labels[[val_text]]
        ) %>%
  ungroup()

combined_data[['interviewer']] <- factor(
  combined_data[['interviewer']],
  levels = var_val_labels$val_text,
  labels = var_val_labels$val
  )

combined_data[['interviewer']] <- factor(
  combined_data[['interviewer']],
  levels = var_val_labels$val,
  labels = var_val_labels$val
  )

attributes(combined_data[['interviewer']])$labels <- NULL

# CARE MANAGER

var_val_labels <- tibble::tibble(
      'val_text' = names(attributes(combined_data[['care_manager']])$labels)
    ) %>%
  rowwise() %>%
      mutate(
        'val' = attributes(combined_data[['care_manager']])$labels[[val_text]]
        ) %>%
  ungroup()

combined_data[['care_manager']] <- factor(
  combined_data[['care_manager']],
  levels = var_val_labels$val_text,
  labels = var_val_labels$val
  )

combined_data[['care_manager']] <- factor(
  combined_data[['care_manager']],
  levels = var_val_labels$val,
  labels = var_val_labels$val
  )

attributes(combined_data[['care_manager']])$labels <- NULL
```

# Blocking Summary Statistics on PHI and Other Variables

We identified our PHI variables, for which we wanted to block summary statistics.

```{r}
blocking_vars <- pull(
  variable_map %>%
    filter(phi) %>%
    select(final_variable)
  )
```

# Codebook Generation

We generated our codebook, with title, subtitle, and description. We blocked summary statistics on our PHI fields.

```{r, message = FALSE}
book <- codebook(
  df = combined_data,
  title = "Link2Care Subject Data",
  no_summary_stats = blocking_vars,
  keep_blank_attributes = FALSE)
```

# 💾 Exporting Codebook to DOCX Format

```{r}
print(book, here("codebooks", "Link2Care Combined Subject Data.docx"))
```


```{r}
rm(book)
rm(variable_map)
rm(combined_data)
rm(blocking_vars)
rm(var_val_labels)
```

