---
title: "Timeline Followback"
date: "2021-06-30 <br> Updated: `r Sys.Date()`"
---

# â­ï¸Overview

This file is used to import the Link2Care follow-up visit survey data and do some initial data cleaning. 

**NOTE on data sources:**

The TLFB data is exported from somewhere as 3 individual Excel files (i.e., alcohol, drug use, location) for each participant. Those individual files are stored on the the UTHealth servers in Participant Data > TLFB Data. At some point, SPSS is used to merge (and possibly clean?) these individual data sets. The merged TLFB data is stored on the UTHealth servers in Participant Data > SPSS Data > TLFB Data. That is the data we are importing below.


# ðŸ“¦Load packages

```{r message=FALSE}
library(dplyr)
library(haven)
library(readr)
library(testthat)
```

# ðŸŒŽConnect to UTH server 

```{bash eval=FALSE}
# Don't drill all the way down to live documents because not all of the data is in live documents.
open 'smb://islgpcifs.uthouston.edu/sph_research/Link2Care/'
```


# ðŸ“¥Import data 

```{r}
tlfb <- read_sav("/Volumes/Link2Care/Participant Data/SPSS Data/TLFB Data/TLFB_Database.sav")

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "TLFB", nrow(tlfb), "rows and", ncol(tlfb), "columns.\n"
)

# 2021-06-30: TLFB 1156 rows and 21 columns.
```


# Clean variable names

_See "Notes on cleaning individual L2C data sets for merging" for the rationale, style guidelines, and instructions for this section._

```{r}

```

  
## Extract content from Word codebook

```{r}
tlfb_cb_content <- read_docx("docs/codebooks/L2C_tlfb Codebook.docx") %>% 
  docx_summary()
```

## Keep the variables of interest only

```{r}
tlfb_cb_col_names <- tlfb_cb_content %>%
  filter(style_name %in% c("section_name", "cb_col_name", "col_name")) %>% 
  select(doc_index, style_name:text) %>% 
  pivot_wider(
    names_from = "style_name",
    values_from = "text"
  )
```

## Clean section names

```{r}
tlfb_cb_col_names <- tlfb_cb_col_names %>%
  mutate(
    # Remove "Sect-number."
    section_name = str_remove(section_name, "Sect-\\d{1,}."),
    # Remove asterisks
    section_name = str_remove_all(section_name, "\\*"),
    # Remove empty spaces
    section_name = str_trim(section_name)
  ) %>% 
  # Fill section down across rows
  fill(section_name)
```

## Record the sections that are completed at visit 2

We will use this for checking to make sure all of the correct questionnaire sections merge later.

**NOTE:** q_sections was created in data_survey_01_qds_v1_import.Rmd

```{r}
q_sections <- read_rds("data/questionnaire_section.rds")
```

```{r}
q_sections[["tlfb"]] <- unique(tlfb_cb_col_names$section_name)
# q_sections[["tlfb"]]
```

```{r}
write_rds(q_sections, "data/questionnaire_section.rds")
```

```{r}
rm(q_sections)
```

## Reduce to one row per column

Currently, cb_col_name and col_name are on separate rows. We will spread the different column names vertically across rows so that we can reduce the data frame down to one row per column.

```{r}
tlfb_cb_col_names <- tlfb_cb_col_names %>%
  # Spread cb_col_name across rows
  fill(cb_col_name) %>% 
  # Spread col_name across rows within cb_col_name
  group_by(cb_col_name) %>% 
  fill(col_name, .direction = "up") %>% 
  # # For data checking
  # filter(section_name == "Self-Rated Health Questionnaire") %>%
  # ungroup() %>%
  # slice(-1) %>%
  # summarise(
  #   length(unique(cb_col_name)),
  #   length(unique(col_name))
  # )
  group_by(cb_col_name) %>% 
  filter(row_number() == 1) %>% 
  ungroup() %>% 
  # Remove first row
  slice(-1)
```

```{r}
dim(tlfb_cb_col_names) # 146   4
```

## Standardize new column names

* Remove _tlfb and tlfb from column names
* Replace spaces with underscores
* Convert to lower case
* Add underscore in-between the abbreviated tool name and question number

```{r}
tlfb_cb_col_names <- tlfb_cb_col_names %>%
  mutate(
    # Remove _tlfb from column name
    # Remove tlfb at end of column name (e.g., DEM1tlfb)
    # Don't include values for col_name that were changed in the Word
    # document.
    col_name = if_else(
      is.na(col_name),
      str_replace(cb_col_name, "_tlfb|tlfb", ""),
      as.character(col_name)
    ),
    # Replace spaces with underscores
    col_name = str_replace_all(col_name, " ", "_"),
    # Convert to lower case
    col_name = str_to_lower(col_name),
    # Add underscore in-between the abbreviated tool name and question number
    col_name = str_replace(col_name, "([a-z])(\\d)", "\\1_\\2"),
    # Fix ptlfb -- an exception
    col_name = str_replace(col_name, "p_v_2", "pv_2")
  )
```

## Check for duplicate column names

Check to make sure this process didn't accidentally create any duplicate column names

```{r}
test_that("No duplicate col_names were created in the visit 2 data.", {
  check_dup_col_name <- tlfb_cb_col_names %>% 
    group_by(col_name) %>% 
    filter(max(row_number()) > 1) %>% 
    pull(col_name)
  
  expect_length(check_dup_col_name, 0)
})
```

## Save column names

Save tlfb_cb_col_names as a key that maps the new names to the old names in case we need that information in the future. Possibly for the codebook.

```{r}
tlfb_col_names_key <- tlfb_cb_col_names %>%  
  # Drop doc_index column
  select(-doc_index) %>% 
  # Add df identifier
  mutate(df = "tlfb") %>% 
  select(df, everything())
```

**NOTE:** col_name_keys.rds was created in data_survey_01_qds_v1_import.Rmd

```{r}
col_name_keys <- read_rds("data/col_name_keys.rds")
```

```{r}
col_name_keys[["tlfb"]] <- tlfb_col_names_key
# col_name_keys[["tlfb"]]
```

```{r}
write_rds(col_name_keys, "data/col_name_keys.rds")
```

```{r}
rm(col_name_keys, tlfb_cb_col_names, tlfb_cb_content)
```

## Differences between codebook columns and data columns

Check to see what differences, if any, exist between the columns in the codebook and the columns in the actual data frame.

```{r}
in_cb_not_df <- setdiff(tlfb_col_names_key$cb_col_name, names(tlfb))
in_cb_not_df
```

There are **0** column names in the codebook that don't appear in the data.  

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected columns exist in the codebook, but not the tlfb df.", {
  expect_equal(
    length(in_cb_not_df),
    0L
  )
})
```

Now, check for columns that exist in the data frame, but not the codebook.

```{r}
in_df_not_cb <- setdiff(names(tlfb), tlfb_col_names_key$cb_col_name)
in_df_not_cb
```

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected columns exist in the tlfb df, but not the tlfb codebook.", {
  expect_equal(
    length(in_df_not_cb),
    53L
  )
})
```

The remainder of these variables are calculated variables created by the SPSS export script. We will save them in a separate data frame and deal with them later. 

```{r}
tlfb_spss_calc_vars <- tlfb %>% 
  select(id = SUBJECT, visit = VISIT_tlfb, all_of(in_df_not_cb))
```

```{r}
write_sav(tlfb_spss_calc_vars, "data/tlfb_spss_calc_vars.sav")
```

Remove calculated variables from the tlfb data. This makes it easier to merge with the other QDS data frames later.

```{r}
tlfb <- tlfb %>% select(!all_of(in_df_not_cb))
```

```{r}
# Future proof this by checking to see if the variables have changed over time.
# If this test fails in the future, come back and make adjustments to how we 
# handle columns as needed.
test_that("The expected number of columns exist in the tlfb df after cleaning.", {
  expect_equal(
    length(names(tlfb)),
    146L
  )
})
```

Clean up

```{r}
rm(tlfb_spss_calc_vars, in_cb_not_df, in_df_not_cb)
```

## Replace variable names in the full data frame

Put them in the same order used in the codebook.

```{r}
tlfb <- tlfb %>% 
  select(all_of(tlfb_col_names_key$cb_col_name))

names(tlfb) <- tlfb_col_names_key$col_name
```


# ðŸ’¾Save the data frame

```{r}
path <- "/Volumes/Link2Care/Participant Data/R Data/qds_tlfb_import.rds"
```

```{r}
write_rds(tlfb, path)
```

Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "QDS Visit 2 saved to", path
)
```


# ðŸ—‘Clean up

```{r}
rm(tlfb_col_names_key, path)
```


# ðŸ–¨Print a message for when this file is being sourced

```{r}
cat(
  paste0(Sys.Date(), ":"),
  "QDS Visit 2 cleaned with", nrow(tlfb), "rows and", ncol(tlfb), "columns.\n"
)

# 2021-04-28: QDS Visit 2 cleaned with 247 rows and 146 columns.
```

```{r echo=FALSE}
sessionInfo()
```













