---
title: "Link2Care Survey Data - Update Individual Survey Data Frames"
date: "2021-07-28 <br> Updated: `r Sys.Date()`"
---

# â­ï¸Overview

This file we update all of the individual data frames that will make up the merged survey data frame. 


# ðŸ“¦Load packages

```{r}
source("R/source_rmd.R")
```


# ðŸŒŽConnect to UTH server 

```{bash eval=FALSE}
# Make sure you are connected to the VPN
open 'smb://islgpcifs.uthouston.edu/sph_research/'
```


# ðŸ“¥Import data 

We previously imported and did some initial cleaning of the following data sets:

* QDS (data_survey_01_qds_import.Rmd)   
* REDCap (data_survey_02_redcap_import.Rmd)    
* Master log (data_survey_03_master_log_import.Rmd)   
* Timeline followback (data_survey_04_tlfb_import.Rmd)   
* Arrest data (data_survey_05_arrests_import.Rmd)   
* Bridge sessions data (data_survey_06_bridge_sessions_import.Rmd) 

## QDS

```{r}
source_rmd("data_survey_01_qds_import.Rmd")

# 2021-07-30: v1 imported with 303 rows and 810 columns.
# 2021-07-30: v2 imported with 276 rows and 210 columns.
# 2021-07-30: v3 imported with 197 rows and 542 columns.
# 2021-07-30: v4 imported with 147 rows and 598 columns.
# 2021-07-30: v5 imported with 133 rows and 639 columns.
# 2021-07-30: QDS data imported and merged with 1056 rows and 1046 columns.
```

## REDCap

```{r}
source_rmd("data_survey_02_redcap_import.Rmd")

# 2021-07-30: REDCap data cleaned with 21 rows and 911 columns.
```

## Master log 

```{r}
source_rmd("data_survey_03_master_log_import.Rmd")

# 2021-07-30: Master log cleaned with 304 rows and 37 columns.
```

## Timeline followback 

```{r}
source_rmd("data_survey_04_tlfb_import.Rmd")

# 2021-07-30: TLFB data cleaned with 1212 rows and 21 columns.
```

## Arrest data

The arrest data is securely transmitted by Dr. Gonzalez as an Excel file, which is stored on the the UTHealth servers in Participant Data > Arrest Data Requests.

Before you can import the Excel file, you must open it and remove the password from the Excel sheet. File -> Passwords... -> Delete password.   

```{r}
source_rmd("data_survey_05_arrests_import.Rmd")

# 2021-07-30: Arrest data cleaned with 238 rows and 8 columns.
```

## Bridge sessions data

```{r}
source_rmd("data_survey_06_bridge_sessions_import.Rmd")

# 2021-07-30: Bridge session wide data cleaned with 300 rows and 20 columns.
```


# ðŸ”„Merge data 

```{r}
source_rmd("data_survey_21_merge.Rmd")

# 2021-07-30: Combined Participant data cleaned with 1078 rows and 1200 columns.
```


# ðŸ—‘Clean up

Don't use `rm(list = ls())` because is causes R to drop the helper functions in data_survey_21_update_all_data.Rmd

```{r}
rm(list = ls())
```

```{r echo=FALSE}
sessionInfo()
```

