---
title: "Link2Care Quarterly Report"
date: ""
output: 
  html_notebook:
    toc: true
    toc_float: true
    css: custom-css.css
---

# Overview {#overview}

* Thanks James. I'm looking at Tables 7-8 and it looks like 8 no showed for randomization in Table 7 but 9 did in table 8. Which is correct?  What is O/U on table 5? >1? This table needs some labels.

* Everything else looks ok. If Brad can just update or confirm the data in Tables 2-4 and add an arrest table, that would be great. And then I can reformat to make this look nice and we will be good to go.


* Delete this file and create a new file that generates formatted reports as soon as you figure out what you are doing.


# Load packages and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)
Sys.setenv(TZ = "US/Central")
```

```{r message=FALSE}
library(tidyverse)
library(bfuncs)
library(ggpubr)
```

[top](#top)


```{r}
screened_in <- readxl::read_excel("/Users/bradcannell/Desktop/L2C_Demographics.xlsx", sheet = "Screened In")
screened_out <- readxl::read_excel("/Users/bradcannell/Desktop/L2C_Demographics.xlsx", sheet = "Screened Out")
```


# Data management

## Stack screened-in and screened out

```{r}
# Variable to identify which data frame each record came from
screened_in$screened_in <- 1L
screened_out$screened_in <- 0L
# Bind rows
l2c <- bind_rows(screened_in, screened_out)
# Factorize screened_in variable
l2c$screened_in_f <- factor(l2c$screened_in, labels = c("Screened-Out", "Screened-In"))
# Drop individual data frames
rm(screened_in, screened_out)
```

```{r}
about_data(l2c) # 201 observations and 14 variables
```

## Format column names

```{r}
# Lower case
names(l2c) <- names(l2c) %>% tolower()
# Replaces spaces and slashes with underscores
names(l2c) <- stringr::str_replace_all(names(l2c), "\\s|\\/", "_")
```

## Drop empty columns and rows

```{r}
# Drop empty columns
l2c <- select(l2c, -starts_with("..."))
# Drop empty rows
l2c <- filter(l2c, !is.na(subject_id))
```

```{r}
about_data(l2c) # 195 observations and 11 variables
```

## Collapse races

```{r}
l2c <- l2c %>% 
  mutate(
    race = case_when(
      is.na(primary_race) ~ NA_character_,
      primary_race == "Black or African American" ~ "Black or African American",
      primary_race == "White" ~ "White",
      TRUE ~ "Other Race"
    )
  )
```

```{r}
about_data(l2c) # 195 observations and 12 variables
```

# Today's Date

```{r}
Sys.Date() # 2019-08-19
```

# Latest date consented

```{r}
max(l2c$date_consented) # 2019-08-09
```

# Participant counts

```{r}
l2c %>% 
  summarise(
    `Total Screened` = n(),                # 195
    `Screened-In` = sum(screened_in),      # 170
    `Screened-Out` = sum(screened_in == 0) # 25
  )
```

# Demographic characteristics of screened-in participants

```{r}
# Create helper function
n_percent <- function(df, x, d = 1) {
  out <- df %>% 
    count(!! enquo(x)) %>% 
    mutate(
      cumsum      = cumsum(n),
      percent     = (n / sum(n) * 100) %>% round(d) %>% format(nsmall = d),
      cum_percent = cumsum(percent),
      n_percent   = paste0(n, " (", percent, "%)"),
      var         = enquo(x) %>% quo_name(),
      cat         = !! enquo(x)
    ) %>% 
    # arrange(desc(n)) %>% 
    select(var, cat, n, percent, n_percent)
  
  out
}
```

### Ages

```{r}
ages <- l2c %>% 
  group_by(screened_in_f) %>% 
  summarise(
    n = n(),
    mean = mean(age) %>% round(1),
    n_mean = paste0(n, " (", mean, ")"),
    min = min(age),
    max = max(age)
  ) %>% 
  print()
```

### Categorical variables

```{r message=FALSE, rows.print=15}
cat_stats <- map_df(
  .x = quos(gender, race, hispanic_latino), 
  .f = n_percent,
  df = l2c %>% group_by(screened_in_f)
) %>% 
  arrange(desc(screened_in_f), var, desc(n)) %>% 
  print()
```

[top](#top)


# Arrests

* Have to get the arrest data from Jenn in a secure email.

* Merge with demographics data so that I know which arm they are in.

```{r message=FALSE}
arrests <- readxl::read_excel("/Users/bradcannell/Desktop/arrest data.xlsx")
arrests <- select(arrests, ID, ArrestedYN) %>% rename(subject_id = ID, arrested = ArrestedYN)
arrests <- arrests %>% left_join(l2c, by = "subject_id")
arrests <- arrests %>% select(subject_id, arrested, l2c)
arrests <- arrests %>% filter(!l2c == "Dropped")
```

```{r}
about_data(arrests) # 27 observations and 3 variables
```

```{r}
gmodels::CrossTable(arrests$l2c, arrests$arrested, fisher = TRUE)
```



# Plots

http://www.sthda.com/english/articles/32-r-graphics-essentials/126-combine-multiple-ggplots-in-one-graph/

```{r}
p_ages <- ggplot(l2c, aes(screened_in_f, age)) +
  geom_jitter(aes(col = screened_in_f), width = 0.20) +
  geom_segment(
      aes(x = c(0.75, 1.75), y = mean, xend = c(1.25, 2.25), yend = mean, col = screened_in_f), 
      size = 1.5, data = ages
    ) +
  annotate(
    "label", 
    x = c(1, 2), 
    y = ages$max, 
    label = paste("Max =", ages$max),
    vjust = -1
  ) +
  annotate(
    "label", 
    x = c(1, 2), 
    y = ages$mean, 
    label = paste("Mean =", ages$mean)
  ) +
  annotate(
    "label", 
    x = c(1, 2), 
    y = ages$min, 
    label = paste("Min =", ages$min),
    vjust = 1.5
  ) +
  expand_limits(y = c(min(ages$min) - 4, max(ages$max) + 4)) +
  scale_x_discrete("Screening Status") +
  scale_y_continuous("Age (Years)") +
  scale_color_manual(values = c("#BC581A", "#00519B")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 12))

p_ages
```

```{r}
cat_stats %>% 
  filter(var == "race") %>% 
ggplot() +
  geom_col(aes(x = cat, y = n, fill = screened_in_f), position = "dodge2") + 
  scale_x_discrete("Race") +
  scale_y_continuous("Count") +
  scale_fill_manual("Screening Status", values = c("#BC581A", "#00519B")) +
  theme_classic()
```







# Session information

```{r echo=FALSE}
rm(list = ls())
```

```{r echo=FALSE}
sessionInfo()
```