---
title: "Import and manage Link2Care Survey Data - QDS Visit 1"
date: "2020-12-23 <br> Updated: `r Sys.Date()`"
---

**Delete when done:** 
2021-01-29: Michael and I had a chat on the phone. He wants all the f/u survey data put into a single complete data frame (QDS, REDCapp, all variables from all visits cleaned) by May 1. That's what I'm attempting to do with this file. Notes/Tasks can be viewed/updated here: https://app.asana.com/0/1152061965261457/1199715313921388

# ⭐️Overview

This file is used to import the Link2Care follow-up visit survey data and do some initial data cleaning (e.g., create calculated variables). 

**NOTE on using multiple import code files:**
Previously, I was trying to clean all the separate data frames (i.e, QDS v1-v5, REDCap, and Master Log) in a single Rmd file. 

In theory, this is more efficient than importing and cleaning each visit file separately. For example, we can clean "race" instead of cleaning "race_v1", "race_v2", etc.

However, there are at least two issues with that approach:   
1. There are intentional differences in the variable names (e.g., "V1" and "V2"), and unintentional errors (e.g., HEIGHT_3) in the variable names, from data frame to data frame that make combining them very difficult.   
2. These differences and errors can be "fixed"; however, doing so makes the variable names so different from the codebook that the codebook is barely usable.

For now, I'm going to try importing and cleaning each data file using a separate code file. There may be opportunities to make this more efficient in the future.

**NOTE on data sources:**
* The QDS data is exported from QDS in SPSS data format. The data has to be exported by visit (i.e., v1, v2, ... v5). The SPSS data is then added to the UTHealth servers.

* Some of the v3-v5 visits are also done using REDCap. That data is exported from REDCap and added to the UTHealth servers.

**NOTE on Kiteworks:**
Currently, I'm importing all of this data from the UTHealth server. The data should also be available on Kiteworks if you are unable to connect to the server for some reason.


# 📦Load packages

```{r message=FALSE}
library(dplyr)
library(haven)
library(readxl)
library(purrr)
library(tidyr)
library(stringr)
library(forcats)
library(officer)
```

```{r}
source("R/nines_to_na.R")
source("R/spss_to_fs.R")
```


# 🌎Connect to UTH server 

```{bash eval=FALSE}
# Don't drill all the way down to live documents because not all of the data is in live documents.
open 'smb://islgpcifs.uthouston.edu/sph_research/Link2Care/'
```


# 📥Import data 

```{r}
v1 <- read_sav("/Volumes/Link2Care/Participant Data/SPSS Data/QDS Data/Visit_1_Data.SAV")
dim(v1) # 264 803
```


# 🚧Data management 

## Remove columns of missing data

There are quite a few columns that have missing values for all rows. We
drop those columns below.

```{r}
v1 <- v1 %>% 
  select(
    where(
      ~ !all(is.na(.x))
    )
  )
```

```{r}
ncol(v1) # 795 So, 803 - 795 = 8 columns dropped.
```

## Clean variable names

**NOTE on changing variable names**

The variable names aren't very descriptive. At first, my plan was to resist the urge to change them in this file. My thought was that I wanted the data that comes out of this file to have variable names that match the variables names in the codebook files. Then I realized, however, that none of the calculated variables will be in the codebook files anyway. Also, there isn't a codebook file for the combined survey data set. So, we can go ahead and rename variables in this file. We will either have to create a new codebook for the combined data or just live without one. 

Having said that, completely changing variable names (e.g., SQ_2 to hispanic) may not be appropriate for this file for a couple of reasons:
1. It isn't necessarily a high priority for the team and we are on a tight deadline.
2. Others may not like the names I select. Instead of creating descriptive variable names in this file, we can use descriptive variable names in the individual analysis files as needed.

So, in this file, we will standardize names (e.g., drop "_V1", "HEIGHT_3") so that they are consistent across the various data files and can be merged.

Additionally, we will:
1. Convert all variable names to lower, snake case.
2. Create all calculated/created variables using lower, snake case.

**NOTES on naming conventions**
* The typical way that variables are named in these data sets is: 
  - <abbreviated_tool_name><question_number>[optionally:dummy_variable_lettered]
    + For example: BPM1_V1, LSN3_V1
  - <abbreviated_tool_name>_<question_number>[optionally:dummy_variable_lettered]
    + For example: Screening Question 2 is named: SQ_2
    + OR: The dummy variable for the "EMAIL" Response to Screening Question 18 is: SQ_18A
  - Many questions also have the visit number embedded in the name.
    + For example: Demographics question 1 is: DEM1V1.
  - However, there are some exceptions to this rule - intentional or not.
    + For example, the fifth MMSE question is: MMS4V

* In order to improve consistency in the variable names, we will adopt the following convention:
  - <abbreviated_tool_name><question_number>[optionally:dummy_variable_lettered]
    + dummy variables will be numbered a-z
    + For example, sq12, t14a
  - We will drop visit number from the variable name an use an explicit visit variable.
  - Exceptions: Demographic variables that almost anyone should be reasonably able to understand without the codebook will be given intuitive, descriptive names (e.g., age, race, gender, marital_status, etc.)

**NOTE on coercing categorical variables to factors**

Originally, I was coercing categorical variables to factors in this code. However, I decided not to do that anymore because it isn't necessarily a high priority for the team and we are on a tight deadline. In fact, others may not even use R for analysis in which case the factor information would be lost entirely. Instead, we can convert categorical variables to factors in the individual analysis files as needed.

**NOTE on recoding 7, 9, 99, etc. to NA**

Originally, I was converting 7, 9, 99, etc. to NA in this code. However, I decided not to do that anymore because it isn't necessarily a high priority for the team and we are on a tight deadline. In fact, others may want to be able to compare "Don't know" and "Refused", which wouldn't be possible if I convert them all to NA here. Instead, we can convert 7, 9, 99, etc. to NA in the individual analysis files as needed.

Therefore, in this file, just clean up the variable names so that they can be merged and create the calculated variables. 

### Read-in variable names from codebook

Using this method, as opposed to typing the variable names in manually, has a couple of advantages:
1. It greatly reduces the risk of typos.
2. It clearly maps any changes between the original codebook name and the new name being used.
3. It may potentially save some time.

Instructions:
* Open the RTF version of the codebook (e.g., L2C_V1 Codebook.RTF), which can be downloaded from the UDrive/Kiteworks.
* Create a .docx version of the codebook using "save as" in Word.
* Create a "cb_col_name" style to identify existing variable names
  - Open styles pane, click "New Style..."
  - Name the new style cb_col_name and change the text color to red (optional).
* Create a "col_name" style to identify new variable names
  - Open styles pane, click "New Style..."
  - Name the new style col_name and change the text color to green (optional).
* Start marking variable names as such
  - Place cursor immediately after each variable name and press the return key. Each variable name needs to be on its own line.
  - Place cursor in each variable name and change the style to cb_col_name in the styles pane.
* Create new/alternate variable names
  - Place cursor immediately after each variable name and press the return key again.
  - Type the new/alternate variable names.
    + Don't worry about capitalization or underscores. We will fix that programmatically below.
    + Do worry about correct spelling.
  - Place cursor in each variable name and change the style to col_name in the styles pane.
* Use a similar procedure for section_name
  - Only include sections that actually have questions in them.
    + For example, NOT Sect-24.	NEGATIVE/POSITIVE AFFECT
  
Assign keyboard shortcut to a style (optional):
* In styles pane, click drop down arrow to the right of the style name (e.g., cb_col_name).
* Click "Modify style..."
* Click "Format" drop down in the bottom left corner of the dialogue box.
* Click "Shortcut Key..."
* Enter the new shortcut key in the "Press new keyboard shortcut:" box.
* Click assign.
* Save changes in the local file.
* Click OK.
  
#### Extract content from Word codebook

```{r}
v1_cb_content <- read_docx("codebooks/L2C_V1 Codebook.docx") %>% 
  docx_summary()
```

#### Keep the variables of interest only

```{r}
v1_cb_col_names <- v1_cb_content %>%
  filter(style_name%in% c("section_name", "cb_col_name", "col_name")) %>% 
  select(doc_index, style_name:text) %>% 
  pivot_wider(
    names_from = "style_name",
    values_from = "text"
  )
```

#### Clean section names

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  mutate(
    # Remove "Sect-number."
    section_name = str_remove(section_name, "Sect-\\d{1,}."),
    # Remove asterisks
    section_name = str_remove_all(section_name, "\\*"),
    # Remove empty spaces
    section_name = str_trim(section_name),
    # Clean " (SQ_7 - SQ_11)" from exclusion criteria
    section_name = str_remove(section_name, " \\(SQ_7 - SQ_11\\)")
  ) %>% 
  # Fill section down across rows
  fill(section_name)
```

#### Record the sections that are at visit 1

We will use this for checking to make sure all of the correct questionnaire sections merged later.

```{r}
q_sections <- list(v1 = unique(v1_cb_col_names$section_name))
q_sections[["v1"]]
```

#### Reduce to one row per column

Currently, cb_col_name and col_name are on separate rows. We will spread the different column names vertically across rows so that we can reduce the data frame down to one row per column.

```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  # Spread cb_col_name across rows
  fill(cb_col_name) %>% 
  # Spread col_name across rows within cb_col_name
  group_by(cb_col_name) %>% 
  fill(col_name, .direction = "up") %>% 
  # # For data checking
  # filter(section_name == "Self-Rated Health Questionnaire") %>%
  # ungroup() %>%
  # slice(-1) %>%
  # summarise(
  #   length(unique(cb_col_name)),
  #   length(unique(col_name))
  # )
  group_by(cb_col_name) %>% 
  filter(row_number() == 1) %>% 
  ungroup() %>% 
  # Remove first row
  slice(-1)
```

```{r}
dim(v1_cb_col_names) # 724   4
```

#### Remove _V1 and V1 from column names

Left off here...
Just finished cleaning the self-rated health section. Pick back up at PTSD. Make sure col_name matches naming conventions.

```{r}
# v1_cb_col_names <- 
v1_cb_col_names %>%
  mutate(
    # Remove _V1 from column name
    # Remove V1 at end of column name (e.g., DEM1V1)
    # Don't include values for col_name that were changed in the Word
    # document.
    col_name = if_else(
      is.na(col_name),
      str_replace(cb_col_name, "_V1|V1", ""),
      col_name
    )
  )
```

Check to make sure this didn't create any duplicate column names

```{r}
v1_cb_col_names %>% 
  group_by(col_name) %>% 
  filter(max(row_number()) > 1)
```


```{r}
v1_cb_col_names <- v1_cb_col_names %>%
  mutate(
    # Remove _V1 from column name
    # Remove V1 at end of column name (e.g., DEM1V1)
    # Don't include values for col_name that were changed in the Word
    # document.
    col_name = if_else(
      is.na(col_name),
      str_replace(cb_col_name, "_V1", ""),
      col_name
    ),
    # Replace spaces with underscores
    col_name = str_replace_all(col_name, " ", "_"),
    # Convert to lower case
    col_name = str_to_lower(col_name),
    # Remove underscore between SQ and number for screening questions
    # The vast majority of the other variable names don’t have an underscore 
    # between the abbreviated tool name and the question number. Taking out the 
    # underscore to make SQ consistent.
    col_name = str_replace(col_name, "^sq_", "sq"),
    # Remove underscore between MMS and number for screening questions
    # The vast majority of the other variable names don’t have an underscore 
    # between the abbreviated tool name and the question number. Taking out the 
    # underscore to make MMS consistent.
    col_name = str_replace(col_name, "(^mms_)(\\d)", "mms\\2"),
    # The demographics variables don't have _V1 at the end. Instead, they have
    # V1 at the end. But sometimes there is a letter after the V1. We will take
    # those out here
    col_name = str_replace(col_name, "(^dem\\d)(V1)", "\\1")
  )

v1_cb_col_names
```

Replace variable names in the full data frame

Put them in the same order used in the codebook.

**NOTE:** The codebook includes a variable called TEST_V1. This doesn't seem to be in the data.

```{r}
v1_col_order <- v1_cb_col_names %>% 
  # The codebook includes a variable called TEST_V1. This doesn't seem to be in 
  # the data.
  filter(cb_col_name != "TEST_V1") %>% 
  pull(cb_col_name)
```

```{r}
test_section <- v1 %>% 
  select(all_of(v1_col_order))

names(test_section) <- v1_cb_col_names %>% 
  # The codebook includes a variable called TEST_V1. This doesn't seem to be in 
  # the data.
  filter(cb_col_name != "TEST_V1") %>% 
  pull(col_name)

test_section
```




































# 🗑Clean up

```{r}
rm(nines_to_na, spss_to_fs)
```













