---
title: "Overview and Guide - Variable Map Creation, Modification, and Utility"
date: "2022-10-02 <br> Updated: `r Sys.Date()`"
format: pdf
editor: 
  markdown: 
    wrap: sentence
---

# ⭐️Overview

This file is intended to provide a high-level overview of the **variable map** structure utilized in the processing of the Link2Care data sets and creation of a combined data set. It includes a rationale for why the variable map structure was created, an example of how to read and interpret the variable map, and example uses of the related functions/scripts written for this structure.

## Note

This file is a work in progress. The helper functions are being revised as the data is being processed, and additional challenges/needs are noted. This file will be finalized and polished at the end of the project process. If one of the helper functions fails to work as expected, the most up-to-date information will be in the script itself.

# 📦Load Packages & Functions

```{r, message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(tibble, warn.conflicts = FALSE)
library(here, warn.conflicts = FALSE)
```

```{r}
source(here("R", "standardize_col_names.R"))
source(here("R", "vm_check.R"))
source(here("R", "flag_unmatching_variables.R"))
source(here("R", "vm_make_source_map.R"))
source(here("R", "vm_create_for_instrument.R"))
source(here("R", "vm_join_inst_section.R"))
source(here("R", "vm_join_sections.R"))
source(here("R", "vm_add_variable.R"))
source(here("R", "vm_delete_variable.R"))
source(here("R", "vm_process_source_df.R"))
source(here("R", "vm_process_many_source.R"))
source(here("R", "vm_factor_apply_val_labels.R"))
```

# Why create a variable map?

1.  This file explains the **variable map**. This variable map is used to facilitate batch processing of the Link2Care variables in other files in the data pipeline.

-   The variable map allows for a single "map" to trace data from the source data set to the final combined/processed data set.
-   The variable map allows for further changes, such as renaming a variable, to be accounted for with a single point modification rather than multiple fixes.
-   The variable map allows for storage and enforcement of attributes such as labels that may be lost in modification processes
-   The variable map allows for specific variables to be flagged, such as by creating a `calculated` column to flag variables created through calculation or `phi` to mark variables for blocking in a codebook or other display.

2.  This is beneficial because the columns in the data are not arranged in the order that they exist in the actual surveys. This makes the data harder to work with, and it will make the codebook we eventually create difficult to use. So, we need to reorder them in the order that they appear in the Link2Care appendix (`codebooks/from_qds/Link2Care_Appendix.pdf`). We create the **variable map** to facilitate the variable ordering process.

-   The Link2Care appendix is organized by section, then instrument, then individual items within an instrument. Ordering of the variables in the combined data should mirror this as closely and reasonably as possible.

    -   The variable map contains 6 primary variables reflecting this desired order:

        -   `variable`: the desired standardized variable name (string)

        -   `section`: the human-readable section name (string)

            -   This human-readable value may also be useful in a codebook, if the section name is desired.

        -   `sec_ord`: the number indicating the order of the **section** within the appendix (integer)

            -   1 is the first section, 2 is the second, and so on

        -   `instrument`: human-readable instrument name (string)

            -   This human-readable value may also be useful in a codebook, if the instrument name is desired.

        -   `inst_ord`: the number indicating the order of the **instrument** within the **section** in the appendix (integer)

            -   1 is the first instrument within a section, 2 is the second, and so on

        -   `item_ord`: the number indicating the order of the **item** within the **instrument**.

            -   1 is the first item within an instrument, 2 is the second, and so on.

-   Some variables in the data do not belong to an instrument in the Link2Care appendix. For example, the questions about COVID vaccines. We can initially order them after the columns that do appear in the Link2Care appendix following the base logic of the Link2Care appendix. However, we must anticipate needing to reorder instruments, sections, or individual variables.

-   The **variable map** structure will facilitate future changes by acting as a single 'choke point'.

    -   Insertion or deletion of a variable may be achieved by changing/shifting values of `item_ord`

        -   This is particularly useful for positioning calculated variables.

    -   Sections may be reordered by changing/shifting `sec_ord`

    -   Instruments may be reordered within sections by changing/shifting `inst_ord`

    -   Moving an instrument to another section will require changing/shifting `section`, `sec_ord`, and `inst_ord`

3.  Each data set has different names for the same variables, including unique typos.

-   The **variable map** accounts for this constraint. For *n* number of source data sets, we require *n+1* columns.

    -   `variable`: the desired standardized variable name (string). This column should only appear once.

    -   `(descriptive name for the source data set)`: the variable name in the source data set (string)


4.  We want to re-create variables that were calculated in SPSS, rather than relying on their imported values.

-   The map organization system allows us to insert variables to ensure a human-readable ordering.
-   The map organization system also allows us to delete variables or exclude them from batch processing.

## Example of reading, manipulating, and utilizing the variable map

# Examples

## Example Data Structures

The following is a small set of dummy data that takes the form of a variable map.

```{r}
example_map <- vm_join_sections(list(
                  vm_join_inst_section('section A', list(
                      vm_create_for_instrument('example', 
                              c('ex_1', 'ex_2', 'ex_3', 'ex_4', 'ex_5')),
                      vm_create_for_instrument('learning', 
                              c('lrn_1', 'lrn_2', 'lrn_3', 'lrn_4', 'lrn_5'))
                        )
                      ),
                  vm_join_inst_section('section B', list(
                      vm_create_for_instrument('teaching', 
                              c('tch_1', 'tch_2', 'tch_3', 'tch_4', 'tch_5')),
                      vm_create_for_instrument('visualizing', 
                              c('vis_1', 'vis_2', 'vis_3', 'vis_4', 'vis_5'))
                        )
                      )
                    )
                  ) %>%
  add_column('exdf_v1' = c('EX_1_V1','EX_2_V1', 'EX_3_V1', 'EX4_V1','EX_5_V1',
                          'LEARN1_V1', 'LEARN2_V1', 'LEAN3V1', 'LEARN4_V1', 
                          'LEARN_5_V1', 'TEA1V1', 'TEA2V1', 'TEA3V1', 'TEA4V1', 
                          'TEA_5V1', 'V_1_1', 'V_2_V1', 'V_3_V1', 'V_4_V', 
                          'V5_V1'),
             'exdf_v2' = c('EX_1_V2','EX_2_V2', 'EXAMP_3_V2', 'EX_4_V2','EX_5_V2',
                          'LEARN1_V2', 'LEARN2_V2', 'LEARN_3_V2', 'LEARN4_V2', 
                          'LEARN_5_V2', 'TEA1V2', 'TEA2V2', 'TEA3V2', 'TEA4V2', 
                          'TEA_5V2', 'V_1_V2', 'V_2_V2', 'V_3_V2', 'V4_V2', 
                          'V5_V2'),
             'exdf_v3' = c('EX_1_V3','EX_2_V3', 'EXAMP_3_V3', 'EX_4_V3','EX_5_V3',
                          'LN1_V3', 'LN2_V3', 'LN_3_V3', 'LN4_V3', 
                          'LN_5_V3', 'TEA1V3', 'TEA2V3', 'TEA3V3', 'TEA4V3', 
                          'TEA5V3', 'V_1_V3', 'V_2_V3', 'V_3_V3', 'V_4_V3', 
                          'V_5V3'),
             attr_label = c('Example Subject ID', 'Example Visit Number', 
                            'Example Data Collection Date', 
                            'Example Interviewer', 'Example Collection Method',
                            'Are you learning?', 'Learn a number', 
                            'Learn a color', 'Learn a word', 
                            'Learn a new number',
                            'Find this color', 'Pick the third word',
                            'How many cups are on the table?', 
                            'Pick a word you enjoy', 'Multiply your numbers',
                            'Correct the spelling of this word',
                            'Which of these math problems has the wrong answer?',
                            'Is it raining today?', 'Do you like cats?', 
                            'Did you enjoy this test?')
             ) %>%
  mutate(attr_var_labels = case_when(
    variable == 'ex_1' ~ list(c(
      'David' = 1, 'Marie' = 2, 'Jason' = 3, 'Caroline' = 4, 'Alex' = 5
      )),
    variable == 'ex_2' ~ list(c(
      'Visit 1: Baseline' = 1, 'Visit 2: 30 day followup' = 2, 
      'Visit 3: Exit' = 3
      )),
    variable == 'ex_3' ~ list(NULL),
    variable == 'ex_4' ~ list(c(
      "Adam" = 'AAA', 'Billie' = 'BBB', 'Charlie' = 'CCC', 'Delta' = 'DDD'
      )),
    variable == 'ex_5' ~ list(c(
      'in person' = 1, 'telephone' = 2, 'mail' = 3
      )),
    variable == 'lrn_1' ~ list(c(
      'Yes' = TRUE, 'No' = FALSE
      )),
    variable == 'lrn_2' ~ list(NULL),
    variable == 'lrn_3' ~ list(NULL),
    variable == 'lrn_4' ~ list(NULL),
    variable == 'lrn_5' ~ list(NULL),
    variable == 'tch_1' ~ list(NULL),
    variable == 'tch_2' ~ list(NULL),
    variable == 'tch_3' ~ list(NULL),
    variable == 'tch_4' ~ list(NULL),
    variable == 'tch_5' ~ list(NULL),
    variable == 'vis_1' ~ list(NULL),
    variable == 'vis_2' ~ list(NULL),
    variable == 'vis_3' ~ list(c(
      "Yes" = TRUE, "No" = FALSE
      )),
    variable == 'vis_4' ~ list(c(
      "Yes" = TRUE, "No" = FALSE
    )),
    variable == 'vis_5' ~ list(c(
      "Yes" = TRUE, "No" = FALSE
    ))
  )) %>%
  add_column(calculated = FALSE, drop_consolidated = FALSE, phi = FALSE)
```

The following are small sets of dummy data that represent the source data frames in our examples.

```{r}
variable_labels <- c(
  'Example Subject ID', 'Example Visit Number', 'Example Data Collection Date', 
  'Example Interviewer', 'Example Collection Method',
  'Are you learning?', 'Learn a number', 'Learn a color', 'Learn a word', 
  'Learn a new number',
  'Find this color', 'Pick the third word', 'How many cups are on the table?', 
  'Pick a word you enjoy', 'Multiply your numbers',
  'Correct the spelling of this word', 
  'Which of these math problems has the wrong answer?',
  'Is it raining today?', 'Do you like cats?', 'Did you enjoy this test?'
  )

variable_value_labels <- list(list(c(
      'David' = 1, 'Marie' = 2, 'Jason' = 3, 'Caroline' = 4, 'Alex' = 5
      )),
     list(c(
      'Visit 1: Baseline' = 1, 'Visit 2: 30 day followup' = 2, 
      'Visit 3: Exit' = 3
      )), 
     list(NULL),
     list(c(
      'Adam' = 'AAA', 'Billie' = 'BBB', 'Charlie' = 'CCC', 'Delta' = 'DDD',
      'Epsilon' = 'EEE'
      )),
     list(c(
      'in person' = 1, 'telephone' = 2, 'mail' = 3
      )),
     list(c(
      'Yes' = TRUE, 'No' = FALSE
      )),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(NULL),
     list(c(
      "Yes" = TRUE, "No" = FALSE
      )),
     list(c(
      "Yes" = TRUE, "No" = FALSE
    )),
    list(c(
      "Yes" = TRUE, "No" = FALSE
    ))
    )

exdf_v1 <- tibble::tibble(
  'TEA4V1' = c('challenge', 'notebook', 'doctor', 'frantic', 'organic'), 
  'TEA_5V1' = c(48, 253, 272, 313, 477), 
  'V_1_1' = c('coast', 'unsightly', 'purpose', 'condemned', 'drag'),
  'EX_3_V1' = c('2020-10-01', '2020-10-02', '2020-10-03', '2020-10-04',
                '2020-10-05'), 
  'EX4_V1' = c('AAA', 'BBB', 'CCC', 'DDD', 'EEE'),
  'EX_5_V1' = c('in person', 'in person', 'telephone', 'mail', 'telephone'),
  'LEARN1_V1' = c(TRUE, TRUE, FALSE, FALSE, TRUE), 
  'LEARN2_V1' = c(1, 4, 8, 16, 18), 
  'V_4_V' = c(FALSE, TRUE, TRUE, FALSE, TRUE), 
  'V5_V1' = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  'LEAN3V1' = c('#69b1c3', '#40d449', '#02dda0', '#0775d4', '#77fe9d'), 
  'LEARN_5_V1' = c(2, 4, 16, 17, 20), 
  'EX_1_V1' = c(1, 2, 3, 4, 5),
  'EX_2_V1' = c(1, 1, 1, 1, 1), 
  'TEA1V1' = c('#4443f7', '#71702b', '#4635a9', '#aad37a', '#aeb8c4'), 
  'TEA2V1' = c('allow', 'ad hoc', 'cheer', 'float', 'rhythm'), 
  'TEA3V1' = c(4, 7, 8, 15, 20), 
  'V_2_V1' = c(1, 7, 15, 16, 19), 
  'V_3_V1' = c(TRUE, FALSE, FALSE, TRUE, TRUE), 
  'LEARN4_V1' = c('fail', 'stir', 'sharp', 'trite', 'concern')
)

for (var_name in colnames(exdf_v1)){
  attributes(exdf_v1[[var_name]])$label <- 
    variable_labels[which(example_map$exdf_v1 == var_name)]
  attributes(exdf_v1[[var_name]])$labels <- 
    variable_value_labels[[which(example_map$exdf_v1 == var_name)]]
}

exdf_v2 <- tibble::tibble(
  'EXAMP_3_V2' = c('2020-11-01', '2020-11-02', '2020-11-03', '2020-11-04',
                   '2020-11-05'), 
  'EX_4_V2' = c('AAA', 'BBB', 'CCC', 'DDD', 'EEE'),  
  'EX_1_V2' = c(5, 2, 3, 1, 4),
  'V_3_V2' = c(FALSE, TRUE, TRUE, TRUE, FALSE), 
  'V4_V2' = c(FALSE, TRUE, FALSE, TRUE, TRUE), 
  'LEARN1_V2' = c(TRUE, TRUE, FALSE, FALSE, TRUE), 
  'LEARN2_V2' = c(2, 3, 9, 18, 19), 
  'EX_2_V2' = c(2, 2, 2, 2, 2), 
  'EX_5_V2' = c('mail', 'telephone', 'in person', 'in person', 'in person'),

  'LEARN_3_V2' = c('#f9ab20', '#41d85c', '#62b9e2', '#ff5eb1', '#d62fe1'), 
  'LEARN4_V2' = c('ablaze', 'scrub', 'gaudy', 'reaction', 'abandoned'), 
  'LEARN_5_V2' = c(2, 5, 12, 14, 15), 
  'EX_DROP_ME' = c(1, 1, 1, 1, 1),
  'TEA3V2' = c(5, 7, 11, 15, 16), 
  'TEA4V2' = c('sedate', 'unkempt', 'zealous', 'copy', 'launch'),
  'TEA_5V2' = c(221, 237, 397, 401, 405), 
  'V_1_V2' = c('wasteful', 'popcorn', 'sordid', 'simple', 'whine'), 
  'V_2_V2' = c(1, 2, 5, 12, 19), 
  'TEA1V2' = c('#e2999e', '#41d5b7', '#ec1c4d', '#ec1c4d', '#8a2f1f'), 
  'TEA2V2' = c('disgusted', 'hard-to-find', 'interesting', 
               'important', 'uttermost'), 
  'V5_V2' = c(TRUE, TRUE, TRUE, TRUE, FALSE),
  
)

for (var_name in colnames(exdf_v2)[!colnames(exdf_v2) == 'EX_DROP_ME']){
  attributes(exdf_v2[[var_name]])$label <- 
    variable_labels[which(example_map$exdf_v2 == var_name)]
  attributes(exdf_v2[[var_name]])$labels <- 
    variable_value_labels[[which(example_map$exdf_v2 == var_name)]]
}

exdf_v3 <- tibble::tibble(
  'EX_1_V3' = c(2, 3, 4, 5, 1),
  'EX_2_V3' = c(3, 3, 3, 3, 3),
  'V_3_V3' = c(TRUE, TRUE, FALSE, FALSE, TRUE), 
  'TEA4V3' = c('icicle', 'window', 'apparel', 'spooky', 'swanky'),
  'TEA5V3' = c(49, 130, 322, 372, 470), 
  'V_4_V3' = c(TRUE, TRUE, TRUE, FALSE, FALSE), 
  'V_5V3' = c(FALSE, TRUE, TRUE, TRUE, FALSE),
  'LN_3_V3' = c('#9eb25a', '#7ef5ea', '#d5cd00', '#96ee8c', '#facd88'), 
  'LN4_V3' = c('hideous', 'entertain', 'married', 'base', 'rice'), 
  'EXAMP_3_V3' = c('2020-12-01', '2020-12-02', '2020-12-03', '2020-12-04',
                   '2020-12-05'), 
  'EX_4_V3' = c('AAA', 'BBB', 'CCC', 'DDD', 'EEE'),
  'LN_5_V3' = c(4, 8, 12, 13, 19), 
  'TEA1V3' = c('#ae226b', '#74ac37', '#c088be', '#ebec20', '#03496e'), 
  'TEA2V3' = c('nippy', 'base', 'mix', 'zoo', 'trousers'), 
  'TEA3V3' = c(8, 14, 18, 19, 20), 
  'V_1_V3' = c('bang', 'kittens', 'rambunctious', 'stove', 'ethereal'), 
  'V_2_V3' = c(1, 8, 11, 12, 15), 
  'EX_5_V3' = c('telephone', 'telephone', 'telephone', 'mail', 'in person'),
  'LN1_V3' = c(TRUE, TRUE, FALSE, FALSE, TRUE), 
  'LN2_V3' = c(8, 10, 14, 15, 17), 
)

for (var_name in colnames(exdf_v3)){
  attributes(exdf_v3[[var_name]])$label <- 
    variable_labels[which(example_map$exdf_v3 == var_name)]
  attributes(exdf_v3[[var_name]])$labels <- 
    variable_value_labels[[which(example_map$exdf_v3 == var_name)]]
}
```

## Reading a Variable Map

The variable map was intended to be human readable, such as if it were exported as an excel file. We created a small set of dummy data to provide an example on how to read this variable map.

```{r}
example_map
```

To orient, we examine the first row:

The standardized variable name is `ex_1` (`variable`). It is the first item (`item_ord`) a part of the 'example' instrument (`instrument`), which is the first instrument (`inst_ord`) in the section 'section A' (`section`), the first section overall (`sec_ord`). The next 3 columns tell us where this value originated: the name of the variable in the source data set(s).

In this case, `ex_1` came from the variable `EX_1_V1` in "exdf_v1", `EX_1_V2` in "exdf_v2", and `EX_1_V3` in "exdf_v3". 

We see the variable label is 'Example Subject ID' (`attr_label`). From `attr_var_labels`, we can see that a value of 1 corresponds to "David", 2 to "Marie", 3 to "Jason", 4 to "Caroline", and 5 to "Alex".

We can also see that this variable is NOT calculated (`calculated` == FALSE), is not marked to be dropped in consolidation (`drop_consolidated` == FALSE), and is not considered phi (`phi` == FALSE).

```{r}
example_map[1,]
```

While the source variables for `ex_1` appeared fairly standardized in their source data sets, this is not always the case. In looking at the third row, for variable `ex_3`, we see several variations in how the corresponding variable was named in the source data sets. In this case, `ex_2` came from the variable `EX_3_V1` in "exdf_v1", `EXAMP_3_V2` in "exdf_v2", and `EXAMP_3_V3` in "exdf_v3".

Despite this variation, this map helps us ensure all of those source values map appropriately into `ex_3` in the combined data set.

```{r}
example_map[3,]
```

## Checking Variable Map Structure (`vm_check()`)

There is a required structure for a variable map to be valid and effective. A function was created to perform this check, return a boolean/logical value indicating if it is valid or invalid, and provide description of the issue if the variable map is invalid.

The function checks that:
1. Each 'variable' is unique
2. Each 'section' is consistently represented by a single value of 'sec_ord', and no two sections share the same order
3. Each 'instrument' is consistently represented by a single value of 'inst_ord'
There is only one 'instrument' for each 'inst_ord' within the same 'section'
5. That each 'instrument' only appears within one 'section'

```{r}
vm_check(example_map)
# TRUE
```

## Creating a Variable Map

We wish to process all three of our source data frames (`exdf_v1`, `exdf_v2`, and `exdf_v3`). To facilitate this, we create a packaged list of sources.

```{r}
source_df_list <- list(
  'exdf_v1' = exdf_v1, 'exdf_v2' = exdf_v2, 'exdf_v3' = exdf_v3
  )
```

We also initiate a list of variables to drop. This list may be used to store specific variables for exclusion in order to record that a variable was deliberately intended for exclusion in processing.

```{r}
dropping_var_list <- list(
  'exdf_v1' = c(), 'exdf_v2' = c(), 'exdf_v3' = c()
  )
```


### Examining Variables in an Instrument (`flag_unmatching_variables()`)

In `example_map` created above, we nested several of our creation functions at once. Now that the overall structure is demonstrated, the creation may be understood in greater detail.

Creation starts at the instrument level. For our example, let's say our source data has an instrument called "example" with 5 items. When looking at our column names in each of the data sets, it becomes clear that the variables are in different orders and contain different typos or other variations that may be challenging for simple standardization. 

V1:

```{r}
colnames(exdf_v1)

#  [1] "TEA4V1"     "TEA_5V1"    "V_1_1"      "EX_3_V1"    "EX4_V1"    
#  [6] "EX_5_V1"    "LEARN1_V1"  "LEARN2_V1"  "V_4_V"      "V5_V1"     
# [11] "LEAN3V1"    "LEARN_5_V1" "EX_1_V1"    "EX_2_V1"    "TEA1V1"    
# [16] "TEA2V1"     "TEA3V1"     "V_2_V1"     "V_3_V1"     "LEARN4_V1"
```
V2:

```{r}
colnames(exdf_v2)

#  [1] "EXAMP_3_V2" "EX_4_V2"    "EX_1_V2"    "V_3_V2"     "V4_V2"     
#  [6] "LEARN1_V2"  "LEARN2_V2"  "EX_2_V2"    "EX_5_V2"    "LEARN_3_V2"
# [11] "LEARN4_V2"  "LEARN_5_V2" "EX_DROP_ME" "TEA3V2"     "TEA4V2"    
# [16] "TEA_5V2"    "V_1_V2"     "V_2_V2"     "TEA1V2"     "TEA2V2"    
# [21] "V5_V2" 
```
V3:

```{r}
colnames(exdf_v3)

#  [1] "EX_1_V3"    "EX_2_V3"    "V_3_V3"     "TEA4V3"     "TEA5V3"    
#  [6] "V_4_V3"     "V_5V3"      "LN_3_V3"    "LN4_V3"     "EXAMP_3_V3"
# [11] "EX_4_V3"    "LN_5_V3"    "TEA1V3"     "TEA2V3"     "TEA3V3"    
# [16] "V_1_V3"     "V_2_V3"     "EX_5_V3"    "LN1_V3"     "LN2_V3"  
```

From careful review of the variable names and the original source data labels and values, we may identify trends that allow us to isolate potential matching variables using tidyselect. We demonstrate this with the first example source data set.

```{r}
incl_keys <- list(
  'starts_with' = c("EX_", "EXAMP_"),
  'contains' = c("EX")
  )
excl_keys <- list(
  'starts_with' = c(" "),
  'contains' = c(" ")
  )

exdf_v1_vars <- exdf_v1 %>%
  select(all_of(starts_with(incl_keys$starts_with)),
             all_of(contains(incl_keys$contains))
      ) %>%
      select(-c(
        all_of(starts_with(excl_keys$starts_with)),
        all_of(contains(excl_keys$contains))
      )
      ) %>%
      names()

exdf_v1_vars

# [1] "EX_3_V1" "EX_5_V1" "EX_1_V1" "EX_2_V1" "EX4_V1" 
```

We may apply our standardization function `standardize_col_names()` to these variables, which give us desired standardized variable names. However, they are not in our desired order.

```{r}
standardize_col_names(exdf_v1_vars)

# [1] "ex_3" "ex_5" "ex_1" "ex_2" "ex_4"
```

We reorder the source variables prior to passing through standardization. We use tidyselect to pull the variable names from our order, so that if any variable name changes in the source data set and it is reprocessed, an error will be raised. 

```{r}
exdf_v1_vars <- exdf_v1 %>%
  select(all_of(c(
    "EX_1_V1", "EX_2_V1", "EX_3_V1", "EX4_V1", "EX_5_V1"
    ))) %>%
  names()

desired_vars <- standardize_col_names(exdf_v1_vars)

desired_vars

# [1] "ex_1" "ex_2" "ex_3" "ex_4" "ex_5"
```

We can then check all of our source data frames, using `flag_unmatching_variables()`, to see if their target variables standardize similarly. We see an odd variable in exdf_v2 called `EX_DROP_ME`. We also see that `EXAMP_3_V2` in exdf_v2 and `EXAMP_3_V3` in exdf_v3 fail to standardize properly, but otherwise the standardization holds. 

```{r}
flagged_vars <- flag_unmatching_variables(
  source_df_list, desired_vars, incl_keys, excl_keys
  )
# [1] "In source  exdf_v1 : "           
# [2] "In source  exdf_v2 : EX_DROP_ME, EXAMP_3_V2"
# [3] "In source  exdf_v3 : EXAMP_3_V3"
```

In this case, we want to drop `EX_DROP_ME`, and have verified that. So, we add the variable to the dropping_list for exdf_v2.

```{r}
dropping_var_list[['exdf_v2']] <- c(dropping_var_list[['exdf_v2']],
                                    'EX_DROP_ME')
```


### Creating a Map for an Instrument (`vm_make_source_map()`, `vm_create_for_instrument()`)

Now that we have our desired variables in our desired initial standardization and order, we can begin to process these variables from our sources into a source map using `vm_make_source_map()`.

The source_map for exdf_v1 is the simplest: the `variable` column mirrors our desired variable list, though does not have the assigned order.

```{r}
df1_source_map <- vm_make_source_map(
  source_df_list, dropping_var_list, 1, 'exdf_v1', incl_keys, excl_keys
  )

df1_source_map
```

The map for exdf_v2 demonstrates the unusual variable `EXAMP_3_V2` that we identified in the flagging step. However, we can also see that the excluded variable `EX_DROP_ME` is not included!

```{r}
df2_source_map <- vm_make_source_map(
  source_df_list, dropping_var_list, 2, 'exdf_v2', incl_keys, excl_keys
  )

df2_source_map
```

We can correct this with a single point mutation, using either the `exdf_v2` or `variable` value to match the proper row.

```{r}
df2_source_map <- vm_make_source_map(
  source_df_list, dropping_var_list, 2, 'exdf_v2', incl_keys, excl_keys
  ) %>%
  mutate(variable = case_when(
    exdf_v2 == 'EXAMP_3_V2' ~ 'ex_3',
    TRUE ~ variable
    )
  )

df2_source_map
```

We already know that exdf_v3 has a similarly unusual variable as exdf_v2, so we can simply perform our point-mutation in the same call.

```{r}
df3_source_map <- vm_make_source_map(
  source_df_list, dropping_var_list, 3, 'exdf_v3', incl_keys, excl_keys
  ) %>%
  mutate(variable = case_when(
    variable == 'examp_3' ~ 'ex_3',
    TRUE ~ variable
    )
  )

df3_source_map
```

We can either join these individual maps...

```{r}
source_map <- full_join(
  df1_source_map, df2_source_map, by = 'variable'
  ) %>%
  full_join(
    df3_source_map, by = 'variable'
  )

source_map
```

... or create them in one piped call.

```{r}
source_map <- vm_make_source_map(
  source_df_list, dropping_var_list, 1, 'exdf_v1', incl_keys, excl_keys
  ) %>%
  full_join(
  # exdf_v2  
  vm_make_source_map(
    source_df_list, dropping_var_list, 2, 'exdf_v2', incl_keys, excl_keys
    ) %>%
    mutate(variable = case_when(
      exdf_v2 == 'EXAMP_3_V2' ~ 'ex_3',
      TRUE ~ variable
      )
    ), 
    by = 'variable'
  ) %>%
  full_join(
    # exdf_v3
    vm_make_source_map(
      source_df_list, dropping_var_list, 3, 'exdf_v3', incl_keys, excl_keys
      ) %>%
      mutate(variable = case_when(
        variable == 'examp_3' ~ 'ex_3',
        TRUE ~ variable
        )
      ), 
    by = 'variable'
  )

source_map
```

We can then initiate the frame of our instrument map using `vm_create_for_instrument()`. We simply pass the name of our instrument, and the desired variables in order, to obtain the initial frame of our instrument map. This initial structure only contains `variable`, `instrument`, and `item_ord`.

```{r}
example_inst <- vm_create_for_instrument('example', desired_vars)

example_inst
```

We can then add all variables from our sources by joining this frame and our source map using the `variable` column!

```{r}
example_inst <- example_inst %>%
  left_join(source_map, 
            by = 'variable')

example_inst
```

We would then add this instrument to a section-based list of instruments. These section-wide lists are initiated with a 'placeholder' entry which is empty, to both enforce the list structure for R and allow easy removal of this placeholder item before use.

```{r}
# Does return two items in output, as R insists on printing names
# and first item is 
# "$placeholder
#  NULL"

sec_instruments <- list("placeholder" = c())

sec_instruments <- append(sec_instruments, list('example' = example_inst))

sec_instruments
```

#### Modifying Standardizations

If we have a variable which is more complex in standardization, this may require a large number of point mutations. It may be more beneficial to create the instrument map, and then standardize after it has been created. We see this with our second example instrument, a "Learning" instrument.

We identify our variables of interest:

```{r}
incl_keys <- list(
  'starts_with' = c("LN", "LEAN"),
  'contains' = c("LEARN")
  )
excl_keys <- list(
  'starts_with' = c(" "),
  'contains' = c(" ")
  )

exdf_v1_vars <- exdf_v1 %>%
  select(all_of(starts_with(incl_keys$starts_with)),
             all_of(contains(incl_keys$contains))
      ) %>%
      select(-c(
        all_of(starts_with(excl_keys$starts_with)),
        all_of(contains(excl_keys$contains))
      )
      ) %>%
      names()

exdf_v1_vars

# [1] "LEAN3V1"    "LEARN1_V1"  "LEARN2_V1"  "LEARN_5_V1" "LEARN4_V1"
```

We reorder the source variables prior to passing through standardization. We use tidyselect to pull the variable names from our order, so that if any variable name changes in the source data set and it is reprocessed, an error will be raised. 

```{r}
exdf_v1_vars <- exdf_v1 %>%
  select(all_of(c(
    "LEARN1_V1", "LEARN2_V1", "LEAN3V1", "LEARN4_V1", "LEARN_5_V1"
    ))) %>%
  names()

desired_vars <- standardize_col_names(exdf_v1_vars)

desired_vars

# [1] "learn_1" "learn_2" "lean_3"  "learn_4" "learn_5"
```

We do not want the typo of `lean_3` to be part of our standardization, so we correct that error with a point mutation.

```{r}
desired_vars[desired_vars == 'lean_3'] <- 'learn_3'

desired_vars

# [1] "learn_1" "learn_2" "learn_3" "learn_4" "learn_5"
```


We can then check all of our source data frames, using `flag_unmatching_variables()`, to see if their target variables standardize similarly. As expected, the exdf_v1 `LEAN3V1` flagged due to its typo. We also identified that exdf_v3 variables followed an entirely separate naming convention, and would not match!

```{r}
flagged_vars <- flag_unmatching_variables(
  source_df_list, desired_vars, incl_keys, excl_keys
  )
# [1] "In source  exdf_v1 : LEAN3V1"         
# [2] "In source  exdf_v2 : "                
# [3] "In source  exdf_v3 : LN_3_V3, LN4_V3, LN_5_V3, LN1_V3, LN2_V3"
```

We created our source map, taking care to point-mutate the deviations identified from our check.

```{r}
source_map <- vm_make_source_map(
  # exdf_v1
  source_df_list, dropping_var_list, 1, 'exdf_v1', incl_keys, excl_keys
    ) %>%
    mutate(variable = case_when(
      exdf_v1 == 'LEAN3V1' ~ 'learn_3',
      TRUE ~ variable
      )
  ) %>%
  full_join(
  # exdf_v2  
  vm_make_source_map(
    source_df_list, dropping_var_list, 2, 'exdf_v2', incl_keys, excl_keys
    ), 
    by = 'variable'
  ) %>%
  full_join(
    # exdf_v3
    vm_make_source_map(
      source_df_list, dropping_var_list, 3, 'exdf_v3', incl_keys, excl_keys
      ) %>%
      mutate(variable = case_when(
        variable == 'ln_1' ~ 'learn_1',
        variable == 'ln_2' ~ 'learn_2',
        variable == 'ln_3' ~ 'learn_3',
        variable == 'ln_4' ~ 'learn_4',
        variable == 'ln_5' ~ 'learn_5',
        TRUE ~ variable
        )
      ), 
    by = 'variable'
  )

source_map
```

We can create our instrument map.

```{r}
learning_inst <- vm_create_for_instrument(
  'learning', desired_vars
  ) %>%
  left_join(source_map, 
            by = 'variable')

learning_inst
```

In our original example map, all of the Learning Instrument variables followed a different naming convention: where our current processing gives us standardization to `learn_` prefixes, if we wished for `ln_` prefixes we could simply mutate this instrument map.

```{r}
learning_inst <- learning_inst %>%
  mutate(variable = paste0(
    'lrn_',
    stringr::str_match(variable, '(learn_)([0-9]+)')[,3]
    )
  )

learning_inst
```

We would then add this instrument to a section-based list of instruments. 

```{r}
sec_instruments <- append(sec_instruments, list('learning' = learning_inst))
```

### Joining Instruments into Sections (`vm_join_inst_section()`)

Instruments are joined together into sections. To demonstrate this, let us say that the instruments "example" and "learning" belong to "section A". As both instruments are already in our `sec_instruments` list, we can perform this join with relative ease by calling `vm_join_inst_section()`.

We pass the desired name of the section and a list of the instruments to our function. If we have not already dropped the 'placeholder' entry in the list, we should do so.

```{r}
sec_instruments <- sec_instruments[names(sec_instruments) != "placeholder"]

example_sec <- vm_join_inst_section('section A', sec_instruments)

example_sec
```

If we were planning to join these sections into a full map, we would add them to a list of sections, similar to the section-wise list of instruments.

```{r}
sections_in_map <- list('placeholder' = c())

sections_in_map <- append(sections_in_map, list('sec_a' = example_sec))
```

### Joining Sections into a Full Map (`vm_join_sections()`)

Joining sections together into a full map is much the same as joining instruments into a section. Let us say our final map has two sections: 'section A' and 'section B'. The instruments 'example' and 'learning' should be in 'section A', which is already present in our section list. The instruments 'teaching' and 'visualizing' belong to 'section B'.

For brevity, we established section B and appended it to our section list using the previously described techniques.

```{r, warning = FALSE}
# Teaching Instrument
incl_keys <- list(
  'starts_with' = c("TEA"),
  'contains' = c(" ")
  )
excl_keys <- list(
  'starts_with' = c(" "),
  'contains' = c(" ")
  )

teaching_inst <- vm_create_for_instrument(
  'teaching', c('tea_1', 'tea_2', 'tea_3', 'tea_4', 'tea_5')
  ) %>%
  left_join(
    vm_make_source_map(
    # exdf_v1
    source_df_list, dropping_var_list, 1, 'exdf_v1', incl_keys, excl_keys
      ) %>%
    full_join(
    # exdf_v2  
    vm_make_source_map(
      source_df_list, dropping_var_list, 2, 'exdf_v2', incl_keys, excl_keys
      ), 
      by = 'variable'
    ) %>%
    full_join(
      # exdf_v3
      vm_make_source_map(
        source_df_list, dropping_var_list, 3, 'exdf_v3', incl_keys, excl_keys
        ), 
      by = 'variable'
    ), by = 'variable'
  ) %>%
  mutate(variable = paste0(
    'tch_',
    stringr::str_match(variable, '(tea_)([0-9]+)')[,3]
    )
  )

# Visualizing Instrument
incl_keys <- list(
  'starts_with' = c("V"),
  'contains' = c(" ")
  )
excl_keys <- list(
  'starts_with' = c(" "),
  'contains' = c(" ")
  )

visualizing_inst <- vm_create_for_instrument(
  'visualizing', c('v_1', 'v_2', 'v_3', 'v_4', 'v_5')
  ) %>%
  left_join(
    # exdf_v1
    vm_make_source_map(
      source_df_list, dropping_var_list, 1, 'exdf_v1', incl_keys, excl_keys
        ) %>%
        mutate(variable = case_when(
            exdf_v1 == 'V_1_1' ~ 'v_1',
            exdf_v1 == 'V_4_V' ~ 'v_4',
            exdf_v1 == 'V5_V1' ~ 'v_5',
            TRUE ~ variable
          )
        ) %>%
      full_join(
      # exdf_v2  
      vm_make_source_map(
        source_df_list, dropping_var_list, 2, 'exdf_v2', incl_keys, excl_keys
        ) %>%
        mutate(variable = case_when(
            exdf_v2 == 'V4_V2' ~ 'v_4',
            exdf_v2 == 'V5_V2' ~ 'v_5',
            TRUE ~ variable
          )
        ), 
        by = 'variable'
      ) %>%
      full_join(
        # exdf_v3
        vm_make_source_map(
          source_df_list, dropping_var_list, 3, 'exdf_v3', incl_keys, excl_keys
          ), 
        by = 'variable'
      ),
    by = 'variable'
  ) %>%
  mutate(variable = paste0(
    'vis_',
    stringr::str_match(variable, '(v_)([0-9]+)')[,3]
    )
  )

# Joining into section

sec_instruments <- list(
  'teaching' = teaching_inst, 'visualizing'  = visualizing_inst
  )

sec_b_map <- vm_join_inst_section('section B', sec_instruments)

sections_in_map <- append(sections_in_map, list('sec_b' = sec_b_map))
```

Joining these sections into a single map is as simple as passing these sections into our `vm_join_sections()` function, taking care to omit the 'placeholder' entry if it has not already been removed

```{r}
sections_in_map <- sections_in_map[names(sections_in_map) != "placeholder"]

created_map <- vm_join_sections(sections_in_map)

created_map
```

### Extracting Attributes into Variable Map

We can also store attributes in our variable map, such as labels and variable value labels. If all data frames have identical labels and value labels, this can be done with a simple for loop to pull from a single data frame.

```{r}
created_map <- created_map %>%
  add_column(attr_label = NA, attr_var_labels = NA)

for (var_name in colnames(exdf_v1)){
  created_map[created_map$exdf_v1 == var_name,]$attr_label <-
    attributes(exdf_v1[[var_name]])$label
  created_map[created_map$exdf_v1 == var_name,]$attr_var_labels <-
    attributes(exdf_v1[[var_name]])$labels
}

created_map
```

Otherwise, selection should be performed based on the desired and needed labels, which is a case-by-case condition beyond the scope of this vignette.

## Modifications of a Variable Map

### Modifying Standardized Variable Names (`variable`)

This map structure also facilitates modifications of standardized variable names, without having to rename every variable manually.

If the third item of the "learning" instrument was renamed in "exdf_v3" for any reason, and we needed to keep the data pipeline intact, we can first check the original standardized name and values:

```{r}
example_map %>%
  filter(instrument == "learning") %>%
  filter(item_ord == 3)
```

And then use this to make a point-fix. In this example, the new variable in "exdf_v3" is "LEARNING_3_V3".

```{r}
modifying_map <- example_map

modifying_map[modifying_map$variable == "lrn_3", "exdf_v3"]<- "LEARNING_3_V3"

modifying_map %>%
  filter(instrument == "learning") %>%
  filter(item_ord == 3)
```

We could also rename our standardized variables, such as if we want to move from sequential names to descriptive names. We could do this for a single variable with a point-modification:

```{r}
modifying_map[modifying_map$variable == "lrn_3", "variable"] <- "enjoys_learning"

modifying_map %>%
  filter(instrument == "learning") %>%
  filter(item_ord == 3)
```

Or for an entire instrument:

```{r}
modifying_map <- modifying_map %>%
  arrange(sec_ord, inst_ord, item_ord) %>%
  mutate(variable = ifelse(instrument == "teaching",
         case_when(item_ord == 1 ~ "years_teaching",
                   item_ord == 2 ~ "employed_teaching",
                   item_ord == 3 ~ "enjoys_teaching",
                   item_ord == 4 ~ "cert_teaching",
                   item_ord == 5 ~ "plan_to_teach"), variable)
  )

modifying_map %>%
  filter(section == 'section B')
```

### Obtaining Desired Variable Order

In general, order within the appendix for all items may be obtained by ordering the map by section order, then instrument order, then item order.

```{r}
modifying_map <- modifying_map %>%
  arrange(sec_ord, inst_ord, item_ord)

modifying_map
```

### Inserting Variables `vm_add_variable()`

We may also insert items within our set. Lets say we create a variable, `ex_2_calc`, which we want to appear just after `ex_2`. We can also use point modifications to flag that this variable is calculated, and add a label.

```{r}
modifying_map <- vm_add_variable(modifying_map, 'example', 'ex_2_calc', 'ex_2') %>%
  mutate(
    calculated = ifelse(variable == 'ex_2_calc', TRUE, FALSE),
    attr_label = ifelse(
      variable == 'ex_2_calc', 
      "Calculated Visit Num", 
      attr_label))

modifying_map
```

By using the function, it forbids us from adding a variable name that has already been used.

```{r}
# Code commented out as it throws an error and stops the document:

# vm_add_variable(modifying_map, 'example', 'ex_2', 'ex_2')

# Error in vm_add_variable(modifying_map, "example", "ex_2", "ex_2") :
# ex_2 also appears in the map for instrument: example
```

### Reordering Instruments Within a Section (`inst_ord`)

We can also reorder our instruments within a section. By examining 'section A' we can see two instruments, 'example' and 'learning', which are the first and second instruments in the section.

```{r}
modifying_map %>%
  filter(section == 'section A') %>%
  select(instrument, inst_ord) %>%
  distinct()
```

We can change this order by targeting `inst_ord` with respect to `instrument` and `section`. Say we wish for 'learning' to be the first instrument, and 'example' the 3rd, with a place held for an instrument that is not yet part of the map.

```{r}
modifying_map <- modifying_map %>%
  mutate(inst_ord = ifelse(section == 'section A',
                           case_when(
                             instrument == 'example' ~ 3,
                             instrument == 'learning' ~ 1
                           ), inst_ord)
         ) %>%
  arrange(sec_ord, inst_ord, item_ord)

modifying_map
```

### Deleting a Variable (`vm_delete_variable()`)

We can also delete a variable, while shifting the map to close the gap seamlessly.

```{r}
vm_delete_variable(modifying_map, 'lrn_2')
```

## Utilizing the Variable Map (`vm_process_source_df()`, `vm_process_many_sources()`, 'vm_factor_apply_val_labels()`)

Finally, the primary utility of the variable map is how we can utilize this variable map in the initial extraction of the variables into a consolidated data set. The variable map is a single "choke point" for any further modifications that are created.

We could process a single data set using our variable map to achieve our standardized names.

```{r}
vm_process_source_df(
  example_map, exdf_v1, 'exdf_v1', dropping_var_list[['exdf_v1']]
  )
```

Or we could process all of our data sets at once and stack them into a single set.

```{r}
packaged_sources <- tibble::tibble(
  'source_df' = list(exdf_v1, exdf_v2, exdf_v3),
  'source_df_col' = c('exdf_v1', 'exdf_v2', 'exdf_v3'),
  'excluding_vars' = dropping_var_list,
)

vm_process_many_source(example_map, packaged_sources)
```

The power of the map is that if, for example, we realized `ex_1` was a subject id and `ex_1` was a collection number, we could rename them on the map *once*. Then any future extracting using the map would utilize these new names without requiring any further modification.

```{r}
modified_map <- example_map %>%
  mutate(variable = case_when(
    variable == 'ex_1' ~ 'id',
    variable == 'ex_2' ~ 'visit',
    TRUE ~ variable
  ))

vm_process_many_source(modified_map, packaged_sources)
```

Similarly, if a variable is renamed in one of our source data sets, we would be notified by our function.

```{r}
exdf_v1 <- exdf_v1 %>%
  rename_at('EX_5_V1', ~'EX5V_1')

packaged_sources <- tibble::tibble(
  'source_df' = list(exdf_v1, exdf_v2, exdf_v3),
  'source_df_col' = c('exdf_v1', 'exdf_v2', 'exdf_v3'),
  'excluding_vars' = list(c(), c(), c()),
)

# Code commented out as it throws an error and stops the document:

# vm_process_many_source(modified_map, packaged_sources)

# Error in vm_process_source_df(var_map, source_df, source_df_col, excluding_vars) :
# Variables missing from exdf_v1: EX_5_V1
# Variables missing from var_map & excluding_vars: EX5V_1
```

But if we make a single point-fix to our variable map, we can process without issue.

```{r}
modified_map <- modified_map %>%
  mutate(exdf_v1 = case_when(
    exdf_v1 == 'EX_5_V1' ~'EX5V_1',
    TRUE ~ exdf_v1
  ))
  
packaged_sources <- tibble::tibble(
  'source_df' = list(exdf_v1, exdf_v2, exdf_v3),
  'source_df_col' = c('exdf_v1', 'exdf_v2', 'exdf_v3'),
  'excluding_vars' = dropping_var_list,
)

example_df <- vm_process_many_source(modified_map, packaged_sources)
example_df
```

We can use our variable map to attach labels to all of the variables in our newly created, combined data set.

```{r}
for (var_name in colnames(example_df)){
  attributes(example_df[[var_name]])$label <-
    modified_map[modified_map$variable == var_name,]$attr_label
}
```

We can also use the function `vm_factor_apply_val_labels()` to modify any variable with value labels into a factor, with those labels applied.

```{r}
vm_factor_apply_val_labels(example_df, modified_map)
```

## Updating Variable Map with Processing Data

If we are performing processing on our created data set, we can include details about those modifications in our variable map.

```{r}
exdf_v1 <- exdf_v1 %>%
  rename_at('EX5V_1', ~'EX_5_V1')

packaged_sources <- tibble::tibble(
  'source_df' = list(exdf_v1, exdf_v2, exdf_v3),
  'source_df_col' = c('exdf_v1', 'exdf_v2', 'exdf_v3'),
  'excluding_vars' = dropping_var_list,
)

example_df <- vm_process_many_source(example_map, packaged_sources)

example_df
```

Perhaps we are interested in the difference between `lrn_2` ("Learn a number") and `ln_5` ("Learn a new number"), but we don't care to keep `lrn_2` or `lrn_5` after processing. The creation of the calculated variable is relatively simple.

```{r}
example_df <- example_df %>%
  mutate(lrn_diff = lrn_5 - lrn_2)

example_df
```

We could adjust our variable map to reflect this modification. We add the new variable, flag it as `calculated`, and add it's label. Then we can mark `lrn_3` and `lrn_5` with a flag, such as `drop_consolidated`.

```{r}
modified_map <- example_map %>%
  vm_add_variable(
    'learning', new_var = 'lrn_diff', prev_var = 'lrn_5',
    opts = tibble::tibble(
      'calculated' = TRUE,
      'drop_consolidated' = FALSE,
      'phi' = FALSE,
      'attr_label' = "Difference in learned numbers"
      )
    ) %>%
  mutate(drop_consolidated = case_when(
    variable == 'lrn_2' ~ TRUE,
    variable == 'lrn_5' ~ TRUE,
    TRUE ~ drop_consolidated
    )
  )

modified_map
```

We could then reorder our data set, including removal of the `drop_consolidated` variables, by using our variable map. We can also add our label individually, or as part of a loop.

```{r}
example_df %>%
  relocate(all_of(
    pull(modified_map %>%
        arrange(sec_ord, inst_ord, item_ord) %>%
        select(variable))
    )
  ) %>%
  select(-all_of(
    pull(modified_map %>%
         filter(drop_consolidated) %>%
         select(variable))
      )
  )

attributes(example_df[['lrn_diff']])$label <- 
  modified_map[modified_map$variable == 'lrn_diff',]$attr_label
```

We can also use flags in the variable map for ease of isolating specific variables, which can become unwieldy and vulnerable to change in larger data sets. 

A key example of this would be flagging variables as PHI. By identifying these variables as PHI, they can either be excluded from a subset easily, or otherwise protected. In packages that display summary statistics but allow for PHI blocking, such as [codebookr](https://brad-cannell.github.io/codebookr/), this allows for easy, streamlined PHI blocking.

In our example map, suppose that the Subject ID and Intervier values are being considered PHI. By filtering from these columns, we can ensure that these 'PHI' cokumns are not displayed.

```{r}
modified_map <- modified_map %>%
  mutate(
    phi = case_when(
      variable == 'ex_1' ~ TRUE,
      variable == 'ex_4' ~ TRUE
    )
  )

example_df %>%
  select(-all_of(
    pull(modified_map %>%
           filter(phi) %>%
           select(variable)
         )
      )
    )
```

