---
title: "Demographics by Visit"
date: "2024-01-11 <br> Updated: `r Sys.Date()`"
format: pdf
editor: 
  markdown: 
    wrap: sentence
---

# ⭐️Overview

This file was used to analyse the breakdown of payment method assignment in each study arm, as well as the demographic breakdown of subjects that participated in each visit.

## Notes

Payment methods for remuneration payments changed during the course of the study. The number of subjects in each study arm that experienced each payment method were isolated for reporting.

Many subjects missed one or more visits. The demographics of subjects attending each visit were isolated for analysis to assess for statistically significant differences.

# 📦Load packages & Functions

```{r, message=FALSE, warning=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(purrr, warn.conflicts = FALSE)
library(haven, warn.conflicts = FALSE)
library(here, warn.conflicts = FALSE)
library(stringr, warn.conflicts = FALSE)
library(lubridate, warn.conflicts = FALSE)
library(readxl, warn.conflicts = FALSE)
library(openxlsx, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(tidyverse, warn.conflicts = FALSE)
library(meantables, warn.conflicts = FALSE)
library(freqtables, warn.conflicts = FALSE)
```

```{r}
source(here("R", "data_mod_check.R"))
```

# 📥 Import the Data

## Combined Data Set

We imported our Combined Data Set

```{r}
combined_data_path <- here::here(
  "data", "Combined Participant Data", "combined_data_03.rds"
  )
```

Import the data.
Check the most recent file modification dates and print for user when this file is being sourced.

```{r message=FALSE}
combined_data <- readr::read_rds(combined_data_path)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Combined data imported with", nrow(combined_data), "rows and", 
  ncol(combined_data), "columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Combined data last modified on OneDrive", 
      as.character(file.info(combined_data_path)$mtime), "\n"
    )

# 2024-01-17: Combined data imported with 1606 rows and 1130 columns.
# Combined data last modified on OneDrive 2024-01-11 18:19:37 
```

We purged the import path for memory management.

```{r}
rm(combined_data_path)
```

# Convenience Function

A simple convenience function was written to facilitate creation of summary statistic tables within this document.

```{r}
summary_stats <- function(t_df, visit_val, cont_cols, cat_cols){
  
  # Takes a dataframe, and lists of continuous and categorical columns.
  # Returns basic summary statistics. Filters by visit value.
  #
  # Input:
  #     t_df (dataframe):     target dataframe
  #     visit_val (string):   string of the desired value of the 'visit' col
  #     cont_cols (list):     list of continuous variable columns
  #                             gives count, mean and SD
  #     cat_cols (list):      list of categorical variable columns
  #                             gives count, percentage, SE
  # Output:
  #     stat_rows (tibble):   tibble containing the variable, category, and
  #                             summary statistics of the given combination of
  #                             column (and category, if applicable) for the
  #                             visit value in t_df.
  #                             [var, cat, n, statistic, error]

  # Continuous Variable Statistics (Count, Mean, SD)
  # ==========================================================================
  # Uses meantables package
  
  # Initiate empty tibble
  # --------------------------------------------------------------------------
  cont_stats <- tibble::tibble(
    !!!c('response_var', 'n', 'mean', 'sd'),
    .rows = 0, 
    .name_repair = ~c('response_var', 'n', 'mean', 'sd')
    ) |>
    dplyr::mutate(
      n = as.numeric(n),
      mean = as.numeric(mean),
      sd = as.numeric(sd)
    )
  
  # Iterate through target columns to obtain desired statistics
  # --------------------------------------------------------------------------
  for (cont_var in cont_cols) {
    col_stats <- t_df |>
      dplyr::filter(!!rlang::sym(visit_val)) |>
      meantables::mean_table(!!rlang::sym(cont_var)) |>
      dplyr::select(response_var, n, mean, sd)
    
    cont_stats <- dplyr::bind_rows(cont_stats, col_stats)
  }
  
  # Add empty "category" column and standardize column names to facilitate 
  # merge with categorical variable stat rows
  # --------------------------------------------------------------------------
  cont_stats <- cont_stats |>
    dplyr::mutate(
      cat = NA
    ) |>
    dplyr::rename_at(
      c('response_var', 'mean', 'sd'),
      ~c('var', 'statistic', 'error')
    ) |>
    dplyr::relocate('var', 'cat', 'n', 'statistic', 'error')
  
  # Categorical Variable Statistics (Count, Percent, SE)
  # ==========================================================================
  # Uses freqtables package
  
  # Initiate empty tibble
  # --------------------------------------------------------------------------
  cat_stats <- tibble::tibble(
    !!!c('var', 'cat', 'n', 'percent', 'se'),
    .rows = 0, 
    .name_repair = ~c('var', 'cat', 'n', 'percent', 'se')
    ) |>
    dplyr::mutate(
      n = as.numeric(n),
      percent = as.numeric(percent),
      se = as.numeric(se)
    )
  
  # Iterate through target columns to obtain desired statistics
  # --------------------------------------------------------------------------
  for (cat_var in cat_cols) {
    col_stats <- t_df |>
      dplyr::filter(!!rlang::sym(visit_val)) |>
      freqtables::freq_table(!!rlang::sym(cat_var)) |>
      dplyr::select(var, cat, n, percent, se)
    
    cat_stats <- dplyr::bind_rows(cat_stats, col_stats)
  }
  
  # Standardize column names to facilitate merge with continuous variable 
  # stat rows
  # --------------------------------------------------------------------------
  cat_stats <- cat_stats |>
    dplyr::rename_at(
      c('percent', 'se'),
      ~c('statistic', 'error')
    )
  
  # Combine and Return Stats
  # ==========================================================================
  stat_rows <- dplyr::bind_rows(cont_stats, cat_stats)
  
  stat_rows
}
```

# Modifications

## Creation of Payment Structure Subset

We created a temporary version of our combined data set to examine enrollment in each payment structure. This involved isolation of our target variables (group, payment_structure, visit, id), consolidation of group into 'UCM' and 'Smartphone' groups, and consolidation of all 'UCM' subjects into the 'original' payment structure.

```{r}
payment_data <- combined_data |>
  dplyr::select(group, payment_structure, id, visit) |>
  dplyr::mutate(
    payment_structure = dplyr::case_when(
      group == "Usual Case Management (UCM)" ~ 'Original',
      TRUE ~ payment_structure
    ),
    group = dplyr::case_when(
      group != 'Usual Case Management (UCM)' ~ 'Smartphone',
      TRUE ~ group
    )
  )
```

## Isolation of Desired Variables

We isolated only the desired variables from our data set.

```{r}
combined_data <- combined_data |>
  dplyr::select(
    id, group, visit, subj_gender, subj_race_ethn, subj_race, subj_hispanic,
    subj_age, drop_flag
    )
```

## Modification of Visit (Pivot to Wide, Binary 'Full Attendance' Variable)

We modified our data set to pivot our data from long format (subject-visit) to wide format (subject), wherein attendance at each visit was indicated with a binary 'TRUE'/'FALSE' logical. We further calculated a binary outcome variable indicating if a subject did or did not attended all study visits.

```{r}
combined_data <- combined_data |>
  dplyr::mutate(
    'TRUE' = TRUE
    ) |>
  tidyr::pivot_wider(
    names_from = visit, values_from = 'TRUE', values_fill = FALSE
    ) |>
  dplyr::rename_at(
    c(
      'Visit 1: Baseline', 'Visit 2: Randomization', 
      'Visit 3: 1 Month Follow-Up', 'Visit 4: 3 Month Follow-Up',
      'Visit 5: 6 Month Follow-Up'
      ),
    ~c('v1', 'v2', 'v3', 'v4', 'v5')
    ) |>
  dplyr::mutate(
    full_attendance = if_else(v1 & v2 & v3 & v4 & v5, TRUE, FALSE)
    ) |>
  dplyr::relocate(id, v1, v2, v3, v4, v5, full_attendance)
```

## Reduction of Race Categories (3 Categories)

We modified race to only include 3 categories: White, Black, and Other.

```{r}
combined_data <- combined_data |>
  dplyr::mutate(
    subj_race_3cat = dplyr::case_when(
      !(subj_race %in% c("White", "Black or African American")) ~ "Other",
      TRUE ~ subj_race
    )
  ) |>
  dplyr::mutate(subj_race_3cat = factor(subj_race_3cat))
```

# Identification of Variable Types

We identified our continuous and categorical variables of interest.

```{r}
cat_cols <- c(
  'subj_gender', 'subj_race_3cat', 'subj_hispanic', 'subj_race_ethn', 'group'
  )
cont_cols <- c('subj_age')
```

# Payment Structure Counts

We examined the counts for each visit:

```{r}
table(payment_data |>
  dplyr::filter(visit == "Visit 1: Baseline") |>
  dplyr::select(group, payment_structure))
```

```{r}
table(payment_data |>
  dplyr::filter(visit == "Visit 2: Randomization") |>
  dplyr::select(group, payment_structure))
```

```{r}
table(payment_data |>
  dplyr::filter(visit == "Visit 3: 1 Month Follow-Up") |>
  dplyr::select(group, payment_structure))
```

```{r}
table(payment_data |>
  dplyr::filter(visit == "Visit 4: 3 Month Follow-Up") |>
  dplyr::select(group, payment_structure))
```

```{r}
table(payment_data |>
  dplyr::filter(visit == "Visit 5: 6 Month Follow-Up") |>
  dplyr::select(group, payment_structure))
```

We also examined the 'ever' counts for each payment method, examining both the UCM and Smartphone groups.

```{r}
#UCM
length(unique(pull(
  combined_data |> 
    filter(group == 'Usual Case Management (UCM)') |>
    select(id)
  )))
#137
```

```{r}
# Smartphone, Original
length(unique(pull(
  payment_data |> 
    filter(group != 'Usual Case Management (UCM)') |> 
    filter(payment_structure == 'Original') |> 
    select(id)
  )))
# 47
```

```{r}
# Smartphone, 1st Modification
length(unique(pull(
  payment_data |> 
    filter(group != 'Usual Case Management (UCM)') |> 
    filter(payment_structure == '1st Modification') |> 
    select(id)
  )))
# 50
```

```{r}
# Smartphone, 2nd Modification
length(unique(pull(
  payment_data |> 
    filter(group != 'Usual Case Management (UCM)') |> 
    filter(payment_structure == '2nd Modification') |> 
    select(id)
  )))
# 200
```

```{r}
rm(payment_data)
```


# Demographic Summary Tables

## Total (All Groups)

### Baseline

Subjects were further filtered to exclude any subjects that were marked for exclusion for any reason other than failure to attend the randomization visit.

```{r}
combined_data <- combined_data |>
  dplyr::filter((drop_flag & is.na(group)) | (!is.na(group) & !drop_flag))
```


We examined the characteristics of all subjects, at baseline. This included non-randomized or otherwise excluded subjects, for a total of 442 subjects

```{r}
nrow(
  combined_data |> 
    dplyr::filter(v1) |>
    dplyr::filter((drop_flag & is.na(group)) | (!is.na(group) & !drop_flag))
     )
# 442
```

```{r}
summary_stats(
  combined_data |> 
    dplyr::filter((drop_flag & is.na(group)) | (!is.na(group) & !drop_flag)), 
  visit_val = 'v1', cont_cols, cat_cols
  )
```

### Visit 2, Included Only

We examined the characteristics of randomized subjects at Visit 2. This included a total of 403 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(v2)
     )
# 403
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag), 
  visit_val = "v2", 
  cont_cols, cat_cols
  )
```


### Visit 3, Included Only

We examined the characteristics of randomized subjects at Visit 3. This included a total of 300 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(v3)
     )
# 300
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag), 
  visit_val = 'v3', 
  cont_cols, cat_cols
  )
```

### Visit 4, Included Only

We examined the characteristics of randomized subjects at Visit 4. This included a total of 236 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(v4)
     )
# 236
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag), 
  visit_val = 'v4', 
  cont_cols, cat_cols
  )
```

### Visit 5, Included Only

We examined the characteristics of randomized subjects at Visit 5. This included a total of 217 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(v5)
     )
# 217
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag), 
  visit_val = 'v5', 
  cont_cols, cat_cols
  )
```

## UCM Group

### Visit 2, Included Only

We examined the characteristics of subjects randomized to the UCM group at Visit 2. This included a total of 136 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Case Management (UCM)") |>
       dplyr::filter(v2)
     )
# 136
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Case Management (UCM)"), 
  'v2', 
  cont_cols, cat_cols
  )
```


### Visit 3, Included Only

We examined the characteristics of subjects randomized to the UCM group at Visit 3. This included a total of 98 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(group == "Usual Case Management (UCM)") |>
       dplyr::filter(v3)
     )
# 98
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Case Management (UCM)"), 
  'v3', 
  cont_cols, cat_cols
  )
```

### Visit 4, Included Only

We examined the characteristics of subjects randomized to the UCM group at Visit 4. This included a total of 71 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(group == "Usual Case Management (UCM)") |>
       dplyr::filter(v4)
     )
# 71
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Case Management (UCM)"),
  'v4', 
  cont_cols, cat_cols
  )
```

### Visit 5, Included Only

We examined the characteristics of subjects randomized to the UCM group at Visit 5. This included a total of 64 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(group == "Usual Case Management (UCM)") |>
       dplyr::filter(v5)
     )
# 64
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Case Management (UCM)"),
  'v5', 
  cont_cols, cat_cols
  )
```

## UCM+SP Group

### Visit 2, Included Only

We examined the characteristics of subjects randomized to the UCM+SP group at Visit 2. This included a total of 136 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)") |>
       dplyr::filter(v2)
     )
# 134
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)"), 
  'v2', 
  cont_cols, cat_cols
  )
```


### Visit 3, Included Only

We examined the characteristics of subjects randomized to the UCM+SP group at Visit 3. This included a total of 107 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)") |>
       dplyr::filter(v3)
     )
# 107
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)"), 
  'v3', 
  cont_cols, cat_cols
  )
```

### Visit 4, Included Only

We examined the characteristics of subjects randomized to the UCM+SP group at Visit 4. This included a total of 84 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)") |>
       dplyr::filter(v4)
     )
# 84
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)"),
  'v4', 
  cont_cols, cat_cols
  )
```

### Visit 5, Included Only

We examined the characteristics of subjects randomized to the UCM+SP group at Visit 5. This included a total of 73 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)") |>
       dplyr::filter(v5)
     )
# 73
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(group == "Usual Care plus Smartphone (UCM+SP)"),
  'v5', 
  cont_cols, cat_cols
  )
```

## SPCM

### Visit 2, Included Only

We examined the characteristics of subjects randomized to the SPCM group at Visit 2. This included a total of 133 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)") |>
       dplyr::filter(v2)
     )
# 133
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)"), 
  'v2', 
  cont_cols, cat_cols
  )
```


### Visit 3, Included Only

We examined the characteristics of subjects randomized to the SPCM group at Visit 3. This included a total of 97 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)") |>
       dplyr::filter(v3)
     )
# 97
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)"),
  'v3', 
  cont_cols, cat_cols
  )
```

### Visit 4, Included Only

We examined the characteristics of subjects randomized to the SPCM group at Visit 4. This included a total of 82 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)") |>
       dplyr::filter(v4)
     )
# 82
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)"), 
  'v4', 
  cont_cols, cat_cols
  )
```

### Visit 5, Included Only

We examined the characteristics of subjects randomized to the SPCM group at Visit 5. This included a total of 81 subjects.

```{r}
nrow(combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)") |>
       dplyr::filter(v5)
     )
# 81
```

```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(
         group == "Usual Care plus Smartphone based Case Management (SPCM)"),
  'v5', 
  cont_cols, cat_cols
  )
```

# Analyses

## Binary Outcome ("Attended All Visits" vs "Did Not Attend All Visits")

We performed binary analyses to examine for any statistically significant associations between our demographics and attendance at all visits.

### All "Non-Excluded" Subjects

#### Summary Statistics

First, summary statistics were generated to examine the two groups ("full attendance" vs "non-full attendance").

Full Attendance:
```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(full_attendance),
  'v1', 
  cont_cols, cat_cols
  )
```

Non-Full Attendance:
```{r}
summary_stats(
  combined_data |> 
       dplyr::filter(!drop_flag) |>
       dplyr::filter(!full_attendance),
  'v1', 
  cont_cols, cat_cols
  )
```

#### Continuous Numeric (Age)

As both groups had well over 30 subjects, age was treated as approximately normally distributed under the central limit theorem. The variances appeared to be approximately equal, which was supported by the F-test of equal variances (F = 1.1254, dof = 275/162 p = 0.409, two-sided test).

```{r}
var.test(subj_age ~ full_attendance, 
         combined_data |>
           dplyr::filter(!drop_flag), 
         alternative = "two.sided")
```

The two-sided t-test of means with equal variance indicated a statistically significant difference in mean age across attendance status (t = 2.4247, dof = 437, p = 0.01573)

```{r}
x_vals <- combined_data |> 
  dplyr::filter(!drop_flag) |>
  dplyr::filter(full_attendance) |>
  dplyr::select(subj_age)

y_vals <- combined_data |> 
  dplyr::filter(!drop_flag) |>
  dplyr::filter(!full_attendance) |>
  dplyr::select(subj_age)

t.test(x_vals, y_vals, alternative = 'two.sided', var.equal=TRUE)
```

```{r}
rm(x_vals)
rm(y_vals)
```


#### Categorical Variables

Categorical variables were tested using a Chi-Square or Fisher's Exact Test for Association.

Gender had expected counts < 5 in cells, due to low counts in the Gender of "Other". As such, Fisher's Exact Test was utilized. Fisher's exact testing demonstrated no statistically significant association between Gender and attendance compliance (p=0.2058).

```{r}
gender_table <- table(combined_data[['full_attendance']], combined_data[['subj_gender']])

fisher.test(gender_table)
```

```{r}
rm(gender_table)
```


Race had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Race and attendance status (X<sup>2</sup> = 1.748, dof = 2, p = 0.4173).

```{r}
race_table <- table(combined_data[['full_attendance']], combined_data[['subj_race_3cat']])

chisq.test(race_table)
```

```{r}
rm(race_table)
```


Ethnicity (Hispanic Origin) had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Ethnicity and attendance status (X<sup>2</sup> = 2.8658 x 10<sup>-30</sup>, dof = 1, p = 1).

```{r}
ethnicity_table <- table(combined_data[['full_attendance']], combined_data[['subj_hispanic']])

chisq.test(ethnicity_table)
```

```{r}
rm(ethnicity_table)
```

Study arm had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between study arm and attendance status (X<sup>2</sup> = 4.1981, dof = 2, p = 0.1226).

```{r}
arm_table <- table(combined_data[['full_attendance']], combined_data[['group']])

chisq.test(arm_table)
```

```{r}
rm(arm_table)
```

### Randomized Subjects Only

We further restricted our comparison to only randomized subjects that were not marked for exclusion.

```{r}
comp_data <- combined_data |>
  dplyr::filter(!drop_flag)
```

#### Summary Statistics

First, summary statistics were generated to examine the two groups ("full attendance" vs "non-full attendance").

Full Attendance:
```{r}
summary_stats(
  comp_data |> 
       dplyr::filter(full_attendance),
  'v1', 
  cont_cols, cat_cols
  )
```

Non-Full Attendance:
```{r}
summary_stats(
  comp_data |> 
       dplyr::filter(!full_attendance),
  'v1', 
  cont_cols, cat_cols
  )
```

#### Continuous Numeric (Age)

As both groups had well over 30 subjects, age was treated as approximately normally distributed under the central limit theorem. The variances appeared to be approximately equal, which was supported by the F-test of equal variances (F = 1.1782, dof = 239/162 p = 0.2619, two-sided test).

```{r}
var.test(subj_age ~ full_attendance, comp_data, 
         alternative = "two.sided")
```

The two-sided t-test of means with equal variance indicated a statistically significant difference in mean age across attendance status (t = 2.1448, dof = 401, p = 0.03257)

```{r}
x_vals <- comp_data |> 
  filter(full_attendance) |>
  select(subj_age)

y_vals <- comp_data |> 
  filter(!full_attendance) |>
  select(subj_age)

t.test(x_vals, y_vals, alternative = 'two.sided', var.equal=TRUE)
```

```{r}
rm(x_vals)
rm(y_vals)
```


#### Categorical Variables

Categorical variables were tested using a Chi-Square or Fisher's Exact Test for Association.

Gender had expected counts < 5 in cells, due to low counts in the Gender of "Other". As such, Fisher's Exact Test was utilized. Fisher's exact testing demonstrated no statistically significant association between Gender and attendance compliance (p=0.1771).

```{r}
gender_table <- table(comp_data[['full_attendance']], comp_data[['subj_gender']])

fisher.test(gender_table)
```

```{r}
rm(gender_table)
```


Race had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Race and attendance status (X<sup>2</sup> = 2.4804, dof = 2, p = 0.2893).

```{r}
race_table <- table(comp_data[['full_attendance']], comp_data[['subj_race_3cat']])

chisq.test(race_table)
```

```{r}
rm(race_table)
```


Ethnicity (Hispanic Origin) had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Ethnicity and attendance status (X<sup>2</sup> = 1.3398 x 10<sup>-30</sup>, dof = 1, p = 1).

```{r}
ethnicity_table <- table(comp_data[['full_attendance']], comp_data[['subj_hispanic']])

chisq.test(ethnicity_table)
```

```{r}
rm(ethnicity_table)
```

Study arm had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between study arm and attendance status (X<sup>2</sup> = 4.1981, dof = 2, p = 0.1226).

```{r}
arm_table <- table(comp_data[['full_attendance']], comp_data[['group']])

chisq.test(arm_table)
```

```{r}
rm(arm_table)
```

### Comparison of each Visit to Randomization Visit

#### Visit 3 against Baseline

##### Continuous Numeric (Age)

As both groups had well over 30 subjects, age was treated as approximately normally distributed under the central limit theorem. The variances appeared to be approximately equal, which was supported by the F-test of equal variances (F = 0.99408, dof = 402/229 p = 0.952, two-sided test).

```{r}
x_vals <- comp_data |> 
  filter(v2) |>
  select(subj_age)

y_vals <- comp_data |> 
  filter(v3) |>
  select(subj_age)

var.test(unlist(x_vals), unlist(y_vals), 
         alternative = "two.sided")
```

The two-sided t-test of means with equal variance indicated a statistically significant difference in mean age across attendance status between v2 and v3 (t = -0.77774, dof = 701, p = 0.437)

```{r}
t.test(x_vals, y_vals, alternative = 'two.sided', var.equal=TRUE)
```

#### Visit 4 against Baseline

##### Continuous Numeric (Age)

As both groups had well over 30 subjects, age was treated as approximately normally distributed under the central limit theorem. The variances appeared to be approximately equal, which was supported by the F-test of equal variances (F = 1.0441, dof = 402/235 p = 0.7188, two-sided test).

```{r}
x_vals <- comp_data |> 
  filter(v2) |>
  select(subj_age)

y_vals <- comp_data |> 
  filter(v4) |>
  select(subj_age)

var.test(unlist(x_vals), unlist(y_vals), 
         alternative = "two.sided")
```

The two-sided t-test of means with equal variance indicated a statistically significant difference in mean age across attendance status between v2 and v4 (t = -0.54499, dof = 637, p = 0.5859)

```{r}
t.test(x_vals, y_vals, alternative = 'two.sided', var.equal=TRUE)
```

```{r}
rm(x_vals)
rm(y_vals)
```

##### Categorical Variables

Categorical variables were tested using a Chi-Square or Fisher's Exact Test for Association.

Gender had expected counts < 5 in cells, due to low counts in the Gender of "Other". As such, Fisher's Exact Test was utilized. Fisher's exact testing demonstrated no statistically significant association between Gender and attendance compliance between v2 and v4 (p=0.409).

```{r}
gender_table <- table(comp_data[['v4']], comp_data[['subj_gender']])

fisher.test(gender_table)
```

```{r}
rm(gender_table)
```


Race had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Race and attendance compliance between v2 and v4 (X<sup>2</sup> = 0.9439, dof = 2, p = 0.6238).

```{r}
race_table <- table(comp_data[['v4']], comp_data[['subj_race_3cat']])

chisq.test(race_table)
```

```{r}
rm(race_table)
```


Ethnicity (Hispanic Origin) had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Ethnicity and attendance compliance between v2 and v4 (X<sup>2</sup> = 0.64181, dof = 1, p = 0.4231).

```{r}
ethnicity_table <- table(comp_data[['v4']], comp_data[['subj_hispanic']])

chisq.test(ethnicity_table)
```

```{r}
rm(ethnicity_table)
```

Study arm had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between study arm and attendance compliance between v2 and v4 (X<sup>2</sup> = 3.4184, dof = 2, p = 0.181).

```{r}
arm_table <- table(comp_data[['v4']], comp_data[['group']])

chisq.test(arm_table)
```

```{r}
rm(arm_table)
```

#### Visit 5 against Baseline

##### Continuous Numeric (Age)

As both groups had well over 30 subjects, age was treated as approximately normally distributed under the central limit theorem. The variances appeared to be approximately equal, which was supported by the F-test of equal variances (F = 1.0924, dof = 402/216 p = 0.4684, two-sided test).

```{r}
x_vals <- comp_data |> 
  filter(v2) |>
  select(subj_age)

y_vals <- comp_data |> 
  filter(v5) |>
  select(subj_age)

var.test(unlist(x_vals), unlist(y_vals), 
         alternative = "two.sided")
```

The two-sided t-test of means with equal variance indicated a statistically significant difference in mean age across attendance status between v2 and v5 (t = -1.2795, dof = 618, p = 0.2012)

```{r}
t.test(x_vals, y_vals, alternative = 'two.sided', var.equal=TRUE)
```

```{r}
rm(x_vals)
rm(y_vals)
```

##### Categorical Variables

Categorical variables were tested using a Chi-Square or Fisher's Exact Test for Association.

Gender had expected counts < 5 in cells, due to low counts in the Gender of "Other". As such, Fisher's Exact Test was utilized. Fisher's exact testing demonstrated no statistically significant association between Gender and attendance compliance between v2 and v5 (p=0.4437).

```{r}
gender_table <- table(comp_data[['v5']], comp_data[['subj_gender']])

fisher.test(gender_table)
```

```{r}
rm(gender_table)
```


Race had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Race and attendance compliance between v2 and v5 (X<sup>2</sup> = 1.7729, dof = 2, p = 0.4121).

```{r}
race_table <- table(comp_data[['v5']], comp_data[['subj_race_3cat']])

chisq.test(race_table)
```

```{r}
rm(race_table)
```


Ethnicity (Hispanic Origin) had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between Ethnicity and attendance compliance between v2 and v5 (X<sup>2</sup> = 0.097412, dof = 1, p = 0.755).

```{r}
ethnicity_table <- table(comp_data[['v5']], comp_data[['subj_hispanic']])

chisq.test(ethnicity_table)
```

```{r}
rm(ethnicity_table)
```

Study arm had expected counts > 5 in all cells, and thus Chi-Square testing was utilized. This demonstrated no statistically significant association between study arm and attendance compliance between v2 and v5 (X<sup>2</sup> = 5.1862, dof = 2, p = 0.07479).

```{r}
arm_table <- table(comp_data[['v5']], comp_data[['group']])

chisq.test(arm_table)
```

```{r}
rm(arm_table)
```