---
title: "Krista Kezbers Request 2022-08-02"
output: 
  word_document:
    reference_doc: "word_style_template_01.docx"
---

# Overview

**2022-08-02 from Krista Kezbers to Brad Cannell**

Hi Brad, Is there any chance you could run a quick frequencies table for the variables below in the L2C dataset?
We have a staff member thinking about an abstract submission but wasn't sure if there was enough data to justify her research questions.
I know you are probably swamped with work, so if it's allowable/possible, feel free to send me the dataset and I can run them.
Let me know what you think.
Thanks, Krista

**2022-07-29 from Nadia Stanley to Krista Kezbers**

Hi Krista, Here are some research questions and potential variables for the topic I mentioned in our meeting today:

**Questions**:

1.  Do unhoused individuals who have certain mental health disorders (Schizophrenia, Bipolar disorder, PTSD, and other Anxiety disorders) report wrongful convictions more often than unhoused individuals without those certain mental health disorders?

2.  Is there a relationship between race and wrongful convictions among unhoused individuals?

**Variables**: (I did not see specific variable names in the appendix)

-   Screening Questionnaire

    -   Q3.
        How would you best describe your race (Check only one):

-   The Brief Homelessness Questionnaire: Question 9 and 20.

    -   Q9.
        Are you currently receiving treatment for mental health problems (example: Depression, Bipolar Disorder, Anxiety)?

    -   Q20.
        Have you ever been convicted of a crime that you did not commit?

-   Score for the MINI Mental Health Status Questionnaire (question 22 in the screening questionnaire)

-   Self-Rated Health Questionnaire: Questions 20,21, 22, and 23.
    These questions could be used to look at specific mental health issues and wrongful conviction.

    -   Q20.
        Have you ever been diagnosed with Schizophrenia or Schizoaffective disorder?

    -   Q21.
        Have you ever been diagnosed with Bipolar disorder?

    -   Q22.
        Have you ever been diagnosed with Post Traumatic Stress Disorder (PTSD)?

    -   Q23.
        Have you ever been diagnosed with an Anxiety Disorder besides PTSD?
        (examples: Panic Disorder,Generalized Anxiety Disorder, Obsessive Compulsive Disorder)


# Load packages

```{r}
library(dplyr, warn.conflicts = FALSE)
library(freqtables)
```


# Load data

```{r}
l2c <- readr::read_rds("../../Participant Data/R data/combined_participant_data.rds")
dim(l2c) # 1285 1205
```


# Data management

Remove "haven_labelled" and "vctrs_vctr" classes

```{r}
for (col in names(l2c)) {
  # class(l2c[[col]])
  class(l2c[[col]]) <- class(l2c[[col]])[!(class(l2c[[col]]) %in% c("haven_labelled", "vctrs_vctr"))]
}
```

Keep baseline data only

```{r}
l2c_v1 <- filter(l2c, visit == 1)
```


# Analysis

```{r}
custom_freq_table <- function(.col) {
  l2c_v1 %>% 
    freq_table({{ .col }}) %>% 
    mutate(across(where(is.double), ~ round(.x, 2))) %>% 
    knitr::kable()
}

# For testing
# custom_freq_table(ml_race)
```

Race and Ethnicity

```{r}
custom_freq_table(ml_race)
```

```{r}
custom_freq_table(ml_hispanic)
```

Are you currently receiving treatment for mental health problems (example: Depression, Bipolar Disorder, Anxiety)?

```{r}
custom_freq_table(bh_9)
```

Have you ever been convicted of a crime that you did not commit?

```{r}
custom_freq_table(bh_26)
```

Score for the MINI Mental Health Status Questionnaire (question 22 in the screening questionnaire)

```{r}
meantables::mean_table(l2c_v1, mms_score) %>% knitr::kable()
```

Have you ever been diagnosed with Schizophrenia or Schizoaffective disorder?

```{r}
custom_freq_table(srh_20)
```

Have you ever been diagnosed with Bipolar disorder?

```{r}
custom_freq_table(srh_21)
```

Have you ever been diagnosed with Post Traumatic Stress Disorder (PTSD)?

```{r}
custom_freq_table(srh_22)
```

Have you ever been diagnosed with an Anxiety Disorder besides PTSD? (examples: Panic Disorder,Generalized Anxiety Disorder, Obsessive Compulsive Disorder)

```{r}
custom_freq_table(srh_23)
```