---
title: "Mental Health Medication Adherence among Recently Incarcerated Homeless"
---

# ⭐️Overview

2022-08-06: Received abstract proposal from Michael. The proposal is in: L2C Teams/Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form.docx

The purpose of the current study is to compare psychiatric medications adherence across diagnoses and to explore how mobile health apps can be used to increase medication adherence. 

## Questions

1. What to do about insurance some people have zeros all the way across -- Even for None? Right now, they are missing.

# 📦Load packages

```{r}
library(dplyr, warn.conflicts = FALSE)
library(dagitty)
library(ggdag, warn.conflicts = FALSE)
library(ggplot2)
library(haven) # Must use any time you are working with haven labeled data
library(readr)
library(freqtables)
library(meantables)
library(purrr)
library(tidyr)
library(stringr)
library(flextable)
library(officer)
```

# 📥Import data 

This data was created in data_survey_31_update_all_data.Rmd

```{r}
l2c <- readr::read_rds("../../Participant Data/R data/combined_participant_data.rds")
dim(l2c) # 1285 1205
```

# 🚧Data management

Keep baseline data only

```{r}
l2c_v1 <- filter(l2c, visit == 1)
dim(l2c_v1) # 360 1205
```

## Variables needed

Independent Variables:

* Have you ever been diagnosed with Depression? [srh_19]
* Have you ever been diagnosed with Schizophrenia or Schizoaffective disorder? [srh_20]
* Have you ever been diagnosed with Bipolar disorder? [srh_21]
* Have you ever been diagnosed with Post Traumatic Stress Disorder (PTSD)? [srh_22]
* Have you ever been diagnosed with an Anxiety Disorder besides PTSD? [srh_23]

Dependent Variables:

* I have a prescription for the following disorders: (check all that apply)
  * Depression: [srh_24a]
  * Schizophrenia or Schizoaffective disorder: [srh_24b]
  * Bipolar Disorder: [srh_24c]
  * Anxiety Disorder: [srh_24d]
  * Post Traumatic Stress Disorder (PTSD): [srh_24e]
  * None of the above: [srh_24f]

* What were the reasons that you did not take your depression medication yesterday? (check all that apply)
  * Side effects:  [srh_26a]
  * Forgot: [srh_26b]
  * The medication is not working: [srh_26c]
  * I do not need the medication anymore: [srh_26d]
  * I have not picked up the medication from the pharmacy: [srh_26e]
  * I cannot get the medication refilled: [srh_26f]
  * Other reasons: [srh_26g]

* What were the reasons that you did not take your Schizophrenia or Schizoaffective disorder medication yesterday? (check all that apply)
  * Side effects:  [srh_28a]
  * Forgot: [srh_28b]
  * The medication is not working: [srh_28c]
  * I do not need the medication anymore: [srh_28d]
  * I have not picked up the medication from the pharmacy: [srh_28e]
  * I cannot get the medication refilled: [srh_28f]
  * Other reasons: [srh_28g]

* What were the reasons that you did not take your Bipolar Disorder medication yesterday? (check all that apply)
  * Side effects:  [srh_30a]
  * Forgot: [srh_30b]
  * The medication is not working: [srh_30c]
  * I do not need the medication anymore: [srh_30d]
  * I have not picked up the medication from the pharmacy: [srh_30e]
  * I cannot get the medication refilled: [srh_30f]
  * Other reasons: [srh_30g]

* What were the reasons that you did not take your Anxiety Disorder medication yesterday? (check all that apply)
  * Side effects:  [srh_32a]
  * Forgot: [srh_32b]
  * The medication is not working: [srh_32c]
  * I do not need the medication anymore: [srh_32d]
  * I have not picked up the medication from the pharmacy: [srh_32e]
  * I cannot get the medication refilled: [srh_32f]
  * Other reasons: [srh_32g]

* What were the reasons that you did not take your PTSD medication yesterday? (check all that apply)
  * Side effects:  [srh_34a]
  * Forgot: [srh_34b]
  * The medication is not working: [srh_34c]
  * I do not need the medication anymore: [srh_34d]
  * I have not picked up the medication from the pharmacy: [srh_34e]
  * I cannot get the medication refilled: [srh_34f]
  * Other reasons: [srh_34g]
  
* Did you take your depression medication yesterday? [srh_25]
* Did you take your Schizophrenia or Schizoaffective disorder medication yesterday? [srh_27]
* Did you take your Bipolar Disorder medication yesterday? [srh_29]
* Did you take your Anxiety Disorder medication yesterday? [srh_31]
* Did you take your PTSD medication yesterday? [srh_33]

Covariates:

* Gender: [ml_gender]
* Latinx: [ml_hispanic]
* Race: [ml_race]
* Age: [ml_age]
* Release from Dallas Jail: [sq_7]
* Current Homelessness: [sq_8]
* Education: [dem_edu_20_cat]
* Insurance: [dem_ins_medicare:dem_ins_none]    
* Do you believe that a smartphone app can help you to change your actions or behavior? [srh_50]
* Have you ever used a smartphone app to manage one or more health-related issues? [srh_51]
* Food/calorie tracking: What type of health related issue? [srh_52a]
* Medication reminders: What type of health related issue? [srh_52b]
* Mood manager: What type of health related issue? [srh_52c]
* Physical activity: What type of health related issue? [srh_52d]
* Sleep Tracker: What type of health related issue? [srh_52e]
* Smoking Cessation: What type of health related issue? [srh_52f]
* Stress reduction: What type of health related issue? [srh_52g]
* Weight loss tracking: What type of health related issue? [srh_52h]
* Other: What type of health related issue? [srh_52i]

```{r}
l2c_v1_analysis <- l2c_v1 %>% 
  select(
    id, group, ml_gender, ml_race, ml_hispanic, ml_age, dem_edu_20_cat, 
    dem_ins_medicare:dem_ins_none, srh_19:srh_23, srh_24a:srh_24f, srh_26a:srh_26g, 
    srh_28a:srh_28g, srh_30a:srh_30g, srh_32a:srh_32g, srh_34a:srh_34g, srh_25, 
    srh_27, srh_29, srh_31, srh_33, srh_50, srh_51, srh_52a:srh_52i
  )

dim(l2c_v1_analysis) # 360  74
```

## 🧮Recode/calculate variables

### Group

Create a variable that indicates if the participant was in a smartphone group or not.

```{r}
l2c_v1_analysis <- l2c_v1_analysis %>% 
  mutate(
    group = factor(group, 1:3, c("UCM", "UCM+SP", "L2C")),
    smart_phone = if_else(group == "UCM", "No", "Yes", NA_character_) %>% factor()
  )
```


### Demographic variables

* Coerce race and gender to factors
* Collapse education categories, coerce to factor
* Collapse insurance categories, coerce to factor

```{r}
l2c_v1_analysis <- l2c_v1_analysis %>%
  mutate(
    
    # Gender
    gender_f = factor(ml_gender, c("M", "F", "Other"), c("Male", "Female", "Other")),
    
    # Race/ethnicity
    race_3cat = case_when(
      is.na(ml_race)  ~ NA_character_,
      ml_race == "AA" ~ "Black or African American",
      ml_race == "W"  ~ "White",
      TRUE         ~ "Other"
    ),
    race_3cat_f = factor(
      race_3cat,
      c("Black or African American", "White", "Other")
    ),
    hispanic_f = factor(ml_hispanic, c("N", "Y"), c("Non-Hispanic", "Hispanic")),
    race_4cat = case_when(
      is.na(hispanic_f) ~ NA_integer_, # Missing - can't determine Hispanic ethnicity
      hispanic_f == "Hispanic" ~ 3L, # Hispanic, any race
      is.na(race_3cat_f) ~ NA_integer_, # Missing - We know non-Hispanic, but not race
      race_3cat_f == "White" ~ 1L, # White, non-Hispanic
      race_3cat_f == "Black or African American" ~ 2L, # Black, non-Hispanic
      race_3cat_f == "Other" ~ 4L # Other race, non-Hispanic
    ),
    race_4cat_f = factor(
      race_4cat,
      c(1L:4L),
      c("White, non-Hispanic", "Black, non-Hispanic", "Hispanic, any race", "Other race, non-Hispanic")
    ),
    
    # Education
    edu_4cat = case_when(
      dem_edu_20_cat < 12 ~ 1L, # Less than HS
      dem_edu_20_cat == 12 ~ 2L, # HS or GED
      dem_edu_20_cat < 16 ~ 3L, # HS grad, no Bachelors
      dem_edu_20_cat <= 20 ~ 4L # Bachelors or higher
    ),
    edu_4cat_f = factor(
      edu_4cat,
      c(1L:4L),
      c("Less than HS", "HS or GED", "HS grad, no Bachelors", "Bachelors or higher")
    )
  ) %>% 
  
  # Insurance
  rowwise() %>% 
  mutate(ins_count = sum(c_across(dem_ins_medicare:dem_ins_private))) %>% 
  ungroup() %>% 
  mutate(
    ins_6cat = case_when(
      dem_ins_none == 1     ~ 6, # None
      ins_count > 1         ~ 5, # Multiple
      dem_medicaid == 1     ~ 1, # Medicaid
      dem_ins_medicare == 1 ~ 2, # Medicare
      dem_ins_private == 1  ~ 3, # Private
      dem_ins_military == 1 ~ 4  # Military
    ),
    ins_6cat_f = factor(
      ins_6cat, 1:6,
      c("Medicaid", "Medicare", "Private", "Military", "Multiple", "None")
    ),
    ins_any = if_else(ins_6cat_f == "None", 0, 1),
    ins_any_f = factor(ins_any, 0:1, c("No", "Yes"))
  ) %>% 
  
  # Relocate calculated variables
  relocate(gender_f, .after = ml_gender) %>% 
  relocate(c(race_3cat, race_3cat_f), .after = ml_race) %>% 
  relocate(hispanic_f, .after = ml_hispanic) %>% 
  relocate(c(edu_4cat, edu_4cat_f), .after = dem_edu_20_cat) %>% 
  relocate(c(ins_count, ins_6cat, ins_6cat_f, ins_any, ins_any_f), .after = dem_ins_private)

dim(l2c_v1_analysis) # 360  87
```

### Independent Variables

* Have you ever been diagnosed with Depression? [srh_19]
* Have you ever been diagnosed with Schizophrenia or Schizoaffective disorder? [srh_20]
* Have you ever been diagnosed with Bipolar disorder? [srh_21]
* Have you ever been diagnosed with Post Traumatic Stress Disorder (PTSD)? [srh_22]
* Have you ever been diagnosed with an Anxiety Disorder besides PTSD? [srh_23]

```{r}
l2c_v1_analysis <- l2c_v1_analysis %>%
  # select(srh_19:srh_23) %>% 
  rowwise() %>% 
  mutate(diag_count = sum(c_across(srh_19:srh_23))) %>% 
  ungroup() %>% 
  mutate(diag_any = diag_count > 0) %>% 
  # Coerce to factors
  mutate(
    across(
      srh_19:srh_23,
      ~ factor(.x, 0:1, c("No", "Yes"))
    )
  ) %>% 
  # Rename for imporoved readability
  rename(
    depression = srh_19, schizophrenia = srh_20, bipolar = srh_21, 
    ptsd = srh_22, anxiety = srh_23
  )

dim(l2c_v1_analysis) # 360  89
```

### Dependent Variables

* I have a prescription for the following disorders: (check all that apply)
  * Depression: [srh_24a]
  * Schizophrenia or Schizoaffective disorder: [srh_24b]
  * Bipolar Disorder: [srh_24c]
  * Anxiety Disorder: [srh_24d]
  * Post Traumatic Stress Disorder (PTSD): [srh_24e]
  * None of the above: [srh_24f]
  
* Did you take your depression medication yesterday? [srh_25]
* Did you take your Schizophrenia or Schizoaffective disorder medication yesterday? [srh_27]
* Did you take your Bipolar Disorder medication yesterday? [srh_29]
* Did you take your Anxiety Disorder medication yesterday? [srh_31]
* Did you take your PTSD medication yesterday? [srh_33]

* What were the reasons that you did not take your depression medication yesterday? (check all that apply)
  * Side effects:  [srh_26a]
  * Forgot: [srh_26b]
  * The medication is not working: [srh_26c]
  * I do not need the medication anymore: [srh_26d]
  * I have not picked up the medication from the pharmacy: [srh_26e]
  * I cannot get the medication refilled: [srh_26f]
  * Other reasons: [srh_26g]

* What were the reasons that you did not take your Schizophrenia or Schizoaffective disorder medication yesterday? (check all that apply)
  * Side effects:  [srh_28a]
  * Forgot: [srh_28b]
  * The medication is not working: [srh_28c]
  * I do not need the medication anymore: [srh_28d]
  * I have not picked up the medication from the pharmacy: [srh_28e]
  * I cannot get the medication refilled: [srh_28f]
  * Other reasons: [srh_28g]

* What were the reasons that you did not take your Bipolar Disorder medication yesterday? (check all that apply)
  * Side effects:  [srh_30a]
  * Forgot: [srh_30b]
  * The medication is not working: [srh_30c]
  * I do not need the medication anymore: [srh_30d]
  * I have not picked up the medication from the pharmacy: [srh_30e]
  * I cannot get the medication refilled: [srh_30f]
  * Other reasons: [srh_30g]

* What were the reasons that you did not take your Anxiety Disorder medication yesterday? (check all that apply)
  * Side effects:  [srh_32a]
  * Forgot: [srh_32b]
  * The medication is not working: [srh_32c]
  * I do not need the medication anymore: [srh_32d]
  * I have not picked up the medication from the pharmacy: [srh_32e]
  * I cannot get the medication refilled: [srh_32f]
  * Other reasons: [srh_32g]

* What were the reasons that you did not take your PTSD medication yesterday? (check all that apply)
  * Side effects:  [srh_34a]
  * Forgot: [srh_34b]
  * The medication is not working: [srh_34c]
  * I do not need the medication anymore: [srh_34d]
  * I have not picked up the medication from the pharmacy: [srh_34e]
  * I cannot get the medication refilled: [srh_34f]
  * Other reasons: [srh_34g]
  
#### Any prescription for the disorders listed above

For each of the questions about prescriptions for specific medications (srh_24a:srh_24e), did the participant respond "yes" to any?
* Yes to any one of them should be a "Yes"
* No to all of them should be a "No"
* NA for any of them should be an NA
* Yes to srh_24f (prescribed none) and a Yes to any of srh_24a:srh_24e should be an NA. Unreliable.
  
```{r}
l2c_v1_analysis <- l2c_v1_analysis %>% 
  # For testing
  # select(srh_24a:srh_24f) %>% 
  # Create a new var: prescribed_any
  rowwise() %>% 
  mutate(
    prescribed_count = sum(c_across(c(srh_24a:srh_24e))),
    prescribed_any   = prescribed_count > 0
  ) %>% 
  # Data check: Missing prescribed_any
  # filter(is.na(prescribed_any)) %>% # 0 rows
  ungroup() %>% 
  # Data check: How many reported a prescription AND said prescribed none?
  # filter(srh_24f == 1 & prescribed_any == TRUE) %>%  # 5. Change to NA - Unreliable
  mutate(
    across(
      c(srh_24f, srh_24a, srh_24b, srh_24c, srh_24d, srh_24e, prescribed_count, prescribed_any),
      ~ ifelse(srh_24f == 1 & prescribed_any == TRUE, NA, .x)
    )
  )

dim(l2c_v1_analysis) # 360  91
```

#### Missed taking a any meds yesterday

Among those who were given a prescription for a medication (srh_24a:srh_24e), how many reported that they did not take it yesterday (srh_25, 27, 29, 31, 33)?

So, 
- For each medication question, did they say yes? 
- If they said yes, did they respond to the "did you take it yesterday" question? 
- Among those who responded to the "did you take it yesterday" question, for every condition that they responded "yes" to having prescription for, how many said yes and no to missing yesterday?

**Data check:** How many of those who reported a prescription have a missing value for did you take it yesterday? None as of 2022-09-06.

```{r}
l2c_v1_analysis %>% 
  # Line up prescription next to take or not for testing
  select(
    srh_24f, # None
    srh_24a, srh_25, # Depression prescription have/take
    srh_24b, srh_27, # Schizophrenia prescription have/take
    srh_24c, srh_29, # Bipolar prescription have/take
    srh_24d, srh_31, # Anxiety prescription have/take
    srh_24e, srh_33  # PTSD prescription have/take
  ) %>% 
  # Create new vars for missing take prescription response
  # If you said "yes" to having a prescription (e.g., srh_24a), did you give a 
  # response to taking it yesterday (e.g., srh_25)?
  mutate(
    dep_yest_miss = srh_24a == 1 & is.na(srh_25),
    sch_yest_miss = srh_24b == 1 & is.na(srh_27),
    bip_yest_miss = srh_24c == 1 & is.na(srh_29),
    anx_yest_miss = srh_24d == 1 & is.na(srh_31),
    pts_yest_miss = srh_24e == 1 & is.na(srh_33)
  ) %>%
  summarise(across(dep_yest_miss:pts_yest_miss, sum, na.rm = TRUE))
```

From above, we know that everyone who reported having a prescription (srh_24a:srh_24e) has a non-missing value for the follow-up "did you take it yesterday" question. Next, let's determine:

1. How many people who were prescribed each type of medication forgot to take it yesterday?
2. How many people who were prescribed any type of medication forgot to take it yesterday?
  
```{r}
l2c_v1_analysis <- l2c_v1_analysis %>%
  # Line up prescription next to take or not for testing
  # select(
  #   srh_24f, # None
  #   srh_24a, srh_25, # Depression prescription have/take
  #   srh_24b, srh_27, # Schizophrenia prescription have/take
  #   srh_24c, srh_29, # Bipolar prescription have/take
  #   srh_24d, srh_31, # Anxiety prescription have/take
  #   srh_24e, srh_33  # PTSD prescription have/take
  # ) %>% 
  
  # Create new vars: prescribed_x_missed
  # If they were ever prescribed a medication, did they answer "no" to any of
  # the "Did you take your X medication yesterday?" questions?
  mutate(
    prescribed_dep_missed = srh_24a == 1 & srh_25 == 0,
    prescribed_schiz_missed = srh_24b == 1 & srh_27 == 0,
    prescribed_bipo_missed = srh_24c == 1 & srh_29 == 0,
    prescribed_anx_missed = srh_24d == 1 & srh_31 == 0,
    prescribed_ptsd_missed = srh_24e == 1 & srh_33 == 0
  ) %>% 
  # Convert FALSE to NA if they weren't prescribed the medication in the first 
  # place. For example, a person who has a value of 0 for srh_24a (prescribed
  # depression meds) and a value of NA for srh_25 (took depression meds 
  # yesterday) currently has a value of FALSE for prescribed_dep_missed (missed
  # depression meds yesterday). Really, it makes more sense for them to have an NA.
  mutate(
    prescribed_dep_missed = if_else(srh_24a == 0, NA, prescribed_dep_missed),
    prescribed_schiz_missed = if_else(srh_24b == 0, NA, prescribed_schiz_missed),
    prescribed_bipo_missed = if_else(srh_24c == 0, NA, prescribed_bipo_missed),
    prescribed_anx_missed = if_else(srh_24d == 0, NA, prescribed_anx_missed),
    prescribed_ptsd_missed = if_else(srh_24e == 0, NA, prescribed_ptsd_missed)
  ) %>% 
  
  # Count number of missed across prescription types
  # select(prescribed_dep_missed:prescribed_ptsd_missed) %>% # For testing
  rowwise() %>%
  mutate(
    prescribed_missed_count = sum(
      c_across(prescribed_dep_missed:prescribed_ptsd_missed),
      na.rm = TRUE
    ),
    # If all "missed" are NA, then prescribed_missed_count should be NA, not 0
    prescribed_missed_na_count = sum(is.na(
      c_across(prescribed_dep_missed:prescribed_ptsd_missed)
    )),
    prescribed_missed_count = if_else(
      prescribed_missed_na_count == 5, NA_integer_, prescribed_missed_count
    )
  ) %>% 
  ungroup() %>% 
  
  # Create a new var: prescribed_missed_any
  # If prescribed_missed_count is > 0, then they where prescribed at least one 
  # medication AND told us that they did not take that prescribed medication
  # yesterday.
  mutate(prescribed_missed_any = if_else(prescribed_missed_count > 0, TRUE, FALSE, NA)) %>% 
  
  # Coerce to factors
  mutate(
    across(
      srh_24a:srh_52i,
      ~ factor(.x, 0:1, c("No", "Yes"))
    )
  ) %>% 
  
  # Rename for improved readability
  rename(
    meds_depression = srh_24a, meds_schizophrenia = srh_24b, 
    meds_bipolar = srh_24c, meds_anxiety = srh_24d, meds_ptsd = srh_24e,
    meds_none = srh_24f,
    meds_depression_yest = srh_25, meds_schizophrenia_yest = srh_27,
    meds_bipolar_yest = srh_29, meds_anxiety_yest = srh_31,
    meds_ptsd_yest = srh_33
  )

dim(l2c_v1_analysis) # 360  99
```

#### Resons for not taking meds

* What were the reasons that you did not take your depression medication yesterday? (check all that apply)
  * Side effects:  [srh_26a]
  * Forgot: [srh_26b]
  * The medication is not working: [srh_26c]
  * I do not need the medication anymore: [srh_26d]
  * I have not picked up the medication from the pharmacy: [srh_26e]
  * I cannot get the medication refilled: [srh_26f]
  * Other reasons: [srh_26g]
  
* Schizophrenia = srh_28a:srh_28g
* Bipolar = srh_30a:srh_30g
* Anxiety = srh_32a:srh_32g
* PTSD = srh_34a:srh_34g

Rename the columns listed above to make them more informative

```{r}
prefixes <- c("dep", "schiz", "bip", "anx", "ptsd") %>% rep(each = 7)
reasons <- c("side_effects", "forgot", "not_work", "not_need", "not_pick_up", "no_refill", "other")
new_names <- paste(prefixes, reasons, sep = "_")
l2c_v1_analysis <- l2c_v1_analysis %>% 
  rename_with(
    .cols = c(srh_26a:srh_34g),
    .fn = ~new_names
  )
```

### Other covariates

* Do you believe that a smartphone app can help you to change your actions or behavior? [srh_50]
* Have you ever used a smartphone app to manage one or more health-related issues? [srh_51]
* Food/calorie tracking: What type of health related issue? [srh_52a]
* Medication reminders: What type of health related issue? [srh_52b]
* Mood manager: What type of health related issue? [srh_52c]
* Physical activity: What type of health related issue? [srh_52d]
* Sleep Tracker: What type of health related issue? [srh_52e]
* Smoking Cessation: What type of health related issue? [srh_52f]
* Stress reduction: What type of health related issue? [srh_52g]
* Weight loss tracking: What type of health related issue? [srh_52h]
* Other: What type of health related issue? [srh_52i]

```{r}
# At this moment, I don't think there is any calculated variables I need to create. 
# I'm going to start by just looking at "did you take your medication?" by diagnosis.
```

# 📈Analysis

The purpose of the current study is to compare psychiatric medications adherence across diagnoses and to explore how mobile health apps can be used to increase medication adherence. 

```{r}
coord_dag <- list(
  x = c(x = 1, c = 2, y = 3),
  y = c(x = 0, c = 1, y = 0)
)

dag <- ggdag::dagify(
  y ~ x,
  x ~ c,
  y ~ c,
  coords = coord_dag,
  labels = c(
    "y" = "Medication \n Adherence", 
    "c" = "Covariates",
    "x" = "MH Diagnosis"
  )
)

ggdag::ggdag(
  dag, # the dag object we created
  text = FALSE, # this means the original names won't be shown
  use_labels = "label") + # instead use the new names
  theme_dag()
```

## MH Diagnosis

How many people had each type of MH diagnosis (srh_19:srh_23)?

* I have a prescription for the following disorders: (check all that apply)
  * Depression: [srh_24a]
  * Schizophrenia or Schizoaffective disorder: [srh_24b]
  * Bipolar Disorder: [srh_24c]
  * Anxiety Disorder: [srh_24d]
  * Post Traumatic Stress Disorder (PTSD): [srh_24e]
  * None of the above: [srh_24f]

```{r}
# One var
l2c_v1_analysis %>% 
  freq_table(!! sym("depression"))
```

```{r}
# Many vars
map_df(
  select(l2c_v1_analysis, depression:anxiety) %>% names(),
  ~ l2c_v1_analysis %>% 
      freq_table(!! sym(.x)) %>% 
      filter(cat == "Yes")
)
```

## Have prescription

How many people had a prescription for each medication? 

* I have a prescription for the following disorders: (check all that apply)
  * Depression: [srh_24a]
  * Schizophrenia or Schizoaffective disorder: [srh_24b]
  * Bipolar Disorder: [srh_24c]
  * Anxiety Disorder: [srh_24d]
  * Post Traumatic Stress Disorder (PTSD): [srh_24e]
  * None of the above: [srh_24f]

```{r}
# One var
l2c_v1_analysis %>% 
  filter(!is.na(!! sym("meds_depression"))) %>% 
  freq_table(!! sym("meds_depression"))
```

```{r}
# Many vars
map_df(
  select(l2c_v1_analysis, meds_depression:meds_ptsd) %>% names(),
  ~ l2c_v1_analysis %>% 
      filter(!is.na(!! sym(.x))) %>% 
      freq_table(!! sym(.x)) %>% 
      filter(cat == "Yes")
)
```

## Missed prescription yesterday

How many people who were prescribed each type of medication forgot to take it yesterday?

* Did you take your depression medication yesterday? [srh_25]
* Did you take your Schizophrenia or Schizoaffective disorder medication yesterday? [srh_27]
* Did you take your Bipolar Disorder medication yesterday? [srh_29]
* Did you take your Anxiety Disorder medication yesterday? [srh_31]
* Did you take your PTSD medication yesterday? [srh_33]

```{r}
# One var
l2c_v1_analysis %>% 
  # Keep only people with a prescription
  filter(!! sym("meds_depression") == "Yes") %>% 
  freq_table(!! sym("meds_depression_yest"))
```

```{r}
# Many vars
map2_df(
  select(l2c_v1_analysis, meds_depression:meds_ptsd) %>% names(),
  select(l2c_v1_analysis, meds_depression_yest:meds_ptsd_yest) %>% names(),
  ~ l2c_v1_analysis %>% 
    # Keep only people with a prescription
    filter(!! sym(.x) == "Yes") %>% 
    freq_table(!! sym(.y)) %>% 
    # DID NOT take medication only
    filter(cat == "No")
) %>% 
  arrange(desc(percent))
```

How many people who were prescribed any type of medication forgot to take it yesterday?

```{r}
l2c_v1_analysis %>% 
  filter(prescribed_any == TRUE) %>% 
  freq_table(prescribed_missed_any)
```

How many people missed taking their medication yesterday by ever having each mental health diagnosis?

```{r}
# One var
l2c_v1_analysis %>% 
  # Remove missing prescribed_missed_any
  filter(!is.na(prescribed_missed_any)) %>% 
  freq_table(!! sym("depression"), !! sym("prescribed_missed_any"))
```

```{r}
map_df(
  # Mental health diagnosis
  select(l2c_v1_analysis, depression:anxiety) %>% names(),
  ~ l2c_v1_analysis %>% 
    # Remove missing prescribed_missed_any
    filter(!is.na(prescribed_missed_any)) %>% 
    freq_table(!! sym(.x), prescribed_missed_any) %>% 
    # DID NOT take medication only
    filter(col_cat == TRUE)
) %>% 
  select(row_var:n_total, percent_row, lcl_row:ucl_row)
```

## Table 1

Define variable list

```{r}
cont_vars <- c("ml_age")
```

```{r}
cat_vars <- c(
  "depression", "schizophrenia", "bipolar", "ptsd", "anxiety", "gender_f", 
  "race_4cat_f", "edu_4cat_f"
)
```

Filter out rows with a missing value for prescribed_missed_any

```{r}
l2c_v1_analysis_complete <- l2c_v1_analysis %>% 
  filter(!is.na(prescribed_missed_any))

dim(l2c_v1_analysis_complete) # 207  99
```

Function cont by group

```{r}
cont_stats_group_fn <- function(.data, .group, .pred, stat_recipe = NULL, .digits = 2) {
  .data %>% 
    # Remove rows with missing values
    filter(!is.na({{ .pred }})) %>%
    group_by({{ .group }}) %>%
    # Calculations
    mean_table({{ .pred }}) %>%  
    # Format statistics
    mean_format(stat_recipe, digits = .digits) %>% 
    # Keep columns of interest
    select(var = response_var, group_cat, formatted_stats) %>%
    # Display by row_cat
    pivot_wider(
      names_from = "group_cat",
      values_from = "formatted_stats"
    )
}

# Test
# cont_stats_group_fn(l2c_v1_analysis_complete, prescribed_missed_any, ml_age, stat_recipe = "mean (sd)")
```

Loop over all continuous variables

```{r}
cont_by_group <- map_df(
  .x = cont_vars,
  .f = ~ cont_stats_group_fn(l2c_v1_analysis_complete, prescribed_missed_any, !! sym(.x), stat_recipe = "mean (sd)")
)
```

Function cat by group

```{r}
cat_stats_group_fn <- function(.data, .outcome, .pred, stat_recipe = NULL, .digits = 0) {
  .data %>% 
    # Remove rows with missing values
    filter(!is.na({{ .pred }})) %>% 
    # Calculations
    freq_table({{ .outcome }}, {{ .pred }}) %>%  
    # Format statistics
    freq_format(stat_recipe, digits = .digits) %>% 
    # Keep columns of interest
    select(row_var:col_cat, formatted_stats) %>%
    # Display by row_cat
    pivot_wider(
      names_from = "row_cat",
      values_from = "formatted_stats"
    ) %>%
    # Add spaces in front of category labels
    mutate(col_cat = paste0("  ", col_cat)) %>%
    # Slide category labels under row variable label
    add_row(col_cat = !!quo_name(enquo(.pred)), .before = 1) %>%
    select(-row_var, -col_var, var = col_cat) %>%
    # Paste all categories into one row
    mutate(
      across(
        everything(),
        function(x) {
          x <- paste(x, collapse = "\n")
          # Remove leading NA
          x <- stringr::str_remove(x, "^NA")
          x
        }
      )
    ) %>%
    slice(1)
}

# Test
# cat_stats_group_fn(l2c_v1_analysis_complete, prescribed_missed_any, gender_f, stat_recipe = "n (percent_row%)")
```

Loop over all categorical variables

```{r}
cat_by_group <- map_df(
  .x = cat_vars,
  .f = ~ cat_stats_group_fn(l2c_v1_analysis_complete, prescribed_missed_any, !! sym(.x), stat_recipe = "n (percent_row%)")
)
```

Bind cat and cont by group

```{r}
table_01 <- bind_rows(
  cont_by_group,
  cat_by_group
)
```

### Make flextable

```{r}
table_01_ft <- flextable(table_01)
```

Format flextable

```{r}
# N's for column headers
col_head_n <- table(l2c_v1_analysis_complete$prescribed_missed_any)
no_col_header <- paste0("None Missed Yesterday\n(n = ", col_head_n[1], ")")
yes_col_header <- paste0("Missed Yesterday\n(n = ", col_head_n[2], ")")
```

```{r}
table_01_ft <- table_01_ft %>%
  # Change column widths. figure out through trial and error
  width(width = c(2.38, 2.07, 2.07)) %>%
  # Center text in all but the first column
  align(j = -1, align = "center", part = "all") %>%
  # Change header names -- add subgroup n's to headers
  set_header_labels(
    var = "Characteristic",
    "FALSE" = no_col_header,
    "TRUE" = yes_col_header
  ) %>%
  # Bold column headers
  bold(part = "header")
```

Improve row headers

```{r}
# Get all of the variable names and add to a data frame
names_to_headers <- tibble(
  string = table_01$var,
  var_name = str_extract(string, "^\\w*"),
  type = if_else(var_name %in% cat_vars, "cat", "cont"),
  # We could maybe event grab these somewhere else if we save recipe
  # For now, just typing in manually
  stat = if_else(type == "cat", "n (col percent)", "mean (sd)")
)
```

```{r}
# Wrap all of this in a function
case_when_vars <- paste0('var_name == ', '"', names_to_headers$var_name, '"', ' ~ "",')
case_when_vars <- paste(case_when_vars, collapse = "\n    ")
case_when_vars <- str_remove(case_when_vars, ",$")
```

```{r}
# The user needs to tell us what the row header text should say
# Print some code that will help us make sure we don't miss any vars
# names_to_headers$var_name
cat(
paste0("names_to_headers <- names_to_headers %>%\n  mutate(header = case_when(\n    ", case_when_vars, "\n  ))")
)
```

```{r}
# A function for updating without starting over could be useful too.
names_to_headers <- names_to_headers %>%
  mutate(header = case_when(
    var_name == "ml_age" ~ "Age",
    var_name == "depression" ~ "Depression",
    var_name == "schizophrenia" ~ "Schizophrenia",
    var_name == "bipolar" ~ "Bipolar",
    var_name == "ptsd" ~ "PTSD",
    var_name == "anxiety" ~ "Anxiety",
    var_name == "gender_f" ~ "Gender",
    var_name == "race_4cat_f" ~ "Race/Ethnicity",
    var_name == "edu_4cat_f" ~ "Eduction"
  ))
```

```{r}
# Add the stats to the row headers
names_to_headers <- names_to_headers %>%
  mutate(header = paste0(header, ", ", stat))
```

```{r}
# Add carrot to the front of var_name so that the row header is only replaced
# when the string is found in the variable name as opposed to anywhere in string
names_to_headers$var_name <- paste0("^", names_to_headers$var_name)
```

```{r}
# Loop over all variables
for (i in 1:nrow(names_to_headers)) {
  table_01_ft <- table_01_ft %>%
    compose(
      i = ~ stringr::str_detect(var, names_to_headers$var_name[[i]]), 
      j = 1, 
      as_paragraph(str_replace(
        names_to_headers$string[[i]], 
        names_to_headers$var_name[[i]], 
        names_to_headers$header[[i]]
      ))
    )
}
```

Finish flextable formatting

```{r}
table_01_ft <- table_01_ft %>%
  # Use padding for row separation
  padding(padding.top = 0, padding.bottom = 10, part = "body") %>%
  # Change font to TNR 11
  font(fontname = "Arial", part = "all") %>%
  fontsize(part = "all", size = 11)
```

Add flextable to Word document

```{r}
doc <- read_docx("../../Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form.docx") %>% 
  body_replace_flextable_at_bkm("table_01", table_01_ft)
```

```{r}
print(
  doc,
  "../../Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form_2022_08_07.docx"
)
```

## Table 2

```{r}
preds <- c("depression", "schizophrenia", "bipolar", "ptsd", "anxiety")
```

```{r}
unadj_formulas <- paste("prescribed_missed_any", preds, sep = " ~ ")
```

```{r}
covars <- c("ml_age", "gender_f", "race_4cat_f", "edu_4cat_f")
```

```{r}
covars_mod <- paste(covars, collapse = " + ")
```

```{r}
rhs <- paste(preds, covars_mod, sep = " + ")
```

```{r}
adj_formulas <- paste("prescribed_missed_any", rhs, sep = " ~ ")
```

### Unadjusted

```{r}
# For testing
glm(
  formula = unadj_formulas[3],
  family = binomial(link = 'logit'),
  data = l2c_v1_analysis
) %>% 
  broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~ format(round(.x, 2), digits = 2, nsmall = 2)
    )
  ) %>% 
  mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
  select(term, stats) %>% 
  slice(2)
```

```{r}
# All predictors
unadj_logistic <- map_df(
  unadj_formulas,
  ~ glm(
    formula = .x,
    family = binomial(link = 'logit'),
    data = l2c_v1_analysis
  ) %>% 
    broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
    mutate(
      across(
        where(is.numeric), 
        ~ format(round(.x, 2), digits = 2, nsmall = 2)
      )
    ) %>% 
    mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
    select(term, stats) %>% 
    slice(2)
)
```

### Check for effect measure modification\

```{r}
emm_rhs <- paste(preds, "smart_phone", sep = "*")
emm_formulas <- paste("prescribed_missed_any", emm_rhs, sep = " ~ ")
```

```{r}
# For testing
glm(
  formula = prescribed_missed_any ~ depression*smart_phone,
  family = binomial(link = 'logit'),
  data = l2c_v1_analysis
) %>% 
  broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~ format(round(.x, 2), digits = 2, nsmall = 2)
    )
  ) %>% 
  mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
  select(term, stats) %>% 
  slice(4)
```

```{r}
# All predictors
map_df(
  emm_formulas,
  ~ glm(
    formula = .x,
    family = binomial(link = 'logit'),
    data = l2c_v1_analysis
  ) %>% 
    broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
    mutate(
      across(
        where(is.numeric), 
        ~ format(round(.x, 2), digits = 2, nsmall = 2)
      )
    ) %>% 
    mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
    mutate(stats = str_replace(stats, "- ", "-")) %>% 
    select(term, stats) %>% 
    slice(4)
)
```


### Adjusted

```{r}
# For testing
glm(
  formula = adj_formulas[1],
  family = binomial(link = 'logit'),
  data = l2c_v1_analysis
) %>% 
  broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~ format(round(.x, 2), digits = 2, nsmall = 2)
    )
  ) %>% 
  mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
  mutate(stats = str_replace(stats, "- ", "-")) %>%
  select(term, stats) %>% 
  slice(2)
```

```{r}
# All predictors
adj_logistic <- map_df(
  adj_formulas,
  ~ glm(
    formula = .x,
    family = binomial(link = 'logit'),
    data = l2c_v1_analysis
  ) %>% 
    broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
    mutate(
      across(
        where(is.numeric), 
        ~ format(round(.x, 2), digits = 2, nsmall = 2)
      )
    ) %>% 
    mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
    mutate(stats = str_replace(stats, "- ", "-")) %>% 
    select(term, stats) %>% 
    slice(2)
)
```

### Combined Flextable

Bind cat and cont by group

```{r}
table_02 <- left_join(
  unadj_logistic,
  adj_logistic,
  by = "term",
  suffix = c("_unadj", "_adj")
)
```

Make flextable

```{r}
table_02_ft <- flextable(table_02)
```

Format flextable

```{r}
table_02_ft <- table_02_ft %>%
  # Change column widths. figure out through trial and error
  width(width = c(3.25, 1.62, 1.62)) %>%
  # Center text in all but the first column
  align(j = -1, align = "center", part = "all") %>%
  # Change header names -- add subgroup n's to headers
  set_header_labels(
    term = "Mental health condition, ever diagnosed",
    stats_unadj = "Unadjusted\nOR (95% CI)",
    stats_adj = "Adjusted\nOR (95% CI)"
  ) %>%
  # Bold column headers
  bold(part = "header")
```

Improve row headers

```{r}
table_02_ft <- table_02_ft %>% 
  compose(i = 1, j = 1, as_paragraph(as_chunk("Depression"))) %>% 
  compose(i = 2, j = 1, as_paragraph(as_chunk("Schizophrenia or Schizoaffective disorder"))) %>% 
  compose(i = 3, j = 1, as_paragraph(as_chunk("Bipolar disorder"))) %>% 
  compose(i = 4, j = 1, as_paragraph(as_chunk("Post Traumatic Stress Disorder (PTSD)"))) %>% 
  compose(i = 5, j = 1, as_paragraph(as_chunk("Anxiety Disorder besides PTSD")))
```

Finish flextable formatting

```{r}
table_02_ft <- table_02_ft %>%
  # Use padding for row separation
  padding(padding.top = 0, padding.bottom = 10, part = "body") %>%
  # Change font to TNR 11
  font(fontname = "Arial", part = "all") %>%
  fontsize(part = "all", size = 11)
```

Add flextable to Word document

```{r}
doc <- read_docx("../../Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form.docx") %>% 
  body_replace_flextable_at_bkm("table_01", table_01_ft) %>% 
  # Overall n in title
  body_replace_text_at_bkm("n_overall", as.character(sum(table(l2c_v1_analysis_complete$prescribed_missed_any)))) %>% 
  body_replace_flextable_at_bkm("table_02", table_02_ft)
```

```{r}
print(
  doc,
  "../../Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form_2022_08_07.docx"
)
```

## Table 3

Reasons for not taking medication on the previous day by medication type.

For column headers, who many people reported not taking each medication on the previous day?

```{r}
l2c_v1_analysis %>% 
  summarise(
    across(
      prescribed_dep_missed:prescribed_ptsd_missed,
      sum, na.rm = TRUE
    )
  )
```

```{r}
# One var
l2c_v1_analysis %>% 
  # Remove missing
  filter(!is.na(!! sym("dep_side_effects"))) %>% 
  freq_table(!! sym("dep_side_effects")) %>% 
  freq_format("n (percent%)", digits = 0)
```

```{r}
# Loop over all reasons
all_reasons <- map_df(
  new_names,
  ~ l2c_v1_analysis %>% 
    # Remove missing
    filter(!is.na(!! sym(.x))) %>% 
    freq_table(!! sym(.x)) %>% 
    freq_format("n (percent%)", digits = 0) %>% 
    # Keep "Yes" only
    filter(cat == "Yes") %>% 
    # Keep var and formatted stats only
    select(var, formatted_stats)
)
```

I checked and the n_total output by the code above matches the total number of people who reported missing a medication a couple of code chunks above. 

Now let's reshape the data to make it easier to fit into the word table

```{r}
all_reasons <- all_reasons %>% 
  # Need to separate the medication type and the reason before pivoting.
  separate(var, c("med", "reason"), extra = "merge") %>% 
  pivot_wider(
    names_from = med,
    values_from = formatted_stats
  )
```

Because I'm running low on time and I already have a table outline made in the Word template document, I'm just going to output this table to a temporary Word doc. Then, I will copy and paste the values into the template.

```{r}
all_reasons_ft <- flextable(all_reasons) %>% autofit()
doc <- read_docx() %>% body_add_flextable(all_reasons_ft)
print(doc, "/Users/bradcannell/Desktop/temp.docx")
```

Add flextable to Word document

```{r}
doc <- read_docx("../../Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form.docx") %>% 
  body_replace_flextable_at_bkm("table_01", table_01_ft) %>% 
  # Overall n in title
  body_replace_text_at_bkm("n_overall", as.character(sum(table(l2c_v1_analysis_complete$prescribed_missed_any)))) %>% 
  body_replace_flextable_at_bkm("table_02", table_02_ft)
```

```{r}
print(
  doc,
  "../../Abstract Projects/Audrey Montgomery/Montgomery_AbstractAndManuscript_Proposal_Form_2022_08_08.docx"
)
```








