---
title: "Determining the Relationship Between Mental Health Disorders and Wrongful Convictions Among Unhoused Individuals"
date: "2022-08-30 <br> Updated: `r Sys.Date()`"
---

# ⭐️Overview

2022-08-06: Received abstract proposal from Michael. The proposal is in: L2C Teams/Abstract Projects/Nadia Stanley/Nstanley_Abstract_Proposal_1_80322.docx


# 📦Load packages

```{r message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(haven) # Must use any time you are working with haven labeled data
library(freqtables)
library(meantables)
library(tidyr)
library(purrr)
library(flextable)
library(officer)
library(stringr)
```


# 📥Import data 

This data was created in data_survey_31_update_all_data.Rmd

```{r}
l2c <- readr::read_rds("../../Participant Data/R data/combined_participant_data.rds")
dim(l2c) # 1285 1205
```


# 🚧Data management

Keep baseline data only

```{r}
l2c_v1 <- filter(l2c, visit == 1)
dim(l2c_v1) # 360 1205
```

Independent variables: 

Mental health disorder (The Brief Homelessness Questionnaire; question 9 & Self-Rated Health Questionnaire; questions 20, 21, 22, & 23)

* bh_9: Are you currently receiving treatment for mental health problems (For example: Depression, Bipolar Disorder, Anxiety)?

* srh_19: Have you ever been diagnosed with Depression?

* srh_20: Have you ever been diagnosed with Schizophrenia or Schizoaffective disorder?

* srh_21: Have you ever been diagnosed with Bipolar disorder?

* srh_22: Have you ever been diagnosed with Post Traumatic Stress Disorder (PTSD)?

* srh_23: Have you ever been diagnosed with an Anxiety Disorder besides PTSD? (examples: Panic Disorder, Generalized Anxiety Disorder, Obsessive Compulsive Disorder)

Dependent variables: 

Self reports of wrongful conviction (The Brief Homelessness Questionnaire; questions 15)

* bh_26: Have you ever been convicted of a crime that you did not commit?

Potential Covariates: 

* Education: dem_edu_20_cat
* Sex: ml_gender
* Age: ml_age
* Race: ml_race
* Ethnicity: ml_hispanic

```{r}
l2c_v1_analysis <- l2c_v1 %>% 
  select(id, group, bh_9, bh_26, srh_19:srh_23, ml_gender, ml_race, ml_hispanic, ml_age, dem_edu_20_cat)

dim(l2c_v1_analysis) # 360  14
```

## 🧮Recode/calculate variables

* Coerce race and gender to factors
* Collapse education categories, coerce to factor

```{r}
l2c_v1_analysis <- l2c_v1_analysis %>% 
  mutate(
    # Gender
    gender_f = factor(ml_gender, c("M", "F", "Other"), c("Male", "Female", "Other")),
    # Race/ethnicity
    race_3cat = case_when(
      is.na(ml_race)  ~ NA_character_,
      ml_race == "AA" ~ "Black or African American",
      ml_race == "W"  ~ "White",
      TRUE         ~ "Other"
    ),
    race_3cat_f = factor(
      race_3cat,
      c("Black or African American", "White", "Other")
    ),
    hispanic_f = factor(ml_hispanic, c("N", "Y"), c("Non-Hispanic", "Hispanic")),
    race_4cat = case_when(
      is.na(hispanic_f) ~ NA_integer_, # Missing - can't determine Hispanic ethnicity
      hispanic_f == "Hispanic" ~ 3L, # Hispanic, any race
      is.na(race_3cat_f) ~ NA_integer_, # Missing - We know non-Hispanic, but not race
      race_3cat_f == "White" ~ 1L, # White, non-Hispanic
      race_3cat_f == "Black or African American" ~ 2L, # Black, non-Hispanic
      race_3cat_f == "Other" ~ 4L # Other race, non-Hispanic
    ),
    race_4cat_f = factor(
      race_4cat,
      c(1L:4L),
      c("White, non-Hispanic", "Black, non-Hispanic", "Hispanic, any race", "Other race, non-Hispanic")
    ),
    # Education
    edu_4cat = case_when(
      dem_edu_20_cat < 12 ~ 1L, # Less than HS
      dem_edu_20_cat == 12 ~ 2L, # HS or GED
      dem_edu_20_cat < 16 ~ 3L, # HS grad, no Bachelors
      dem_edu_20_cat <= 20 ~ 4L # Bachelors or higher
    ),
    edu_4cat_f = factor(
      edu_4cat,
      c(1L:4L),
      c("Less than HS", "HS or GED", "HS grad, no Bachelors", "Bachelors or higher")
    )
  )

dim(l2c_v1_analysis) # 360  22
```

Coerce independent and dependent vars to factors.
I'm also going to make them more readable for the table

```{r}
l2c_v1_analysis <- l2c_v1_analysis %>%
  rename(
    mh_treatment = bh_9, depression_ever = srh_19, schizophrenia_ever = srh_20, 
    bipolar_ever = srh_21, ptsd_ever = srh_22, anxiety_ever = srh_23, 
    conviction = bh_26
  ) %>% 
  mutate(
    across(
      depression_ever:anxiety_ever,
      ~ factor(.x, 0:1, c("No", "Yes")),
      .names = "{col}_f"
    )
  )

dim(l2c_v1_analysis) # 360  27
```

# 📈Analysis

Frequencies of MH disorders
* bh_9: Are you currently receiving treatment for mental health problems (For example: Depression, Bipolar Disorder, Anxiety)?
* srh_19: Have you ever been diagnosed with Depression?
* srh_20: Have you ever been diagnosed with Schizophrenia or Schizoaffective disorder?
* srh_21: Have you ever been diagnosed with Bipolar disorder?
* srh_22: Have you ever been diagnosed with Post Traumatic Stress Disorder (PTSD)?
* srh_23: Have you ever been diagnosed with an Anxiety Disorder besides PTSD? (examples: Panic Disorder, Generalized Anxiety Disorder, Obsessive Compulsive Disorder)

```{r}
# One var
l2c_v1_analysis %>% 
  freq_table(!! sym("mh_treatment")) %>% 
  freq_format("n (percent)", digits = 1)
```

Any mental health diagnosis ever

```{r}
l2c_v1_analysis %>% 
  select(depression_ever:anxiety_ever) %>% 
  rowwise() %>% 
  mutate(
    mh_diag_ever_count = sum(c_across(everything())),
    mh_diag_ever_any = mh_diag_ever_count > 0
  ) %>% 
  ungroup() %>% 
  freq_table(mh_diag_ever_any)
```


```{r}
map_df(
  # Mental health diagnosis
  select(l2c_v1_analysis, depression:anxiety) %>% names(),
  ~ l2c_v1_analysis %>% 
    freq_table(!! sym(.x)) %>% 
    freq_format("n (percent)", digits = 1)
) %>% 
  select(var, cat, n_total, formatted_stats) %>% 
  # Show Yes only
  filter(cat == "Yes")
```

bh_26: Have you ever been convicted of a crime that you did not commit?

```{r}
l2c_v1_analysis %>% 
  freq_table(!! sym("conviction")) %>% 
  freq_format("n (percent)", digits = 1)
```

## Table 1

Define variable list

```{r}
cont_vars <- c("ml_age")
```

```{r}
cat_vars <- c(
  "depression", "schizophrenia", "bipolar", "ptsd", "anxiety", "gender_f", 
  "race_4cat_f", "edu_4cat_f"
)
```

Function cont by group

```{r}
cont_stats_group_fn <- function(.data, .group, .pred, stat_recipe = NULL, .digits = 2) {
  .data %>% 
    # Remove rows with missing values
    filter(!is.na({{ .pred }})) %>%
    group_by({{ .group }}) %>%
    # Calculations
    mean_table({{ .pred }}) %>%  
    # Format statistics
    mean_format(stat_recipe, digits = .digits) %>% 
    # Keep columns of interest
    select(var = response_var, group_cat, formatted_stats) %>%
    # Display by row_cat
    pivot_wider(
      names_from = "group_cat",
      values_from = "formatted_stats"
    )
}

# Test
# cont_stats_group_fn(l2c_v1_analysis, conviction, ml_age, stat_recipe = "mean (sd)")
```

Loop over all continuous variables

```{r}
cont_by_group <- map_df(
  .x = cont_vars,
  .f = ~ cont_stats_group_fn(l2c_v1_analysis, conviction, !! sym(.x), stat_recipe = "mean (sd)")
)
```

Function cat by group

```{r}
cat_stats_group_fn <- function(.data, .outcome, .pred, stat_recipe = NULL, .digits = 0) {
  .data %>% 
    # Remove rows with missing values
    filter(!is.na({{ .pred }})) %>% 
    # Calculations
    freq_table({{ .outcome }}, {{ .pred }}) %>%  
    # Format statistics
    freq_format(stat_recipe, digits = .digits) %>% 
    # Keep columns of interest
    select(row_var:col_cat, formatted_stats) %>%
    # Display by row_cat
    pivot_wider(
      names_from = "row_cat",
      values_from = "formatted_stats"
    ) %>%
    # Add spaces in front of category labels
    mutate(col_cat = paste0("  ", col_cat)) %>%
    # Slide category labels under row variable label
    add_row(col_cat = !!quo_name(enquo(.pred)), .before = 1) %>%
    select(-row_var, -col_var, var = col_cat) %>%
    # Paste all categories into one row
    mutate(
      across(
        everything(),
        function(x) {
          x <- paste(x, collapse = "\n")
          # Remove leading NA
          x <- stringr::str_remove(x, "^NA")
          x
        }
      )
    ) %>%
    slice(1)
}

# Test
# cat_stats_group_fn(l2c_v1_analysis, bh_26, gender_f, stat_recipe = "n (percent_row%)")
```

Loop over all categorical variables

```{r}
cat_by_group <- map_df(
  .x = cat_vars,
  .f = ~ cat_stats_group_fn(l2c_v1_analysis, conviction, !! sym(.x), stat_recipe = "n (percent_row%)")
)
```

Bind cat and cont by group

```{r}
table_01 <- bind_rows(
  cont_by_group,
  cat_by_group
)
```

Make flextable

```{r}
table_01_ft <- flextable(table_01)
```

Format flextable

```{r}
# N's for column headers
col_head_n <- table(l2c_v1_analysis$conviction)
no_col_header <- paste0("Not Convicted\n(n = ", col_head_n[1], ")")
yes_col_header <- paste0("Convicted\n(n = ", col_head_n[2], ")")
```

```{r}
table_01_ft <- table_01_ft %>%
  # Change column widths. figure out through trial and error
  width(width = c(2.17, 2.17, 2.17)) %>%
  # Center text in all but the first column
  align(j = -1, align = "center", part = "all") %>%
  # Change header names -- add subgroup n's to headers
  set_header_labels(
    var = "Characteristic",
    No = no_col_header,
    Yes = yes_col_header
  ) %>%
  # Bold column headers
  bold(part = "header")
```

Improve row headers

```{r}
# Get all of the variable names and add to a data frame
names_to_headers <- tibble(
  string = table_01$var,
  var_name = str_extract(string, "^\\w*"),
  type = if_else(var_name %in% cat_vars, "cat", "cont"),
  # We could maybe event grab these somewhere else if we save recipe
  # For now, just typing in manually
  stat = if_else(type == "cat", "n (col percent)", "mean (sd)")
)
```

```{r}
# Wrap all of this in a function
case_when_vars <- paste0('var_name == ', '"', names_to_headers$var_name, '"', ' ~ "",')
case_when_vars <- paste(case_when_vars, collapse = "\n    ")
case_when_vars <- str_remove(case_when_vars, ",$")
```

```{r}
# The user needs to tell us what the row header text should say
# Print some code that will help us make sure we don't miss any vars
# names_to_headers$var_name
cat(
paste0("names_to_headers <- names_to_headers %>%\n  mutate(header = case_when(\n    ", case_when_vars, "\n  ))")
)
```

```{r}
# A function for updating without starting over could be useful too.
names_to_headers <- names_to_headers %>%
  mutate(header = case_when(
    var_name == "ml_age" ~ "Age",
    var_name == "depression" ~ "Depression",
    var_name == "schizophrenia" ~ "Schizophrenia",
    var_name == "bipolar" ~ "Bipolar",
    var_name == "ptsd" ~ "PTSD",
    var_name == "anxiety" ~ "Anxiety",
    var_name == "gender_f" ~ "Gender",
    var_name == "race_4cat_f" ~ "Race/Ethnicity",
    var_name == "edu_4cat_f" ~ "Eduction"
  ))
```

```{r}
# Add the stats to the row headers
names_to_headers <- names_to_headers %>%
  mutate(header = paste0(header, ", ", stat))
```

```{r}
# Add carrot to the front of var_name so that the row header is only replaced
# when the string is found in the variable name as opposed to anywhere in string
names_to_headers$var_name <- paste0("^", names_to_headers$var_name)
```

```{r}
# Loop over all variables
for (i in 1:nrow(names_to_headers)) {
  table_01_ft <- table_01_ft %>%
    compose(
      i = ~ stringr::str_detect(var, names_to_headers$var_name[[i]]), 
      j = 1, 
      as_paragraph(str_replace(
        names_to_headers$string[[i]], 
        names_to_headers$var_name[[i]], 
        names_to_headers$header[[i]]
      ))
    )
}
```

Finish flextable formatting

```{r}
table_01_ft <- table_01_ft %>%
  # Use padding for row separation
  padding(padding.top = 0, padding.bottom = 10, part = "body") %>%
  # Change font to TNR 11
  font(fontname = "Arial", part = "all") %>%
  fontsize(part = "all", size = 11)
```

Add flextable to Word document

```{r}
doc <- read_docx("../../Abstract Projects/Nadia Stanley/Nstanley_Abstract_Proposal_1_80322.docx") %>% 
  body_replace_flextable_at_bkm("table_01", table_01_ft)
```

```{r}
print(
  doc,
  "../../Abstract Projects/Nadia Stanley/Nstanley_Abstract_Proposal_2022_08_07.docx"
)
```

## Table 2

```{r}
preds <- c("depression", "schizophrenia", "bipolar", "ptsd", "anxiety")
```

```{r}
unadj_formulas <- paste("conviction", preds, sep = " ~ ")
```

```{r}
covars <- c("ml_age", "gender_f", "race_4cat_f", "edu_4cat_f")
```

```{r}
covars_mod <- paste(covars, collapse = " + ")
```

```{r}
rhs <- paste(preds, covars_mod, sep = " + ")
```

```{r}
adj_formulas <- paste("conviction", rhs, sep = " ~ ")
```

# Unadjusted

```{r}
# For testing
glm(
  formula = unadj_formulas[3],
  family = binomial(link = 'logit'),
  data = l2c_v1_analysis
) %>% 
  broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~ format(round(.x, 2), digits = 2, nsmall = 2)
    )
  ) %>% 
  mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
  select(term, stats) %>% 
  slice(2)
```

```{r}
# All predictors
map_df(
  unadj_formulas,
  ~ glm(
    formula = .x,
    family = binomial(link = 'logit'),
    data = l2c_v1_analysis
  ) %>% 
    broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
    mutate(
      across(
        where(is.numeric), 
        ~ format(round(.x, 2), digits = 2, nsmall = 2)
      )
    ) %>% 
    mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
    select(term, stats) %>% 
    slice(2)
)
```



```{r}
# For testing
glm(
  formula = adj_formulas[1],
  family = binomial(link = 'logit'),
  data = l2c_v1_analysis
) %>% 
  broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~ format(round(.x, 2), digits = 2, nsmall = 2)
    )
  ) %>% 
  mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
  select(term, stats) %>% 
  slice(2)
```

```{r}
# All predictors
map_df(
  adj_formulas,
  ~ glm(
    formula = .x,
    family = binomial(link = 'logit'),
    data = l2c_v1_analysis
  ) %>% 
    broom::tidy(exp = TRUE, conf.int = TRUE) %>% 
    mutate(
      across(
        where(is.numeric), 
        ~ format(round(.x, 2), digits = 2, nsmall = 2)
      )
    ) %>% 
    mutate(stats = paste0(estimate, " (", conf.low, "-", conf.high, ")")) %>% 
    select(term, stats) %>% 
    slice(2)
)
```

# 🗑Clean up

```{r}
rm(list = ls())
```

```{r echo=FALSE}
sessionInfo()
```
